### 2022-11-14 ms.Rmd
more eda

---
title: 'To be determined: Associations between internet use and well-being in gallup world poll data'
shorttitle: tbd
leftheader: tbd
author: 
  - name: Matti Vuorre
    affiliation: 1
    corresponding: yes
    address: Oxford Internet Institute, University of Oxford
    email: matti.vuorre@oii.ox.ac.uk
    role:
      - Concept
  - name: Andrew K. Przybylski
    affiliation: 1
    email: andy.przybylski@oii.ox.ac.uk
    role:
      - Concept

affiliation:
  - id: 1
    institution: Oxford Internet Institute, University of Oxford

authornote: |
  \noindent \textbf{This manuscript is not yet peer-reviewed.}

abstract: |
  We analyse GWP data to look at relation between internet use and well-being.

keywords: words, key
wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
bibliography: "references.bib"
floatsintext: yes
linenumbers: yes
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass: apa7
classoption: jou
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
---

<!-- First a section of lots of EDA -->

```{r setup, include = FALSE}
library(papaja)
library(scales)
library(knitr)
library(corrr)
library(tidyverse)
opts_chunk$set(
  include = FALSE
)

# Parallel computation options
MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
```

```{r}
#| label: data-clean
path <- "data-raw/gwp.rds"

# List of indices
ix <- list(
  life_satisfaction = c("WP16"),
  negative_experiences = c("WP68", "WP69", "WP70", "WP71", "WP74"), # negative experiences
  positive_experiences = c("WP60", "WP61", "WP63", "WP65", "WP67"), # positive experiences
  loneliness = c("WP27", "WP10248"), # social life index, or inverse "loneliness"
  law = c("WP112", "WP113", "WP117", "WP118"), # law and order index
  foodshelter = c("WP40", "WP43"), # food and shelter index
  # community basics index
  communitybasics = c("WP91", "WP92", "WP94", "WP95", "WP98", "WP93", "WP97"), 
  # financiallife = c("WP2319", "WP30", "WP31", "WP88"),
  civicengagement = c("WP108", "WP109", "WP110"),
  communityattachment = c("WP83", "WP85", "WP86"),
  diversityindex = c("WP103", "WP105", "WP106"),
  # Gallup-Sharecare Global Well-Being Index
  gwpi_purpose = c("WP14442", "WP14443"),
  gwpi_social = c("WP14444", "WP14445"),
  gwpi_financial = c("WP14446", "WP14447"),
  gwpi_community = c("WP14450", "WP14451"),
  gwpi_physical = c("WP14448", "WP14449")
)

if (dir.exists("data-raw/gallup") & !file.exists(path)) {
  library(haven)
  library(labelled)
  # Load relevant variables
  dat <- read_spss(
    "data-raw/gallup/The_Gallup_042722.sav", 
    col_select = c(
      WP5, # country
      YEAR_CALENDAR,
      WP1220, # age
      WP1219, # sex
      WP14, # urbanicity
      INCOME_2, # Annual Household Income in International Dollars
      WP16056, # internet access
      WP39, # internet access at home
      WP19544, # internet on your phone
      WP15862, # internet used past 7 days
      # outcomes, indices, etc
      all_of(
        unlist(ix)
      )
    )
  )

  # Rename and recode demographics and predictors
  dat <- dat %>% 
    mutate(
      country = as_factor(WP5),
      year = as.integer(YEAR_CALENDAR),
      age = na_if(as.numeric(WP1220), 100),
      sex = factor(as_factor(WP1219), levels = c("Female", "Male")),
      urban = factor(
        as_factor(WP14),
        levels = c(
          "A rural area or on a farm", "A small town or village", 
          "A suburb of a large city", "A large city"  
        ),
        labels = c("Rural", "Town", "Suburb", "City")
      ), 
      income = as.numeric(INCOME_2),
      internet_access = factor(as_factor(WP16056), levels = c("No", "Yes")),
      internet_past7days = factor(as_factor(WP15862), levels = c("No", "Yes")),
      internet_home = factor(as_factor(WP39), levels = c("No", "Yes")),
      internet_phone = factor(as_factor(WP19544), levels = c("No", "Yes")),
      .keep = "unused",
      .before = 1
    )

  # Recode items
  # make (DK) and (Refused) NAs
  # make values run from 0 (negative construct) to max (positive construct)

  # primary index variables
  dat %>% 
    select(all_of(unlist(ix[1:4], use.names = FALSE))) %>% 
    generate_dictionary()
  dat <- dat %>% 
    mutate(
      # Life satisfaction is already in correct order, 98 & 99 are DK and refused
      WP16 = if_else(WP16 %in% 98:99, as.integer(NaN), as.integer(WP16)),
      # Negative experiences, positive experiences, and "loneliness"
      # 3:DK, 4:refused, 1:yes, 2:no
      across(
        all_of(as.character(unlist(ix[2:4]))), 
        ~if_else(. %in% 3:4, as.integer(NaN), as.integer(2 - .))
      )

    )

  # Then the other scales
  dat %>% 
    select(all_of(unlist(ix[-c(1:4)], use.names = FALSE))) %>% 
    generate_dictionary()
  dat <- dat %>% 
    mutate(
      # Law and order, Food and shelter, Community basics, Civic engagement, Community attachment, Diversity index
      # 1: positive (various) 2: negative (various), 3:DK, 4:refuse
      across(
        all_of(as.character(unlist(ix[5:10]))), 
        ~if_else(. %in% 3:4, as.integer(NaN), as.integer(2 - .))
      ),
      # GWPI items
      # 1: disagree 5:agree, 8:DK 9:refused
      across(
        all_of(as.character(unlist(ix[11:15]))), 
        ~if_else(. %in% 8:9, as.integer(NaN), as.integer(. - 1))
      ),
    )

  # Aggregate scales
  for (i in 1:length(ix)) {
    dat[[names(ix[i])]] <- rowMeans(
      select(
        dat, 
        all_of(as.character(unlist(ix[i])))
      ), 
      na.rm = TRUE
    ) 
  }

  # Remove other scale items
  dat <- dat %>% 
    select(-all_of(as.character(unlist(ix[5:15]))))

  # Save
  write_rds(dat, path)
}
dat <- read_rds(path)
```

```{r}
#| label: chord-diagram
#| eval: false
# Correlation
library(circlize)

x <- dat %>% 
  select(-c(1:6, all_of(as.character(unlist(ix[1:4]))))) %>% 
  mutate(across(starts_with("internet"), as.numeric)) %>% 
  # correlate()

x2 <- x %>% 
  stretch() %>% 
  drop_na(r) %>% 
  mutate(
    across(x:y, ~str_replace(., "internet", "www"))
  )

x2 %>% 
  chordDiagramFromDataFrame(
    col = colorRamp2(
      c(-1, 1), 
      c("firebrick1", "dodgerblue1")
      ),
    transparency = 0.25
  )
```

```{r}
x <- dat %>% 
  filter(year == 2021) %>% 
  select(
    -c(
      1:5, internet_access, internet_home, starts_with("gwpi"),
      all_of(as.character(unlist(ix[1:4])))
    )
  ) %>% 
  mutate(across(where(is.factor), ~as.numeric(.)-1)) %>% 
  correlate(method = "spearman")

x %>% 
  rename_with(~str_replace(., "internet", "net") %>% str_trunc(12, ellipsis = "")) %>% 
  # rearrange() %>%
  shave() %>% 
  fashion() %>% 
  as_tibble() %>% 
  select(1:13) %>% 
  kable(caption = "Correlations in 2021")
```

```{r}
#| label: eda-missingness
#| eval: false
# Explore missingness in data
library(naniar)
dat %>% 
  group_by(year) %>% 
  summarise(
    `Total rows` = n(),
    across(c(income, urban, starts_with("internet")), ~sum(!is.na(.)))
  ) %>% 
  mutate(
    across(income:internet_phone, ~./`Total rows`),
    `Total rows` = number(`Total rows`, big.mark = ",")
  ) %>% 
  kable(
    digits = 2, 
    caption = "Existing covariates over time in GWP data"
  )

dat %>% 
  group_by(year, country) %>% 
  summarise(
    across(
      starts_with("internet"),
      .fns = list(total = ~n(), missing = ~sum(is.na(.))), 
      .names = "{.col}.{.fn}"
    )
  ) %>% 
  ungroup() %>% 
  pivot_longer(-c(year, country)) %>% 
  separate(name, c("x", "y"), sep = "\\.") %>% 
  pivot_wider(values_from = value, names_from = y) %>% 
  filter(country %in% sample(unique(dat$country), 25)) %>%
  ggplot(aes(year, missing/total, col = x)) +
  geom_line() +
  facet_wrap("country") +
  theme(legend.position = "bottom")

# Cross-missingness
dat %>% 
  filter(year == 2019) %>% 
  select(income, urban, starts_with("internet")) %>% 
  naniar::as_shadow() %>% 
  rename_with(~str_remove(., "internet_") %>% str_remove("_NA")) %>% 
  mutate(across(everything(), as.numeric)) %>% 
  cor(method = "spearman") %>% 
  kable(digits = 2)
```

# Methods

Gallup world poll is a dataset that has data.

## Internet engagement

- "Communications Access Index"
  - [WP39]: Does your home have access to the internet? 
  - [WP16056]: Do you have access to the internet in any way, whether on a mobile phone, a computer, or some other device?
    1 Yes
    2 No
    3 (DK)
    4 (Refused)
- "Communications Use Index"
  - [WP15862]: Have you used the internet in the past seven days, whether on a mobile phone, a computer, or some other device?
    1 Yes
    2 No
    3 (DK)
    4 (Refused)
- In "Appendix A: 2021 Core Questions and Codes"
  - [WP19544]: Can your mobile phone be used to access the Internet?
    1 Yes
    2 No
    3 (DK)
    4 (Refused)

## Data analysis

We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses.

\clearpage

# References

::: {#refs custom-style="Bibliography"}
:::

<!-- Create an appendix with new page, table, and figure numbers. -->

<!-- \clearpage -->
<!-- \onecolumn -->

<!-- # Supplementary online material to Title (Authors) -->

<!-- Prepend table & figure numbers with S and reset counters -->
<!-- \setcounter{page}{1} -->
<!-- \setcounter{table}{0} -->
<!-- \setcounter{figure}{0} -->
<!-- \renewcommand{\thetable}{S\arabic{table}} -->
<!-- \renewcommand{\thefigure}{S\arabic{figure}} -->

<!-- ```{r include-only-for-pdf} -->
<!-- #| include: !expr knitr::is_latex_output() -->
<!-- ``` -->

### 2022-11-25 ms.Rmd
Lots of EDA

@@
 ---
-title: 'To be determined: Associations between internet use and well-being in gallup world poll data'
-shorttitle: tbd
-leftheader: tbd
+title: 'How well do internet access and use predict well-being: A study of a boat load of people from everywhere in the world'
+shorttitle: Internet and well-being
+leftheader: Internet and well-being
 author: 
@@
     role:
-      - Concept
+      - Thought leader
   - name: Andrew K. Przybylski
@@
     role:
-      - Concept
+      - Visionary
 
@@
 abstract: |
-  We analyse GWP data to look at relation between internet use and well-being.
+  With the increasing global penetration of internet technologies and proliferation of subsequent online platforms, debate on their effects on human well-being has remained topical.
+Research suggests that online platforms such as social media might affect users negatively.
+However, studied from another perspective, research also suggests that access and use of internet technologies is a precondition for well-being in today's interconnected world.
 
-keywords: words, key
-wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
+  In this study, we tested how different aspects of internet access and use predicted 8 well-being outcomes over 16 years among 2.45 million individuals living in 164 countries.
+Results.
+Implications.
+Conclusion.
+
+keywords: well-being, internet technology, technology effects
+wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
 bibliography: "references.bib"
 floatsintext: yes
-linenumbers: yes
+linenumbers: no
 draft: no
@@
 
-<!-- First a section of lots of EDA -->
-
 ```{r setup, include = FALSE}
@@
 library(knitr)
+library(patchwork)
+library(ggdist)
 library(corrr)
@@
 opts_chunk$set(
-  include = FALSE
+  include = FALSE,
+  cache = TRUE
 )
@@
 if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
+theme_set(
+  theme_linedraw(base_size = 13) +
+    theme(
+      strip.background = element_rect(fill = "gray90", color = "gray90"),
+      strip.text = element_text(color = "black", hjust = 0),
+      panel.grid.minor = element_blank(),
+      panel.grid.major = element_line(colour = "black", linetype = "dotted")
+    )
+)
 ```
@@
   life_satisfaction = c("WP16"),
-  negative_experiences = c("WP68", "WP69", "WP70", "WP71", "WP74"), # negative experiences
-  positive_experiences = c("WP60", "WP61", "WP63", "WP65", "WP67"), # positive experiences
-  loneliness = c("WP27", "WP10248"), # social life index, or inverse "loneliness"
-  law = c("WP112", "WP113", "WP117", "WP118"), # law and order index
-  foodshelter = c("WP40", "WP43"), # food and shelter index
-  # community basics index
-  communitybasics = c("WP91", "WP92", "WP94", "WP95", "WP98", "WP93", "WP97"), 
-  # financiallife = c("WP2319", "WP30", "WP31", "WP88"),
-  civicengagement = c("WP108", "WP109", "WP110"),
-  communityattachment = c("WP83", "WP85", "WP86"),
-  diversityindex = c("WP103", "WP105", "WP106"),
-  # Gallup-Sharecare Global Well-Being Index
+  negative_experiences = c("WP68", "WP69", "WP70", "WP71", "WP74"),
+  positive_experiences = c("WP60", "WP61", "WP63", "WP65", "WP67"),
+  social_life = c("WP27", "WP10248"), 
+  laworder = c("WP112", "WP113", "WP117", "WP118"), 
+  foodshelter = c("WP40", "WP43"), 
   gwpi_purpose = c("WP14442", "WP14443"),
   gwpi_social = c("WP14444", "WP14445"),
-  gwpi_financial = c("WP14446", "WP14447"),
-  gwpi_community = c("WP14450", "WP14451"),
+  # gwpi_financial = c("WP14446", "WP14447"),
   gwpi_physical = c("WP14448", "WP14449")
@@
     col_select = c(
-      WP5, # country
+      WP5, 
       YEAR_CALENDAR,
-      WP1220, # age
-      WP1219, # sex
-      WP14, # urbanicity
-      INCOME_2, # Annual Household Income in International Dollars
-      WP16056, # internet access
-      WP39, # internet access at home
-      WP19544, # internet on your phone
-      WP15862, # internet used past 7 days
-      # outcomes, indices, etc
+      WP1220,
+      WP1219, 
+      WP23, 
+      WP1223, 
+      INCOME_2,
+      WP2319,
+      WP16056,
+      WP39,
+      WP19544,
+      WP15862,
       all_of(
@@
 
-  # Rename and recode demographics and predictors
+  # Replace values with labels DK and Refused to proper NAs
+  val_labels(dat)  # These are the current value labels
+  to_na <- function(x) {
+    na_values(x) <- val_labels(x)[c("(DK)", "(Refused)")]
+    x
+  }
+  dat <- dat %>% 
+    mutate(across(c(everything(), -WP1219, -WP1220), to_na))
+  dat <- user_na_to_na(dat)
+  val_labels(dat)
+  str(dat)
+
   dat <- dat %>% 
     mutate(
-      country = as_factor(WP5),
+      country = fct_drop(as_factor(WP5)),
       year = as.integer(YEAR_CALENDAR),
-      age = na_if(as.numeric(WP1220), 100),
+      age = as.integer(ceiling(WP1220)),
       sex = factor(as_factor(WP1219), levels = c("Female", "Male")),
-      urban = factor(
-        as_factor(WP14),
-        levels = c(
-          "A rural area or on a farm", "A small town or village", 
-          "A suburb of a large city", "A large city"  
-        ),
-        labels = c("Rural", "Town", "Suburb", "City")
+      healthprob = factor(as_factor(WP23), levels = c("No", "Yes")),
+      relationship = fct_collapse(
+        as_factor(dat$WP1223),
+        Single = c("Single/Never been married", "Separated", "Divorced", "Widowed"),
+        Relationship = c("Married", "Domestic partner")
       ),
       income = as.numeric(INCOME_2),
+      income_feeling = 4 - as.integer(WP2319),
       internet_access = factor(as_factor(WP16056), levels = c("No", "Yes")),
@@
 
-  # Recode items
-  # make (DK) and (Refused) NAs
-  # make values run from 0 (negative construct) to max (positive construct)
+  # Fix one of each 13yr and 101yr
+  dat$age <- if_else(dat$age < 15L, 15L, if_else(dat$age > 100L, 100L, dat$age))
+  summary(dat$age)
 
@@
     mutate(
-      # Life satisfaction is already in correct order, 98 & 99 are DK and refused
-      WP16 = if_else(WP16 %in% 98:99, as.integer(NaN), as.integer(WP16)),
+      # Life satisfaction is already in correct order but rescale
+      life_satisfaction = if_else(
+        WP16 %in% 98:99, 
+        as.numeric(NaN), 
+        as.numeric(WP16) / 10
+      ),
       # Negative experiences, positive experiences, and "loneliness"
-      # 3:DK, 4:refused, 1:yes, 2:no
+      # 1 is yes, 2 is no; reverse
       across(
         all_of(as.character(unlist(ix[2:4]))), 
-        ~if_else(. %in% 3:4, as.integer(NaN), as.integer(2 - .))
+        ~as.integer(2 - .)
       )
-
+    ) %>% 
+    mutate(
+      negative_experiences = rowMeans(
+        select(., WP68, WP69, WP70, WP71, WP74), na.rm = TRUE
+      ),
+      positive_experiences = rowMeans(
+        select(., WP60, WP61, WP63, WP65, WP67), na.rm = TRUE
+      ),
+      social_life = rowMeans(
+        select(., WP27, WP10248), na.rm = TRUE
+      )
     )
@@
   dat %>% 
-    select(all_of(unlist(ix[-c(1:4)], use.names = FALSE))) %>% 
     generate_dictionary()
@@
     mutate(
-      # Law and order, Food and shelter, Community basics, Civic engagement, Community attachment, Diversity index
-      # 1: positive (various) 2: negative (various), 3:DK, 4:refuse
-      across(
-        all_of(as.character(unlist(ix[5:10]))), 
-        ~if_else(. %in% 3:4, as.integer(NaN), as.integer(2 - .))
-      ),
+      # Law and order
+      WP112 = 2 - WP112,
+      WP113 = 2 - WP113,
+      WP117 = WP117 - 1,
+      WP118 = WP118 - 1,
+    ) %>% mutate(
+      laworder = rowMeans(select(., WP112, WP113, WP117, WP118), na.rm = TRUE),
+      # Food and shelter [note below], 
+      foodshelter = rowMeans(select(., WP40, WP43), na.rm = TRUE) - 1,
       # GWPI items
-      # 1: disagree 5:agree, 8:DK 9:refused
-      across(
-        all_of(as.character(unlist(ix[11:15]))), 
-        ~if_else(. %in% 8:9, as.integer(NaN), as.integer(. - 1))
-      ),
+      gwpi_purpose = rowMeans(select(., WP14442, WP14443), na.rm = TRUE) - 1,
+      gwpi_social = rowMeans(select(., WP14444, WP14445), na.rm = TRUE) - 1,
+      # WP14447 = 6 - WP14447,
+      # gwpi_finance = rowMeans(select(., WP14446, WP14447), na.rm = TRUE) - 1,
+      gwpi_physical = rowMeans(select(., WP14448, WP14449), na.rm = TRUE) - 1,
+      .keep = "unused"
     )
 
-  # Aggregate scales
-  for (i in 1:length(ix)) {
-    dat[[names(ix[i])]] <- rowMeans(
-      select(
-        dat, 
-        all_of(as.character(unlist(ix[i])))
-      ), 
-      na.rm = TRUE
-    ) 
-  }
-
-  # Remove other scale items
+  # Remove now unnecessary variables
+  glimpse(dat)
   dat <- dat %>% 
-    select(-all_of(as.character(unlist(ix[5:15]))))
+    select(-c(WP16, WP40, WP43, WP112, WP113, WP117, WP118, WP1223, starts_with("WP1444")))
 
@@
 dat <- read_rds(path)
+
+# A few dozen missing sex
+dat <- drop_na(dat, sex)
+
+# Income logp1
+dat <- mutate(dat, income = log(income+1))
 ```
@@
 # Correlation
-library(circlize)
+# library(circlize)
+# 
+# x <- dat %>% 
+#   select(-c(1:6, all_of(as.character(unlist(ix[1:4]))))) %>% 
+#   mutate(across(starts_with("internet"), as.numeric)) %>% 
+#   correlate()
+#   
+#   x2 <- x %>% 
+#   stretch() %>% 
+#   drop_na(r) %>% 
+#   mutate(
+#     across(x:y, ~str_replace(., "internet", "www"))
+#   ) 
+# 
+# x2 %>% 
+#   chordDiagramFromDataFrame(
+#     col = colorRamp2(
+#       c(-1, 1), 
+#       c("firebrick1", "dodgerblue1")
+#     ),
+#     transparency = 0.25
+#   )
+```
 
-x <- dat %>% 
-  select(-c(1:6, all_of(as.character(unlist(ix[1:4]))))) %>% 
-  mutate(across(starts_with("internet"), as.numeric)) %>% 
-  # correlate()
+# Introduction
 
-x2 <- x %>% 
-  stretch() %>% 
-  drop_na(r) %>% 
+- What we do and why, and what is the problem
+- Previous related efforts
+- The theories™
+- What's left for us to study
+
+## Well-being
+
+In this study, we tried to capture a wide variety of responses under the umbrella term of well-being [@ryffStructurePsychologicalWellbeing1995].
+
+## Well-being in the internet age
+
+Go into some depth on the literature linking the internet (how broad? is anyone talking about the internet vs specific things like tiktok?).
+
+## Current study
+
+Our overarching aim was to estimate the extent to which internet access and use predict well-being, while adjusting for other background variables that might confound the relationship.
+Our goal with these adjustments, discussed in more detail below, was to move toward identifying the independent contributions that internet access and use might have on well-being.
+
+- Research question 1, motivated by the past research, albeit contested, and healthcare / policy recommendations suggesting that internet device/platform use might lead to negative outcomes (especially for youth):
+  - **RQ1 - Hypothesis 1.** Individuals who used internet in the past 7 days would report lower well-being than those who didn't;
+  - **RQ1 - H2.** this contrast would be pronounced for young individuals who have not yet developed healthy self-regulation.
+- Research question 2, motivated by the idea of a "digital divide": 
+  - **RQ2 - H1.** Individuals who have access to the internet report greater well-being than those who don't;
+  - **RQ2 - H2.** this difference is more pronounced in countries where overall internet adoption is greater.
+- Research question 3, motivated by the worries over digital devices: 
+  - **RQ3 - H1.** Individuals who have internet access on their phones report lower levels of well-being;
+  - **RQ3 - H2.** ???
+
+In addition, because previous literature has highlighted important sex differences in the associations between internet technology use and well-being, especially among young people, we examined whether the sex of the individual mattered to any of our target associations.
+
+We did not have specific hypotheses regarding the different outcomes, but rather investigated a holistic picture.
+To answer, we estimated really interesting and informative bayesian multilevel models that assumed plausible data-generating mechanisms and respected data missingness as a bona-fide phenomenon to be modelled alongside the existing data.
+
+# Methods
+
+```{r}
+# Summarise original values
+tmp <- dat %>% 
+  group_by(year) %>% 
+  summarise(
+    `Total rows` = n(),
+    across(c(starts_with("internet")), ~sum(!is.na(.)))
+  ) %>% 
   mutate(
-    across(x:y, ~str_replace(., "internet", "www"))
+    across(starts_with("internet"), ~ . / `Total rows`)
   )
 
-x2 %>% 
-  chordDiagramFromDataFrame(
-    col = colorRamp2(
-      c(-1, 1), 
-      c("firebrick1", "dodgerblue1")
-      ),
-    transparency = 0.25
+# Create combined internet access variable
+dat <- dat %>% 
+  mutate(
+    internet_access = if_else(year < 2016, internet_home, internet_access)
+  ) %>% 
+  select(-internet_home)
+
+# Because internet variable coverage is so poor in 2005 we only use data from 2006
+dat <- filter(dat, year > 2005)
+```
+
+We analysed data from the Gallup World Poll [@gallupWorldPollMethodology2022].
+Gallup World Poll (GWP) is a nationally representative (of each country's civilian, non-institutionalized, adult [15+] population) continuous annual survey of approximately 1,000 individuals from each of 164 countries from 2005 to 2022.
+Gallup conducts the surveys through one-hour interviews either face-to-face or via telephone, in the respondents native language, and the core questionnaire is translated to the major conversational language of each country.
+For the GWP methodological details, see @gallupWorldPollMethodology2022.
+We used data from `r number(nrow(dat), big.mark = ",")` individuals from 2006 to 2022.
+
+## Data availability
+
+We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
+All the code, and simulated datasets, is available at [Zenodo].
+We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database.
+
+## Internet access and use
+
+The key variables that we considered as predictors measured the respondents' access and use of the internet.
+From 2005 to 2022, GWP has surveyed these with four items that have varying coverage over the years.
+First, GWP measures internet access with *"Does your home have access to the internet?"* (2005 to 2015).
+Because the coverage of existing data for this variable was so low in 2005 (`r percent(tmp$internet_home[1], .1)`), we used this variable from 2006 to 2015, where the mean percentage of non-missing values was `r percent(mean(tmp$internet_home[2:11]), .1)`.
+From 2016 to 2022, a similar question measured overall internet access with *"Do you have access to the internet in any way, whether on a mobile phone, a computer, or some other device?"* (mean coverage `r percent(mean(tmp$internet_access[12:18]), .1)`).
+Because of the similarity of these two questions, and to extend the range of data coverage, we merged these two variables to one "internet access" variable.
+
+Second, GWP has asked about mobile internet access with *"Can your mobile phone be used to access the Internet?"* from 2017 to 2022 (mean coverage `r percent(mean(tmp$internet_phone[13:18]), .1)`).
+Third, GWP has measured internet *use* with *"Have you used the internet in the past seven days, whether on a mobile phone, a computer, or some other device?"* from 2015 to 2022.
+However, due to poor coverage in 2015 (`r percent(mean(tmp$internet_past7days[11]), .1)`), we used this variable from 2016 to 2022 (mean coverage `r percent(mean(tmp$internet_past7days[12:18]), .1)`).
+
+All of these items had binary "Yes"/"No" response options, and respondents were given the option to decline an answer or report that they didn't know. We coded the latter two as missing values.
+
+```{r}
+#| label: fig-internet
+#| include: true
+#| fig.height: 5.5
+#| fig.cap: Internet access and use data availability and summary over time.
+
+# Figure
+sanitize_labels <- function(x) {
+  # Make internet predictors look ok
+  x %>% 
+    str_replace("_", " ") %>% 
+    str_replace("7", " 7 ") %>% 
+    str_to_sentence()
+}
+
+p1 <- dat %>% 
+  select(
+    year, starts_with("internet"),
+    life_satisfaction, negative_experiences, 
+    positive_experiences, social_life
+  ) %>% 
+  mutate(across(c(where(is.factor)), ~as.numeric(.)-1)) %>% 
+  group_by(year) %>% 
+  summarise(
+    across(
+      everything(), 
+      list(valid = ~sum(!is.na(.)) / n(), mean = ~mean(., na.rm = TRUE)), 
+      .names = "{.col}.{.fn}"
+    )
+  ) %>% 
+  mutate(across(ends_with("valid"), ~if_else(. < 0.1, NaN, .))) %>% 
+  pivot_longer(-c(year)) %>% 
+  separate(name, c("variable", "measure"), sep = "\\.") %>% 
+  ggplot(aes(year, value, col = measure)) +
+  scale_color_brewer(
+    "Variable",
+    palette = "Set1",
+    labels = ~factor(., levels = c("mean", "valid"), labels = c("Mean response", "Valid responses"))
+  ) +
+  scale_y_continuous(
+    limits = 0:1,
+    expand = expansion(c(0.03, 0.06)),
+    labels = ~percent(., 1)
+  ) +
+  scale_x_continuous(
+    "Year",
+    breaks = extended_breaks(5)
+  ) +
+  geom_line(linewidth = 0.4) +
+  geom_point() +
+  facet_wrap(
+    "variable", 
+    scales = "free_x",
+    labeller = as_labeller(sanitize_labels),
+    nrow = 1
+  ) +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom", 
+    legend.title = element_blank()
+  )
+p2 <- (p1 %+% filter(p1$data, str_starts(variable, "internet"))) + 
+  theme(
+    legend.position = "none",
+    axis.title.x = element_blank()
+  )
+p3 <- (p1 %+% filter(p1$data, !str_starts(variable, "internet")))
+(p2 / p3) +
+  plot_annotation(tag_levels = "A") +
+  plot_layout(heights = c(5.5, 4.5))
+```
+
+## Well-being outcomes
+
+We focused on eight measures of well-being, broadly defined, in the Gallup World Poll: Life satisfaction, negative and positive experiences, social life satisfaction.
+In addition to these four outcomes, which were included in the GWP from 2005 to 2022, we studied four indicators from the Gallup-Sharecare Global Well-being Index™, which is a "barometer of individuals perceptions of their own well-being", and was measured between 2013 and 2015.
+
+Life satisfaction was measured with a single item: *"Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top.
+The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you.
+On which step of the ladder would you say you personally feel you stand at this time?"*, and respondents chose a number from 0 to 10.
+We rescaled this item to range from 0 to 1.
+
+Negative and positive experiences are both measured through a set of five Yes/No items.
+For negative experiences, respondents answered the prompts *"Did you experience the following feelings during a lot of the day yesterday?"*, *"How about physical pain / worry / sadness / stress / anger?"*.
+For positive experiences, the items were *"Did you feel well-rested yesterday?"*; *"Were you treated with respect all day yesterday?"*; *"Did you smile or laugh a lot yesterday?"*; *"Did you learn or do something interesting yesterday?*"; and *"Did you experience the following feelings during a lot of the day yesterday?
+How about enjoyment?"*.
+
+In 2013 through 2015, the GWP database also included the (Gallup-Sharecare) Global Well-being Index™, which measured (among others) experiences of purpose (*"liking what one does each day and being motivated to achieve one’s goals"*); social well-being (*"having supportive relationships and love in your life"*); and physical well-being, from which we included the item *"In the last seven days, you have felt active and productive every day"*.
+The sense of purpose was measured with prompts *"You like what you do every day"* and *"You learn or do something interesting every day"*.
+Social well-being was measured with *"Someone in your life always encourages you to be healthy"* and *"Your friends and family give you positive energy every day"*.
+All items included the prompt *"Thinking about your life in general, please rate your level of agreement with each of the following using a five-point scale, where 5 means you STRONGLY AGREE and 1 means you STRONGLY DISAGREE.
+You may choose any of the numbers 1, 2, 3, 4, or 5."*
+
+While these scales are not psychometrically validated, Gallup cites prominent scientists as having helped with their development.
+While we find that statement of dubious value, we believe that the unique scope of the dataset, both across time and countries, makes it a valuable object of study.
+
+## Covariates
+
+Our intent in this study was to approach the independent contributions of internet access and use on well-being.
+To that end, we adjusted for plausible covariates that were available in the GWP.
+First, previous research has highlighted important differences between males and females in both their levels of well-being and use of internet technologies (e.g.
+Figure \@ref(fig:fig-internet-by-sex)).
+In addition for adjusting for sex, we included it as a moderator in all our analyses.
+
+```{r}
+#| label: fig-internet-by-sex
+#| include: true
+#| fig.height: 2.8
+#| fig.cap: Overall proportions of each country's internet users by sex.
+Points are individual countries.
+The regression line indicates that males overall were more likely to have internet access and used internet more frequently, but this divide was smaller for countries where overall adoption was greater.
+dat %>% 
+  group_by(country, year, sex) %>% 
+  summarise(across(starts_with("internet"), ~mean(as.numeric(.)-1, na.rm = TRUE))) %>% 
+  group_by(country, sex) %>% 
+  summarise(across(starts_with("internet"), ~mean(., na.rm = TRUE))) %>% 
+  ungroup() %>% 
+  mutate(m = rowMeans(select(., starts_with("internet")), na.rm = TRUE)) %>% 
+  arrange(m) %>% 
+  mutate(country = fct_inorder(country)) %>% 
+  select(-m) %>% 
+  pivot_longer(starts_with("internet")) %>%
+  pivot_wider(names_from = sex, values_from = value) %>% 
+  ggplot(aes(Male, Female)) +
+  scale_x_continuous(
+    "Males",
+    labels = ~percent(., 1)
+  ) +
+  scale_y_continuous(
+    "Females",
+    labels = ~percent(., 1)
+  ) +
+  geom_abline(linetype = "dotted") +
+  geom_point(shape = 1, col = "dodgerblue1") +
+  geom_smooth(method = "lm", se = FALSE, col = "dodgerblue4") +
+  facet_wrap(
+    "name",
+    nrow = 1,
+    labeller = as_labeller(sanitize_labels),
+  ) +
+  theme(
+    aspect.ratio = 1
   )
@@
 
-```{r}
-x <- dat %>% 
-  filter(year == 2021) %>% 
-  select(
-    -c(
-      1:5, internet_access, internet_home, starts_with("gwpi"),
-      all_of(as.character(unlist(ix[1:4])))
-    )
-  ) %>% 
-  mutate(across(where(is.factor), ~as.numeric(.)-1)) %>% 
-  correlate(method = "spearman")
+Second, there is a vast literature on the associations between *adolescent* internet technology use and well-being [ref] (while at the same time few seem to be interested in older individuals [@burnsThoughtExperimentWhat2022]).
+Much of the policy discussion has also revolved around protecting young people from online harms [ref!].
+We therefore included age as a covariate in our models.
 
-x %>% 
-  rename_with(~str_replace(., "internet", "net") %>% str_trunc(12, ellipsis = "")) %>% 
-  # rearrange() %>%
-  shave() %>% 
-  fashion() %>% 
-  as_tibble() %>% 
-  select(1:13) %>% 
-  kable(caption = "Correlations in 2021")
-```
+In addition:
 
-```{r}
-#| label: eda-missingness
-#| eval: false
-# Explore missingness in data
-library(naniar)
-dat %>% 
-  group_by(year) %>% 
-  summarise(
-    `Total rows` = n(),
-    across(c(income, urban, starts_with("internet")), ~sum(!is.na(.)))
-  ) %>% 
-  mutate(
-    across(income:internet_phone, ~./`Total rows`),
-    `Total rows` = number(`Total rows`, big.mark = ",")
-  ) %>% 
-  kable(
-    digits = 2, 
-    caption = "Existing covariates over time in GWP data"
-  )
-
-dat %>% 
-  group_by(year, country) %>% 
-  summarise(
-    across(
-      starts_with("internet"),
-      .fns = list(total = ~n(), missing = ~sum(is.na(.))), 
-      .names = "{.col}.{.fn}"
-    )
-  ) %>% 
-  ungroup() %>% 
-  pivot_longer(-c(year, country)) %>% 
-  separate(name, c("x", "y"), sep = "\\.") %>% 
-  pivot_wider(values_from = value, names_from = y) %>% 
-  filter(country %in% sample(unique(dat$country), 25)) %>%
-  ggplot(aes(year, missing/total, col = x)) +
-  geom_line() +
-  facet_wrap("country") +
-  theme(legend.position = "bottom")
-
-# Cross-missingness
-dat %>% 
-  filter(year == 2019) %>% 
-  select(income, urban, starts_with("internet")) %>% 
-  naniar::as_shadow() %>% 
-  rename_with(~str_remove(., "internet_") %>% str_remove("_NA")) %>% 
-  mutate(across(everything(), as.numeric)) %>% 
-  cor(method = "spearman") %>% 
-  kable(digits = 2)
-```
-
-# Methods
-
-Gallup world poll is a dataset that has data.
-
-## Internet engagement
-
-- "Communications Access Index"
-  - [WP39]: Does your home have access to the internet? 
-  - [WP16056]: Do you have access to the internet in any way, whether on a mobile phone, a computer, or some other device?
-    1 Yes
-    2 No
-    3 (DK)
-    4 (Refused)
-- "Communications Use Index"
-  - [WP15862]: Have you used the internet in the past seven days, whether on a mobile phone, a computer, or some other device?
-    1 Yes
-    2 No
-    3 (DK)
-    4 (Refused)
-- In "Appendix A: 2021 Core Questions and Codes"
-  - [WP19544]: Can your mobile phone be used to access the Internet?
-    1 Yes
-    2 No
-    3 (DK)
-    4 (Refused)
+- Health problems (yes/no)
+- Relationship status (relationship/single)
+- income (within-country centered)
 
@@
 We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses.
+
+```{r}
+dat
+```
+
+# Results
+
+```{r}
+#| include: true
+x <- dat %>% 
+  # filter(year > 2013) %>% 
+  select(
+    starts_with("internet"),
+    income, healthprob, relationship, 
+    laworder, foodshelter,
+    life_satisfaction, negative_experiences, positive_experiences, social_life,
+    starts_with("gwpi_")
+  ) %>% 
+  mutate(across(where(is.factor), ~as.numeric(.)-1)) %>% 
+  correlate()
+y <- x %>% 
+  # shave() %>% 
+  fashion(na_print = "-") %>% 
+  as_tibble() %>% 
+  mutate(term = str_glue("{term} ({1:nrow(x)})")) %>% 
+  mutate(term = sanitize_labels(term))
+  names(y) <- c(" ", 1:(ncol(y)-1))
+  y %>%   
+    apa_table(
+      font_size = "scriptsize",
+      placement = "h",
+      caption = "Pearson correlations between key variables.",
+      note = "We used all pairwise-complete observations."
+    )
+```
 
@@
 
-<!-- Create an appendix with new page, table, and figure numbers. -->
+\clearpage
+\onecolumn
 
-<!-- \clearpage -->
-<!-- \onecolumn -->
-
-<!-- # Supplementary online material to Title (Authors) -->
+# Supplementary online analyses to *Internet and well-being* (Vuorre & Przybylski, 2022)
 
 <!-- Prepend table & figure numbers with S and reset counters -->
-<!-- \setcounter{page}{1} -->
-<!-- \setcounter{table}{0} -->
-<!-- \setcounter{figure}{0} -->
-<!-- \renewcommand{\thetable}{S\arabic{table}} -->
-<!-- \renewcommand{\thefigure}{S\arabic{figure}} -->
 
-<!-- ```{r include-only-for-pdf} -->
-<!-- #| include: !expr knitr::is_latex_output() -->
-<!-- ``` -->
+\setcounter{page}{1}
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+## Variable descriptions
+
+## Data availability
+
+Some variables are only collected during certain years
+
+```{r}
+#| label: eda-missingness
+#| include: true
+# Explore missingness in data
+library(naniar)
+dat %>% 
+  group_by(year) %>% 
+  summarise(
+    `Total rows` = n(),
+    across(c(income, starts_with("internet")), ~sum(!is.na(.)))
+  ) %>% 
+  mutate(
+    across(income:internet_phone, ~percent(./`Total rows`, .01)),
+    `Total rows` = number(`Total rows`, big.mark = ",")
+  ) %>% 
+  apa_table(
+    font_size = "scriptsize",
+    digits = 2,
+    caption = "Existing covariates over time.",
+    note = "Numbers indicate percentages of non-missing values."
+  )
+```
+
+## Correlation matrices
+
+Below, we show correlation matrices between the key variables separately for each year in the data.
+In addition to the correlation values, these matrices describe the (co-)occurrence of variables.
+Where cells in the matrices are empty, the correlation could not be estimated.
+This is typically due to those variables not existing in the same year.
+Sometimes there is no correlation between the internet variables because one is conditional on the other (e.g.
+internet home }} internet access)
+
+```{r include-only-for-pdf, results = 'asis'}
+#| label: eda-corr-matrix
+#| include: !expr knitr::is_latex_output()
+
+yearly_correlation_matrix <- function(year) {
+
+  dir.create("tmp/")
+  path <- str_glue("tmp/cormat-{year}.rds")
+  if (!file.exists(path)) {
+    x <- dat %>% 
+      filter(year == {{year}})
+    x <- x %>% 
+      select(
+        starts_with("internet"),
+        income, healthprob, relationship, 
+        laworder, foodshelter,
+        life_satisfaction, negative_experiences, positive_experiences, social_life,
+        starts_with("gwpi_")
+      ) %>% 
+      mutate(across(where(is.factor), ~as.numeric(.)-1)) %>% 
+      correlate()
+    saveRDS(x, path)
+  } else {x <- readRDS(path)}
+
+  y <- x %>% 
+    # shave() %>% 
+    fashion(na_print = "-") %>% 
+    as_tibble() %>% 
+    mutate(term = str_glue("{term} ({1:nrow(x)})"))
+  names(y) <- c(" ", 1:(ncol(y)-1))
+  y %>%   
+    apa_table(
+      font_size = "scriptsize",
+      placement = "h",
+      caption = str_glue("Year: {year}. Pearson correlations between key variables."),
+      note = str_glue("We used all pairwise-complete observations.")
+    )
+}
+x <- unique(dat$year) %>% 
+  map(~yearly_correlation_matrix(.x))
+unlist(x) %>% cat
+```

### 2022-12-13 ms.Rmd
Snapshot analyses

--- 2022-11-14 ms.Rmd
@@
 ---
-title: 'To be determined: Associations between internet use and well-being in gallup world poll data'
-shorttitle: tbd
-leftheader: tbd
+title: 'A multiverse analysis of the associations between internet use and well-being'
+shorttitle: Internet and well-being
+leftheader: Internet and well-being
 author: 
@@
     email: matti.vuorre@oii.ox.ac.uk
-    role:
-      - Concept
   - name: Andrew K. Przybylski
@@
     email: andy.przybylski@oii.ox.ac.uk
-    role:
-      - Concept
-
 affiliation:
@@
     institution: Oxford Internet Institute, University of Oxford
-
 authornote: |
@@
 
-abstract: |
-  We analyse GWP data to look at relation between internet use and well-being.
-
-keywords: words, key
-wordcount: "`r wordcountaddin:::word_count(filename = 'ms.Rmd')`"
+keywords: well-being, internet technology, technology effects
+wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
 bibliography: "references.bib"
 floatsintext: yes
-linenumbers: yes
+linenumbers: no
 draft: no
@@
 classoption: jou
+header-includes:
+  - |
+    \setlength{\parskip}{0pt}
+    \setlength\parindent{24pt}
 output: 
@@
     number_sections: false
+editor_options: 
+  chunk_output_type: console
 ---
 
-<!-- First a section of lots of EDA -->
-
-```{r setup, include = FALSE}
+```{r}
+#| label: setup
+#| include: false
 library(papaja)
@@
 library(knitr)
+library(lme4)
+library(ggh4x)
+library(emmeans)
+library(ggside)
+library(ggbeeswarm)
+library(broom.mixed)
+library(patchwork)
+library(ggdist)
 library(corrr)
@@
 opts_chunk$set(
-  include = FALSE
+  include = FALSE,
+  cache = TRUE,
+  dev = "ragg_png"
 )
@@
 if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
+CORES <- MAX_CORES - 2
+theme_set(
+  theme_linedraw(base_size = 9.6) +
+    theme(
+      strip.background = element_rect(fill = "gray90", color = "gray90"),
+      strip.text = element_text(color = "black", hjust = 0),
+      panel.grid = element_blank()
+    )
+)
+
+# Function to clean up variable names for plots and tables
+sanitize_labels <- function(x, pad7 = TRUE) {
+  # Make internet predictors look ok
+  x <- x %>% 
+    str_replace("_", " ") %>% 
+    str_to_sentence() %>% 
+    str_replace("Gwb", "GWBI")
+  if (pad7) x <- str_replace(x, "7", " 7 ")
+  x
+}
+
+# Function to print large numbers
+number2 <- function(x, ...) number(x, ..., big.mark = ',')
 ```
@@
 path <- "data-raw/gwp.rds"
+if (dir.exists("data-raw/gallup") & !file.exists(path)) {
 
@@
     life_satisfaction = c("WP16"),
-  negative_experiences = c("WP68", "WP69", "WP70", "WP71", "WP74"), # negative experiences
-  positive_experiences = c("WP60", "WP61", "WP63", "WP65", "WP67"), # positive experiences
-  loneliness = c("WP27", "WP10248"), # social life index, or inverse "loneliness"
-  law = c("WP112", "WP113", "WP117", "WP118"), # law and order index
-  foodshelter = c("WP40", "WP43"), # food and shelter index
-  # community basics index
-  communitybasics = c("WP91", "WP92", "WP94", "WP95", "WP98", "WP93", "WP97"), 
-  # financiallife = c("WP2319", "WP30", "WP31", "WP88"),
-  civicengagement = c("WP108", "WP109", "WP110"),
-  communityattachment = c("WP83", "WP85", "WP86"),
-  diversityindex = c("WP103", "WP105", "WP106"),
-  # Gallup-Sharecare Global Well-Being Index
-  gwpi_purpose = c("WP14442", "WP14443"),
-  gwpi_social = c("WP14444", "WP14445"),
-  gwpi_financial = c("WP14446", "WP14447"),
-  gwpi_community = c("WP14450", "WP14451"),
-  gwpi_physical = c("WP14448", "WP14449")
+    negative_experiences = c("WP68", "WP69", "WP70", "WP71", "WP74"),
+    positive_experiences = c("WP60", "WP61", "WP63", "WP65", "WP67"),
+    social_life = c("WP27", "WP10248"), 
+    laworder = c("WP112", "WP113", "WP117", "WP118"), 
+    foodshelter = c("WP40", "WP43"), 
+    gwb_purpose = c("WP14442", "WP14443"),
+    gwb_social = c("WP14444", "WP14445"),
+    gwb_physical = c("WP14448", "WP14449")
   )
 
-if (dir.exists("data-raw/gallup") & !file.exists(path)) {
   library(haven)
@@
     col_select = c(
-      WP5, # country
+      WGT,
+      WP5, 
       YEAR_CALENDAR,
-      WP1220, # age
-      WP1219, # sex
-      WP14, # urbanicity
-      INCOME_2, # Annual Household Income in International Dollars
-      WP16056, # internet access
-      WP39, # internet access at home
-      WP19544, # internet on your phone
-      WP15862, # internet used past 7 days
-      # outcomes, indices, etc
+      WP1220,
+      WP1219, 
+      WP3117,
+      WP23, 
+      WP1223, 
+      EMP_2010,
+      INCOME_2,
+      WP2319,
+      WP16056,
+      WP39,
+      WP19544,
+      WP15862,
       all_of(
@@
 
-  # Rename and recode demographics and predictors
+  # Replace values with labels DK and Refused to proper NAs
+  val_labels(dat)  # These are the current value labels
+  to_na <- function(x) {
+    na_values(x) <- val_labels(x)[c("(DK)", "(Refused)")]
+    x
+  }
+  dat <- dat %>% 
+    mutate(across(c(everything(), -WP1219, -WP1220, -EMP_2010, -WP3117), to_na))
+  na_values(dat$WP3117) <- val_labels(dat$WP3117)[c("(DK)", "(RF)")]
+  dat <- user_na_to_na(dat)
+  val_labels(dat)
+  str(dat)
+
   dat <- dat %>% 
     mutate(
-      country = as_factor(WP5),
+      country = fct_drop(as_factor(WP5)),
       year = as.integer(YEAR_CALENDAR),
-      age = na_if(as.numeric(WP1220), 100),
+      age = as.integer(ceiling(WP1220)),
       sex = factor(as_factor(WP1219), levels = c("Female", "Male")),
-      urban = factor(
-        as_factor(WP14),
-        levels = c(
-          "A rural area or on a farm", "A small town or village", 
-          "A suburb of a large city", "A large city"  
+      weight = WGT,
+      healthproblems = factor(as_factor(WP23), levels = c("No", "Yes")),
+      relationship = fct_collapse(
+        as_factor(dat$WP1223),
+        Single = c(
+          "Single/Never been married", 
+          "Separated", 
+          "Divorced", 
+          "Widowed"
         ),
-        labels = c("Rural", "Town", "Suburb", "City")
+        Relationship = c("Married", "Domestic partner")
       ),
       income = as.numeric(INCOME_2),
+      income_feeling = 4 - as.integer(WP2319),
+      education = as.numeric(WP3117),
+      work = EMP_2010,
       internet_access = factor(as_factor(WP16056), levels = c("No", "Yes")),
@@
 
-  # Recode items
-  # make (DK) and (Refused) NAs
-  # make values run from 0 (negative construct) to max (positive construct)
+  # Binary work
+  dat$work <- as_factor(dat$work)
+  count(dat, work)
+  dat$work <- fct_collapse(
+    dat$work, 
+    no = c("Unemployed", "Out of workforce"), 
+    yes = c(
+      "Employed full time for an employer", 
+      "Employed full time for self", 
+      "Employed part time do not want full time", 
+      "Employed part time want full time")
+  )
+  dat$work <- factor(dat$work, levels = c("no", "yes"), labels = c("No", "Yes"))
+
+  # Fix one of each 13yr and 101yr
+  dat$age <- if_else(dat$age < 15L, 15L, if_else(dat$age > 100L, 100L, dat$age))
+  summary(dat$age)
 
@@
     mutate(
-      # Law and order, Food and shelter, Community basics, Civic engagement, Community attachment, Diversity index
-      # 1: positive (various) 2: negative (various), 3:DK, 4:refuse
-      across(
-        all_of(as.character(unlist(ix[5:10]))), 
-        ~if_else(. %in% 3:4, as.integer(NaN), as.integer(2 - .))
+      # Law and order
+      WP112 = 2 - WP112,
+      WP113 = 2 - WP113,
+      WP117 = WP117 - 1,
+      WP118 = WP118 - 1,
+    ) %>% mutate(
+      laworder = rowMeans(
+        select(., WP112, WP113, WP117, WP118), na.rm = TRUE
       ),
+      # Food and shelter [note below], 
+      foodshelter = rowMeans(
+        select(., WP40, WP43), na.rm = TRUE
+      ) - 1,
       # GWPI items
-      # 1: disagree 5:agree, 8:DK 9:refused
-      across(
-        all_of(as.character(unlist(ix[11:15]))), 
-        ~if_else(. %in% 8:9, as.integer(NaN), as.integer(. - 1))
-      ),
+      gwb_purpose = (
+        rowMeans(select(., WP14442, WP14443), na.rm = TRUE) - 1
+      ) / 4,
+      gwb_social = (
+        rowMeans(select(., WP14444, WP14445), na.rm = TRUE) - 1
+      ) / 4,
+      gwb_physical = (
+        rowMeans(select(., WP14448, WP14449), na.rm = TRUE) - 1
+      ) / 4,
+      .keep = "unused"
     )
 
-  # Aggregate scales
-  for (i in 1:length(ix)) {
-    dat[[names(ix[i])]] <- rowMeans(
+  # Remove now unnecessary variables
+  glimpse(dat)
+  dat <- dat %>% 
     select(
-        dat, 
-        all_of(as.character(unlist(ix[i])))
-      ), 
-      na.rm = TRUE
+      -c(
+        WP16, WP40, WP43, 
+        WP112, WP113, WP117, 
+        WP118, WP1223, starts_with("WP1444")
       )
-  }
-
-  # Remove other scale items
-  dat <- dat %>% 
-    select(-all_of(as.character(unlist(ix[5:15]))))
+    )
 
@@
 dat <- read_rds(path)
+
+# A few dozen missing sex and age
+dat <- drop_na(dat, sex, age) %>% 
+  mutate(sex = fct_drop(sex))
+
+# Income logp1
+dat <- mutate(dat, income = log(income+1))
+
+# Count observations and take out years with small N
+# Summarise original values
+x_sum <- dat %>% 
+  group_by(year) %>% 
+  summarise(
+    n = n(),
+    countries = length(unique(country)),
+    across(c(starts_with("internet")), ~sum(!is.na(.)))
+  ) %>% 
+  mutate(
+    across(starts_with("internet"), ~ . / n)
+  ) 
+# Too little data in 2022, and poor internet value coverage in 2005
+dat <- filter(dat, between(year, 2006, 2021))
+
+# Create combined internet access variable
+dat <- dat %>% 
+  mutate(
+    internet_access = if_else(year < 2016, internet_home, internet_access)
+  ) %>% 
+  select(-internet_home)
+yr <- paste(range(dat$year), collapse = " to ")
 ```
@@
 ```{r}
-#| label: chord-diagram
-#| eval: false
-# Correlation
-library(circlize)
+#| label: multiverse-specifications
+dat2 <- dat %>% 
+  select(
+    country, year, 
+    age, sex, 
+    weight,
+    education, work,
+    healthproblems, relationship,
+    income,
+    starts_with("internet"),
+    starts_with("gwb"),
+    life_satisfaction, negative_experiences, 
+    positive_experiences, social_life
+  ) %>% 
+  drop_na(age) %>% 
+  mutate(
+    age = cut(
+      age, 
+      breaks = c(15, 25, 35, 45, 55, 65, 101), 
+      labels = c("15 to 24", "25 to 34", "35 to 44", "45 to 54", "55 to 64", "65 +"),
+      include.lowest = TRUE, right = FALSE
+    )
+  ) %>% 
+  group_by(country, year) %>% 
+  mutate(
+    # Center all covariates and predictors
+    across(
+      c(education, income),
+      ~. - mean(., na.rm = TRUE)
+    ),
+    across(
+      c(healthproblems, relationship, work, starts_with("internet")), 
+      ~((as.numeric(.)-1) - mean((as.numeric(.)-1), na.rm = TRUE))
+    )
+  ) %>% 
+  ungroup()
 
-x <- dat %>% 
-  select(-c(1:6, all_of(as.character(unlist(ix[1:4]))))) %>% 
-  mutate(across(starts_with("internet"), as.numeric)) %>% 
-  # correlate()
+#' Expand a vector of covariate names to all their combinations
+#'
+#' For example expand_covariate(c("age", "sex")) returns
+#' c("age", "sex", "age + sex", "1")
+#'
+#' @param covariate e.g. c("age", "sex")
+#'
+#' @return a character vector
+expand_covariate <- function(covariate) {
+  list(
+    "1",
+    do.call(
+      "c", 
+      map(seq_along(covariate), ~combn(covariate, .x, FUN = list))) %>%
+      map(~paste(.x, collapse = " + "))
+  ) %>%
+    unlist
+}
 
-x2 <- x %>% 
-  stretch() %>% 
-  drop_na(r) %>% 
+No <- function(formula, data) {
+  fit <- lmer(formula = formula, data = data, weights = rep(1, nrow(data)))
+  out <- tidy(fit, conf.int = TRUE)
+  bind_cols(out, n = nobs(fit))
+}
+Yes <- function(formula, data) {
+  fit <- lmer(formula = formula, data = data, weights = weight)
+  out <- tidy(fit, conf.int = TRUE)
+  bind_cols(out, n = nobs(fit))
+}
+No <- possibly(No, tibble(n = 0))
+Yes <- possibly(Yes, tibble(n = 0))
+
+specs <- expand_grid(
+  year = unique(dat2$year),
+  distinct(dat2, sex, age),
+  y = c(
+    "life_satisfaction",
+    "negative_experiences",
+    "positive_experiences",
+    "social_life",
+    "gwb_purpose", "gwb_social", "gwb_physical"
+  ),
+  x = c(
+    "internet_access",
+    "internet_past7days",
+    "internet_phone"
+  ),
+  covariate = c(
+    "healthproblems",
+    "relationship",
+    "education",
+    "work",
+    "income"
+  ) %>% expand_covariate(),
+  model = c("No", "Yes")
+) %>% 
   mutate(
-    across(x:y, ~str_replace(., "internet", "www"))
+    formula = str_glue("{y} ~ {x} + {covariate} + ({x} | country)")
   )
 
-x2 %>% 
-  chordDiagramFromDataFrame(
-    col = colorRamp2(
-      c(-1, 1), 
-      c("firebrick1", "dodgerblue1")
-      ),
-    transparency = 0.25
+# Subset the specs to things that exist in the data
+specs <- specs %>% 
+  filter(
+    !(x == "internet_phone" & year < 2017),  # Existed 2017 onwards
+    !(x == "internet_past7days" & year < 2015), # 2015 onwards
+    !(str_starts(y, "gwb_") & !between(year, 2013, 2015)) # only these years
   )
@@
 ```{r}
-x <- dat %>% 
-  filter(year == 2021) %>% 
-  select(
-    -c(
-      1:5, internet_access, internet_home, starts_with("gwpi"),
-      all_of(as.character(unlist(ix[1:4])))
+#| label: multiverse-run
+dir.create("tmp", FALSE)
+path <- "tmp/multiverse-lmer.rds"
+if (!file.exists(path)) {
+
+  library(furrr)
+  plan(multisession, workers = CORES)
+
+  # Pass these global objects to `future_pmap()`
+  opts <- furrr_options(
+    globals = list(dat2 = dat2, No = No, Yes = Yes),
+    packages = c("lme4", "purrr", "dplyr", "broom.mixed")
+  )
+
+  fits <- specs %>% 
+    mutate(
+      out = future_pmap(
+        list(model, formula, year, sex, age),
+        ~do.call(
+          what = ..1, 
+          args = list(
+            formula = ..2, 
+            data = filter(
+              dat2, 
+              year == ..3, 
+              sex == ..4, 
+              age == ..5
+            )
+          )
+        ),
+        .options = opts
       )
     ) %>% 
-  mutate(across(where(is.factor), ~as.numeric(.)-1)) %>% 
-  correlate(method = "spearman")
+    ungroup() %>% 
+    unnest(out)
 
-x %>% 
-  rename_with(~str_replace(., "internet", "net") %>% str_trunc(12, ellipsis = "")) %>% 
-  # rearrange() %>%
-  shave() %>% 
-  fashion() %>% 
-  as_tibble() %>% 
-  select(1:13) %>% 
-  kable(caption = "Correlations in 2021")
+  saveRDS(fits, path)
+} else {fits <- readRDS(path)}
+
+fits <- rename(fits, weights = model) %>% 
+  filter(n > 0)
+fits_gwb <- fits %>% filter(str_detect(y, "gwb_"))
+fits <- fits %>% filter(!str_detect(y, "gwb_"))
+
+# Counts for text
+n_specs_all <- nrow(specs) %>% number2()
+n_specs_main <- specs %>% 
+  filter(!str_detect(y, "gwb_")) %>% 
+  nrow() %>% 
+  number2()
+n_specs_gwb <- specs %>% 
+  filter(str_detect(y, "gwb_")) %>% 
+  nrow() %>% 
+  number2()
+
+mv <- fits %>% 
+  filter(term == x) %>% 
+  arrange(estimate, y) %>% 
+  group_by(y) %>% 
+  mutate(i = 1:n()) %>% 
+  ungroup() %>% 
+  mutate(sig = sign(conf.low) == sign(conf.high)) %>% 
+  mutate(
+    decision = case_when(
+      conf.low < 0 & conf.high < 0 ~ "Negative",
+      conf.low > 0 & conf.high > 0 ~ "Positive",
+      !sig ~ "Not significant"
+    ) %>% 
+      factor(levels = c("Negative", "Not significant", "Positive"))
+  )
+
+mvs <- mv %>% 
+  reframe(
+    estimate = quantile(estimate, probs = c(.25, .5, .75)), 
+    quantile = c(.25, .5, .75),
+    .by = c(y)
+  ) %>% 
+  pivot_wider(
+    names_from = quantile, 
+    values_from = estimate
+  )
+
+mvs <- mv %>% 
+  mutate(
+    decision = case_when(
+      conf.low < 0 & conf.high < 0 ~ "Negative",
+      conf.low > 0 & conf.high > 0 ~ "Positive",
+      !sig ~ "Not significant"
+    ) %>% 
+      factor(levels = c("Negative", "Not significant", "Positive"))
+  ) %>% 
+  summarise(p = n(), .by = c(y, decision)) %>% 
+  mutate(
+    p = p / sum(p), .by = y
+  ) %>% 
+  complete(y, decision, fill = list(p = 0)) %>% 
+  pivot_wider(names_from = decision, values_from = p) %>% 
+  left_join(mvs) %>% 
+  left_join(
+    summarise(mv, n = median(n), .by = y)
+  )
+
+mvs_all <- mv %>% 
+  mutate(
+    estimate = if_else(y == "negative_experiences", -1*estimate, estimate)
+  ) %>% 
+  reframe(
+    estimate = quantile(estimate, probs = c(.25, .5, .75)), 
+    quantile = c(.25, .5, .75),
+  ) %>% 
+  pivot_wider(
+    names_from = quantile, 
+    values_from = estimate
+  )
+
+mvs_all <- mv %>% 
+  mutate(
+    across(
+      c(estimate, conf.low, conf.high), 
+      ~if_else(y == "negative_experiences", -1*., .)
+    )
+  ) %>% 
+  mutate(
+    decision = case_when(
+      conf.low < 0 & conf.high < 0 ~ "Negative",
+      conf.low > 0 & conf.high > 0 ~ "Positive",
+      !sig ~ "Not significant"
+    ) %>% 
+      factor(levels = c("Negative", "Not significant", "Positive"))
+  ) %>% 
+  summarise(p = n(), .by = c(decision)) %>% 
+  mutate(
+    p = p / sum(p)
+  ) %>% 
+  complete(decision, fill = list(p = 0)) %>% 
+  pivot_wider(names_from = decision, values_from = p) %>% 
+  bind_cols(mvs_all) %>% 
+  bind_cols(
+    summarise(mv, n = median(n))
+  )
+mvs <- bind_rows(
+  mvs,
+  mutate(mvs_all, y = "Total")
+) %>% 
+  mutate(Outcome = sanitize_labels(y), N = n, .keep = "unused", .before = 1)
+rm(mvs_all)
+```
+
+---
+abstract: |
+  With the increasing global penetration of the internet, and technologies and platforms enabled by it, their potential effects on individuals' well-being remains hotly debated.
+On one hand, these technologies have enabled novel forms of commerce, education, and leisure; on the other, many are worried that their use might negatively affect individuals by, for example, displacing time spent on other healthy activities.
+Moreover, research findings on the effects of internet technologies on well-being have been mixed and, to date, inconclusive and of limited geographic and demographic scope.
+In the current work, we examined the extent to which having internet access, a smartphone, or being an active internet user affected seven well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals living in `r length(unique(dat$country))` countries.
+We first tested the extent to which well-being varied as a function of internet connectivity.
+Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being using a multiverse analysis over `r n_specs_all` plausible model and subgroup specifications.
+`r percent(mvs$Positive[5], .01)` of these specifications indicated that internet connectivity was associated with positive well-being, while only `r percent(mvs$Negative[5], .01)` indicated negative associations.
+---
+
+The increasing adoption and use of internet-enabled technologies and platforms has spurred debate about their potential effects on people's psychological well-being and functioning.
+However, even after considerable scientific attention, an understanding of the associations between internet technology use and well-being remains elusive, and results of scientific studies on this topic have been mixed.
+
+## Current study
+
+Our overarching aim was to estimate the extent to which internet access and use predicts psychological well-being in cross-sectional samples of `r number2(nrow(dat))` individuals from `r length(unique(dat$country))` countries between 2006 and 2021.
+We studied seven indicators of well-being; life satisfaction, the extent to which individuals experienced daily negative and positive experiences; two indicators of social well-being; physical well-being, and feelings of purpose.
+We investigated the extent to which having any access to the internet; having mobile internet; and having used internet in the past 7 days predicted those aspects of well-being.
+
+We first asked what was the average difference, among the whole sample, in well-being between those individuals who had access to or used the internet, and those who did not.
+That is, our first research question addressed the basic association between internet and well-being.
+
+Second, our aim was to identify the unique contributions that internet access and use might have on well-being, and whether those might vary between demographics or over time.
+To this end, we used a set of meaningful covariates to adjust our models with.
+
+# Methods
+
+We analysed data from the Gallup World Poll [@gallupWorldPollMethodology2022].
+Gallup World Poll (GWP) is a nationally representative (of each country's civilian, non-institutionalized, adult [15+] population) continuous annual survey of approximately 1,000 individuals from each of 164 countries, conducted from 2005 to 2022.
+Gallup conducts the surveys through one-hour interviews either face-to-face or via telephone, with questionnaires that are translated to the major conversational language of each country.
+For the GWP methodological details, see @gallupWorldPollMethodology2022.
+We used data from `r number2(nrow(dat))` individuals from 2006 to 2021.
+(There were only 5,001 respondents from three countries in 2022, so we did not analyse that year.)
+
+## Data availability
+
+We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
+All our code, and a simulated GWP dataset, is available at [DOI].
+We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database.
+
+## Internet access and use
+
+The key variables that we considered as predictors measured the respondents' access and use of the internet.
+From 2005 to 2021, GWP has surveyed these with four items with varying coverage over time.
+First, GWP measures internet access with *"Does your home have access to the internet?"* (2005 to 2015).
+Because the coverage of existing data for this variable was very low in 2005, we used this variable from 2006 to 2015, where the mean percentage of non-missing values was `r percent(mean(x_sum$internet_home[1:10]), .1)`.
+From 2016 to 2022, a similar question measured overall internet access with *"Do you have access to the internet in any way, whether on a mobile phone, a computer, or some other device?"* (mean coverage `r percent(mean(x_sum$internet_access[11:16]), .1)`).
+Because these two questions were so similar, and to extend the range of data coverage, we merged these two to one "internet access" variable.
+
+Second, GWP has asked about mobile internet access with *"Can your mobile phone be used to access the Internet?"* from 2017 to 2022 (mean coverage `r percent(mean(x_sum$internet_phone[12:16]), .1)`).
+Third, GWP has measured internet *use* with *"Have you used the internet in the past seven days, whether on a mobile phone, a computer, or some other device?"* from 2015 to 2022.
+However, due to poor coverage in 2015, we used this variable from 2016 to 2021 (mean coverage `r percent(mean(x_sum$internet_past7days[11:16]), .1)`).
+
+All of these items had binary "Yes"/"No" response options, and respondents were given the option to decline an answer or report that they didn't know. We coded the latter two as missing values.
+
+## Well-being outcomes
+
+We focused on eight measures of well-being, broadly defined, in the Gallup World Poll: Life satisfaction, negative and positive experiences, social life satisfaction.
+In addition to these four outcomes, which were included in the GWP from 2005 to 2022, we studied four indicators from the Gallup-Sharecare Global Well-being Index™ (GWPI), which is a "barometer of individuals perceptions of their own well-being".
+
+Life satisfaction was measured with a single item: *"Please imagine a ladder, with steps numbered from 0 at the bottom to 10 at the top.
+The top of the ladder represents the best possible life for you and the bottom of the ladder represents the worst possible life for you.
+On which step of the ladder would you say you personally feel you stand at this time?"*, and respondents chose a number from 0 to 10.
+We rescaled this item to range from 0 to 1.
+
+Negative and positive experiences are both measured through a set of five Yes/No items.
+For negative experiences, respondents answered the prompts *"Did you experience the following feelings during a lot of the day yesterday?
+How about physical pain / worry / sadness / stress / anger?"*.
+For positive experiences, the items were *"Did you feel well-rested yesterday?"*; *"Were you treated with respect all day yesterday?"*; *"Did you smile or laugh a lot yesterday?"*; *"Did you learn or do something interesting yesterday?*"; and *"Did you experience the following feelings during a lot of the day yesterday?
+How about enjoyment?"*.
+
+In addition, we included two variables intended to measure individuals' "social support structure and opportunities to make friends" (*"Someone in your life always encourages you to be healthy"* and *"Your friends and family give you positive energy every day"*).
+We included these items as a proxy for social well-being.
+While we recognize their potentially limited validity, we thought that, from the variables available, they best corresponded to the inverse of loneliness, an important and much-studied aspect of well-being in connection to digital technologies.
+
+In 2013 through 2015, the GWP database also included a (Gallup-Sharecare) Global Well-being Index™ (GWPI), which measured (among others) experiences of purpose (*"liking what one does each day and being motivated to achieve one’s goals"*); social well-being (*"having supportive relationships and love in your life"*); and physical well-being, from which we included the item *"In the last seven days, you have felt active and productive every day"*.
+The sense of purpose was measured with prompts *"You like what you do every day"* and *"You learn or do something interesting every day"*.
+All items included the prompt *"Thinking about your life in general, please rate your level of agreement with each of the following using a five-point scale, where 5 means you STRONGLY AGREE and 1 means you STRONGLY DISAGREE.
+You may choose any of the numbers 1, 2, 3, 4, or 5."* However, because the GWPI was measured only between 2013 and 2015, we present those results separately in the appendix.
+
+While these scales are not psychometrically validated, Gallup cites prominent scientists as having helped with their development (@gallupWorldPollMethodology2022, p.
+5).
+While we find that statement of dubious value, we believe that the extensive scope of the dataset, across both time and countries, makes these variables uniquely valuable objects of study.
+
+## Covariates
+
+Our intent in this study was to approach the independent contributions of internet access and use on well-being.
+To that end, we adjusted our models for plausible covariates that were available in the GWP.
+First, previous research has highlighted important differences between age groups and sexes in their levels of well-being and use of internet technologies, and associations between the two.
+We therefore conducted our analyses separately for each sex and age group.
+However, to reduce the computational complexity of our analyses, and because there are no strong a priori reasons to assume large differences between adjacent ages, we split the continuous age variable into eight categories (15 to 24, 25 to 34, 35 to 44, 45 to 54, 55 to 64, and 65 +).
+
+Second, internet platforms and technologies are not static but continuously developed in order to better serve their users, and to be more engaging.
+Because this has led to worries that their effects on individuals' well-being might change over time [@vuorreThereNoEvidence2021], we analysed the data separately for each year.
+
+Third, because individuals' levels of well-being and internet access (and use) are likely associated with multiple contextual factors, we chose a set of plausible covariates to adjust our models in an attempt to isolate the independent contributions of internet access and use on well-being.
+To that end, we used the respondent's income, educational, work, and relationship statuses, and whether or not they reported having health problems as covariates in our models.
+
+The GWP queries respondents' for their monthly household income in their local currencies.
+GWP used hot deck imputation for individuals who reported an income range (~15%) or who did not provide responses (~15%).
+GWP then converted those values to International Dollars using the World Bank's purchasing power parity conversion factor, with the intent of making income estimates comparable across all respondents and countries.
+In our analyses, we log-transformed income.
+The GWP coded each respondent's educational status to one of three categories: Elementary education or less (up to eight years of education), some secondary education (nine to 15 years), and tertiary (education beyond high school).
+We used this variable as a continuous predictor with values 0, 1, and 2.
+Since 2009, GWP measured work status with five levels related to the quantity of work, but we recoded this as a binary employed vs.
+not variable.
+Relationship status was measured with a question about marital status with six response options.
+We recoded this to a binary in relationship vs.
+not variable.
+Respondents also answered "Do you have any health problems that prevent you from doing any of the things people your age normally can do?" with a binary yes/no response format.
+
+## Multiverse analysis
+
+Our general data-analytic approach was a regression model predicting one outcome (e.g.
+life satisfaction) from an intercept, one predictor (e.g.
+overall internet access), and zero or more of the covariates discussed above.
+Where the outcome consisted of multiple items, we took the mean.
+We conducted models separately for each sex, age group, and year.
+Because the data for each year, sex, and age was nested within countries, we specified a multilevel model where the intercept and coefficient of the internet predictor varied randomly over countries.
+For well-being outcome $y$ and internet predictor $x$, the model was
+
+\begin{align*} 
+y_i &\sim \text{Normal}(\mu_i, \sigma^{2}), \\
+\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} +
+  (\alpha_{1} + \beta_{1\text{country}[i]})x_i
+  \dots, \\
+\begin{bmatrix} 
+\beta_0 \\ \beta_1 
+\end{bmatrix} 
+& \sim\text{Normal}\left(
+  \begin{bmatrix}
+  0 \\ 0 
+  \end{bmatrix}, 
+  \begin{bmatrix} 
+  \sigma_{\beta_0}^2 & \\ \sigma_{\beta_0\beta_1} & \sigma_{\beta_1}^2 
+  \end{bmatrix} 
+\right).
+\end{align*}
+
+In the above, $i$ indexes rows in the data, and $j$ indicates one of the 164 countries.
+We wrote $\dots$ to represent a particular combination of the covariates (including none), of which there were 32.
+In addition to the model specifications, GWP recommends using model weights to adjust for demographic representativeness in some analyses, and so we conducted the analyses both with and without model weights.
+
+Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariates, and whether model weights were included or not, leading to `r number2(n_specs_all)` specifications.
+However, because not all combinations were possible (e.g.
+mobile internet access did not exist before 2017), our final multiverse consisted of `r number2(n_specs)` specifications.
+We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses.
+
+# Results
+
+```{r}
+path <- "tmp/fits-lmer-total.rds"
+if (!file.exists(path)) {
+
+  library(furrr)
+  plan(multisession, workers = 8)
+
+  # Pass these global objects to `future_pmap()`
+  opts <- furrr_options(
+    globals = list(dat2 = dat2, No = No),
+    packages = c("lme4", "purrr", "dplyr", "broom.mixed")
+  )
+
+  fits_avg <- expand_grid(
+    y = c(
+      "life_satisfaction",
+      "negative_experiences",
+      "positive_experiences",
+      "social_life",
+      "gwb_purpose", "gwb_social", "gwb_physical"
+    ),
+    x = c(
+      "internet_access",
+      "internet_past7days",
+      "internet_phone"
+    )
+  ) %>% 
+    mutate(
+      model = "No",
+      formula = str_glue("{y} ~ {x} + ({x} | country)")
+    ) %>% 
+    mutate(
+      out = future_pmap(
+        list(model, formula),
+        ~do.call(
+          what = ..1, 
+          args = list(
+            formula = ..2, 
+            data = dat2
+          )
+        ),
+        .options = opts
+      )
+    ) %>% 
+    ungroup() %>% 
+    unnest(out)
+
+  fits_avg <- fits_avg %>% 
+    filter(term == x) %>% 
+    select(-c(effect, group, term, model, formula))
+
+  saveRDS(fits_avg, path)
+} else {fits_avg <- readRDS(path)}
+
+# Median association (with reversed negative experiences)
+tmp <- fits_avg %>% 
+  mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
+  summarise(across(c(estimate, std.error), median))
+```
+
+Before conducting our full multiverse analysis, we addressed our first research question concerning the overall associations between internet access and use, and well-being.
+To do so, we regressed each outcome on each predictor with the multilevel model described above, but without using covariates or weights, and using all available data without partitioning it by sex, age, or time.
+
+```{r}
+#| label: fig-rq1
+#| include: true
+#| fig.height: 5.4
+#| fig.cap: Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences.
+Small points are countries' means, and solid colored points and lines are means of the countries' means.
+Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\% confidence interval.
+
+tmp1 <- dat %>% 
+  pivot_longer(starts_with("internet")) %>% 
+  drop_na(value) %>%
+  group_by(country, name, value) %>% 
+  summarise(
+    across(
+      c(life_satisfaction:social_life), 
+      ~mean(., na.rm = TRUE)
+    ),
+  ) %>% 
+  ungroup() %>% 
+  pivot_longer(contains("_"), names_to = "outcome", values_to = "y") %>% 
+  filter(!(name == "internet_phone" & str_detect(outcome, "gwb_"))) %>% 
+  pivot_wider(names_from = value, values_from = y) %>% 
+  mutate(z = Yes - No) %>% 
+  pivot_longer(c(No, Yes, z), names_to = "x")
+
+tmp2 <- tmp1 %>% 
+  group_by(name, outcome, x) %>% 
+  summarise(m = mean_cl_boot(value, conf.int = 0.95)) %>% 
+  ungroup() %>% 
+  unnest(m) %>% 
+  mutate(sig = sign(ymin) == sign(ymax)) %>% 
+  mutate(
+    decision = case_when(
+      ymin < 0 & ymax < 0 ~ "Negative",
+      ymin > 0 & ymax > 0 ~ "Positive",
+      !sig ~ "Not significant"
+    ) %>% 
+      factor(levels = c("Negative", "Not significant", "Positive")) %>% 
+      fct_drop()
+  )
+
+tmp1 %>% 
+  ggplot(aes(x, value)) +
+  scale_color_brewer(
+    "Difference",
+    palette = "Set1"
+  ) +
+  scale_y_continuous(
+    "Well-being mean",
+    breaks = extended_breaks(7),
+    expand = expansion(.1)
+  ) +
+  scale_x_discrete(
+    "Internet",
+    expand = expansion(0.4),
+    labels = ~str_replace(., "z", "Y-N")
+  ) +
+  geom_hline(yintercept = 0, linewidth = .1) +
+  geom_line(
+    data = . %>% filter(x != "z"),
+    aes(group = country),
+    linewidth = .1, alpha = .5, col = "gray70",
+    position = position_quasirandom(width = .45)
+  ) +
+  geom_point(
+    alpha = .55, size = .8, shape = 1, stroke = .33, 
+    col = "gray70", fill = "white",
+    position = position_quasirandom(width = .45)
+  ) +
+  geom_pointrange(
+    data = tmp2 %>% filter(x %in% c("No", "Yes")),
+    aes(y = y, ymin = ymin, ymax = ymax),
+    size = 0.5, fatten = 1.8
+  ) +
+  geom_pointrange(
+    data = tmp2 %>% filter(!(x %in% c("No", "Yes"))),
+    aes(y = y, ymin = ymin, ymax = ymax, color = decision),
+    size = 0.5, fatten = 1.5
+  ) +
+  geom_line(
+    data = tmp2 %>% filter(x %in% c("No", "Yes")),
+    aes(y = y),
+    linewidth = .33,
+    group = 1,
+    show.legend = FALSE
+  ) +
+  geom_label(
+    data = fits_avg %>% 
+      filter(!str_detect(y, "gwb_")) %>% 
+      mutate(
+        across(c(where(is.numeric), -n), ~number(., .001)),
+        n = number2(n),
+        name = x, x = "No", outcome = y
+        ),
+    aes(
+      label = str_glue("b = {estimate}\n[{conf.low}, {conf.high}]")
+    ),
+    x = -Inf, y = -Inf, 
+    size = 2.7, hjust = 0, vjust = 0, lineheight = 1, fill = NA,
+    label.size = 0, label.padding = unit(0.5, "line")
+  ) +
+  facet_grid(
+    name ~ outcome, 
+    labeller = as_labeller(~sanitize_labels(.))
+  ) +
+  theme(
+    legend.position = "bottom"
+  )
 ```
@@
 ```{r}
-#| label: eda-missingness
-#| eval: false
-# Explore missingness in data
-library(naniar)
-dat %>% 
-  group_by(year) %>% 
+tmp1 <- dat %>% 
+  pivot_longer(starts_with("internet")) %>% 
+  drop_na(value) %>%
+  group_by(country, year, name, value) %>% 
   summarise(
-    `Total rows` = n(),
-    across(c(income, urban, starts_with("internet")), ~sum(!is.na(.)))
+    across(
+      c(life_satisfaction:social_life), 
+      ~mean(., na.rm = TRUE)
+    ),
+  ) %>% 
+  ungroup() %>% 
+  pivot_longer(contains("_"), names_to = "outcome", values_to = "y") %>% 
+  filter(!(name == "internet_phone" & str_detect(outcome, "gwb_"))) %>% 
+  pivot_wider(names_from = value, values_from = y) %>% 
+  mutate(z = Yes - No) %>% 
+  pivot_longer(c(No, Yes, z), names_to = "x")
+
+tmp2 <- tmp1 %>% 
+  group_by(year, name, outcome, x) %>% 
+  summarise(m = mean_cl_boot(value, conf.int = 0.95)) %>% 
+  ungroup() %>% 
+  unnest(m) %>% 
+  mutate(sig = sign(ymin) == sign(ymax)) %>% 
+  mutate(
+    decision = case_when(
+      ymin < 0 & ymax < 0 ~ "Negative",
+      ymin > 0 & ymax > 0 ~ "Positive",
+      !sig ~ "Not significant"
+    ) %>% 
+      factor(levels = c("Negative", "Not significant", "Positive")) %>% 
+      fct_drop()
+  )
+tmp2 %>% 
+  filter(x == "z") %>% 
+  ggplot(aes(year, y)) +
+  coord_cartesian(ylim = c(-0.2, 0.25)) +
+  geom_hline(yintercept = 0, linewidth = .1) +
+  geom_line(
+    data = tmp1 %>% filter(x == "z"),
+    aes(y = value, group = country),
+    alpha = .1, color = "grey60"
+  ) +
+  geom_ribbon(
+    aes(ymin = ymin, ymax = ymax),
+    alpha = .33
+  ) +
+  geom_line() +
+  facet_grid(
+    name ~ outcome, 
+    labeller = as_labeller(~sanitize_labels(.))
+  )
+```
+
+The overall association between internet access and use and well-being was consistently positive (Figure \@ref(fig:fig-rq1)).
+On average, across the three internet predictors and four well-being outcomes, individuals who had access to (or used) the internet reported (median) `r number(tmp$estimate, .01)` units (median SE: `r number(tmp$std.error, .001)`) greater well-being than those who did not (we reversed the coefficients for negative experiences for these aggregate numbers).
+Figure \@ref(fig:fig-rq1) shows these data aggregated for each country, and the spread across countries of differences between people who had access to (or used) the internet and who didn't.
+These results showed, uniformly across the four well-being outcomes, that individuals who had access to, or actively used, the internet reported greater well-being than those who did not.
+
+```{r}
+#| label: tbl-multiverse
+#| include: true
+out_sum_2 <- out_sum_2 %>% 
+  mutate(
+    N = number2(N, 1),
+    across(c(Negative, `Not significant`, Positive), ~percent(., .01)),
+    across(c(`0.25`, `0.5`, `0.75`), ~number(., .01))
   ) %>% 
   mutate(
-    across(income:internet_phone, ~./`Total rows`),
-    `Total rows` = number(`Total rows`, big.mark = ",")
-  ) %>% 
-  kable(
-    digits = 2, 
-    caption = "Existing covariates over time in GWP data"
+    Median = `0.5`,
+    IQR = str_glue("[{`0.25`}, {`0.75`}]"),
+    .keep = "unused",
+    .after = 2
+  )
+out_sum_2 %>%   
+  apa_table(
+    caption = "Summary of multiverse analysis of associations between internet access (or use) and well-being.", 
+    note = 'N is the median sample size across specifications.
+"Total" indicates quantities across well-being outcomes (we reversed associations with negative experiences for this aggregate number).',
+    col_spanners = list(
+      "Association magnitude" = c(3, 4),
+      "Proportions of significant associations" = c(5, 7)
+    ), 
+    placement = "ht"
+  )
+```
+
+However, although the estimates in Figure \@ref(fig:fig-rq1) were surprisingly uniform across outcomes and predictors, they did not yet address our second, main research question: The extent to which internet access and use might independently contribute to individuals' well-being.
+To best do so, while at the same time incorporate uncertainty in how, where, or for whom to study this association, we next turned to the multiverse analysis.
+In this analysis, we examined the association between well-being and internet use over `r number2(n_specs)` model specifications (and an additional `r number2(n_specs_gwb)` specifications for the GWBI outcomes in the appendix).
+
+We show the average results of this multiverse analysis in Table \@ref(tab:tbl-multiverse).
+First, for life satisfaction, the median sample size across specifications was `r out_sum_2$N[[1]]`.
+On average, answering 'Yes' to an internet access or use question was associated with a `r out_sum_2$Median[[1]]` unit increase in life satisfaction, with the central 50% of associations lying in the `r out_sum_2$IQR[[1]]` interval.
+`r out_sum_2$Positive[[1]]` of the estimated associations were positive.
+Numerical results for the other three well-being outcomes were consistent, and the total proportion of specifications that resulted in negative associations was only `r out_sum_2$Negative[[5]]`.
+
+Figure \@ref(fig:fig-multiverse) shows that across all model specifications, the multilevel model's estimated association between internet access and use, for the average country, was very consistently positive.
+Each vertical slice of figure \@ref(fig:fig-multiverse) identifies a model specification, indexed on the x-axis.
+For example, one point could represent the association between internet access (X = Internet access in panel B) for males aged 65 or over (Age), with a model that included only an intercept (Covariates = 1) as additional covariates, in the year 2019, for a model estimated without weights (No weights).
+
+```{r}
+#| include: true
+#| label: fig-multiverse
+#| out.width: "\\textwidth"
+#| fig.env: "figure*"
+#| fig.height: 7.6
+#| fig.width: 9
+#| fig.cap: Multiverse analysis results of associations between three internet use predictors and four well-being outcomes.
+A.
+Estimated associations, in order of increasing magnitude, shown separately for each of the four main well-being outcomes.
+The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point.
+B.
+A dashboard of model specifications.
+Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
+
+p1 <- out %>% 
+  ggplot(aes(i, estimate, col = decision)) +
+  scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
+  scale_y_continuous(position = "right",
+    "Estimated association (95%CI)",
+    breaks = extended_breaks(7)
+  ) +
+  scale_x_continuous(
+    "Analysis specification (in order of association magnitude)",
+    breaks = extended_breaks(5),
+    expand = expansion(.015)
+  ) +
+  geom_hline(yintercept = 0, linewidth = .1) +
+  geom_point(size = .25) +
+  geom_linerange(
+    aes(ymin = conf.low, ymax = conf.high),
+    linewidth = .2, alpha = .2
+  ) +
+  geom_ysidedensity(
+    aes(x = after_stat(ndensity)), 
+    col = "grey20", fill = "grey60", alpha = .4, n = 3001
+  ) +
+  geom_ysidepoint(
+    data = out_sum %>% 
+      # Just for coloring the dot
+      mutate(
+        decision = cut(
+          `0.5`, 
+          breaks = c(-1, -.0001, .0001, 1), 
+          labels = levels(out$decision)
+        )
+      ),
+    aes(y = `0.5`, x = 0),
+    size = 2, position = position_nudge(x = .025)
+  ) +
+  scale_ysidex_continuous(expand = expansion(c(0, .2))) +
+  facet_wrap(
+    "y", 
+    scales = "free_x", 
+    nrow = 1, 
+    drop = TRUE,
+    labeller = as_labeller(sanitize_labels)
+    ) +
+  theme(
+    axis.title.x = element_blank(),
+    legend.position = "none",
+    ggside.panel.scale = 0.1,
+    ggside.panel.spacing.x = unit(0, "pt"),
+    ggside.axis.text = element_blank(),
+    ggside.axis.ticks = element_blank()
   )
 
-dat %>% 
-  group_by(year, country) %>% 
-  summarise(
-    across(
-      starts_with("internet"),
-      .fns = list(total = ~n(), missing = ~sum(is.na(.))), 
-      .names = "{.col}.{.fn}"
+p2 <- out %>% 
+  mutate(
+    weights = factor(
+      weights, 
+      levels = c("No", "Yes"), 
+      labels = c("No weights", "Weights"))
+  ) %>% 
+  pivot_longer(
+    c(year, age, sex, x, covariate, weights), 
+    values_transform = as.character
+  ) %>%
+  mutate(
+    name = factor(
+      name, 
+      levels = c("x", "age", "sex", "covariate", "year", "weights"),
+      labels = c("X", "Age", " ", "Covariates", "Year", "  ")
+    ),
+    value = fct_relevel(value, unique(specs$covariate)),
+    value = fct_recode(value, `No covariates` = "1")
+  ) %>% 
+  ggplot(aes(i, value, col = decision)) +
+  scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
+  scale_y_discrete(
+    position = "right",
+    labels = ~sanitize_labels(., FALSE)
+  ) +
+  scale_x_continuous(
+    "Analysis specification (ordered by increasing magnitude of association)",
+    breaks = extended_breaks(5),
+    expand = expansion(.01)
+  ) +
+  geom_point(shape = 20, size = .2) +
+  facet_grid(
+    cols = vars(y),
+    rows = vars(name), 
+    scales = "free_y", 
+    space = "free_y", 
+    switch = "y", 
+    drop = TRUE,
+    labeller = as_labeller(sanitize_labels)
+  ) +
+  theme(
+    axis.text.y = element_text(size = rel(0.6)),
+    axis.title.y = element_blank(),
+    # axis.text.x = element_blank(),
+    legend.position = "none"
   )
+
+((p1 / p2) +
+  plot_layout(heights = c(3.6, 6.4))) +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r}
+#| include: true
+#| label: fig-multiverse-zoom
+#| out.width: "\\textwidth"
+#| fig.env: "figure*"
+#| fig.cap: Median associations between the internet predictors and well-being outcomes by sex and age, ordered by covariate specification.
+The specifications are ordered as in Figure 2; where greater numbers indicate more covariates in the model.
+p1 <- fits %>% 
+  filter(term == x) %>% 
+  reframe(
+    q = c(.1, .5, .9),
+    value = quantile(estimate, probs = c(.1, .5, .9)),
+    .by = c(covariate, age, sex, x, y)
+  ) %>% 
+  pivot_wider(names_from = q) %>% 
+  mutate(
+    covariate = fct_relevel(covariate, unique(specs$covariate)),
+    i = as.numeric(covariate)
+  ) %>%
+  ggplot(aes(i, `0.5`)) +
+  geom_hline(yintercept = 0, size = .1) +
+  scale_color_viridis_d(
+    "Age"
+  ) +
+  scale_y_continuous(
+    "Median association"
+  ) +
+  scale_x_continuous(
+    "Covariate specification"
+  ) +
+  geom_line(aes(group = age, col = age)) +
+  facet_nested(
+    x + sex ~ y,
+    labeller = as_labeller(sanitize_labels)
+  )
+
+p1
+```
+
+```{r}
+fits %>% 
+  filter(term == x) %>% 
+  reframe(
+    q = c(.1, .5, .9),
+    value = quantile(estimate, probs = c(.1, .5, .9)),
+    .by = c(covariate, age, x, y)
+  ) %>% 
+  pivot_wider(names_from = q) %>% 
+  mutate(
+    covariate = fct_relevel(covariate, unique(specs$covariate)),
+    covariate = fct_recode(covariate, `No covariates` = "1")
+  ) %>%
+  ggplot(aes(`0.5`, covariate, col = age)) +
+  geom_vline(xintercept = 0, size = .1) +
+  scale_color_brewer(palette = "Set1") +
+  scale_x_continuous(
+    "Estimated association"
+  ) +
+  ggstance::geom_pointrangeh(
+    aes(xmin = `0.1`, xmax = `0.9`),
+    size = .1, fatten = 0.25,
+    position = position_dodge(width = 1)
+  ) +
+  facet_nested(
+    x ~ y,
+    labeller = as_labeller(sanitize_labels)
+  )
+```
+
+```{r}
+#| eval: false
+library(ggstance)
+library(ggh4x)
+fits %>% 
+  drop_na(age, sex) %>% 
+  filter(
+    covariate %in% c("1", "healthproblems + income"),
+    !str_detect(y, "gwb"),
+    year %% 2 == 1,
+    year >= 2015
   ) %>% 
   ungroup() %>% 
-  pivot_longer(-c(year, country)) %>% 
-  separate(name, c("x", "y"), sep = "\\.") %>% 
-  pivot_wider(values_from = value, names_from = y) %>% 
-  filter(country %in% sample(unique(dat$country), 25)) %>%
-  ggplot(aes(year, missing/total, col = x)) +
-  geom_line() +
-  facet_wrap("country") +
-  theme(legend.position = "bottom")
-
-# Cross-missingness
-dat %>% 
-  filter(year == 2019) %>% 
-  select(income, urban, starts_with("internet")) %>% 
-  naniar::as_shadow() %>% 
-  rename_with(~str_remove(., "internet_") %>% str_remove("_NA")) %>% 
-  mutate(across(everything(), as.numeric)) %>% 
-  cor(method = "spearman") %>% 
-  kable(digits = 2)
+  mutate(
+    sig = sign(conf.low) == sign(conf.high),
+    covariate = factor(
+      covariate, labels = c("No covariates", "Income and health problems")
+    ),
+    color = str_glue("{sex}\n{covariate}")
+  ) %>% 
+  arrange(sex, covariate) %>% 
+  mutate(color = fct_inorder(color)) %>% 
+  ggplot(aes(year, estimate, col = color)) +
+  scale_color_manual(
+    "Model covariates",
+    values = c("firebrick1", "firebrick4", "dodgerblue1", "dodgerblue4")
+  ) +
+  scale_shape_manual(values = c(21, 19)) +
+  scale_y_continuous(
+    "Estimated association (95%CI)",
+    labels = ~percent(., 1)
+  ) +
+  scale_x_continuous(
+    "Year",
+    breaks = c(2015, 2017, 2019, 2021),
+    labels = ~str_glue("'{str_sub(., 3, 4)}")
+  ) +
+  geom_hline(yintercept = 0, linewidth = .1) +
+  geom_pointrange(
+    aes(ymin = conf.low, ymax = conf.high, shape = sig),
+    position = position_dodge2(1),
+    fatten = 2.5, fill = "white", stroke = .8
+  ) +
+  guides(shape = "none") +
+  facet_nested(
+    age ~ y + x, scales = "free_x",
+    labeller = as_labeller(sanitize_labels)
+  ) +
+  theme(
+    legend.position = "bottom", 
+    legend.title = element_blank()
+  )
 ```
 
-# Methods
+# Discussion
 
-Gallup world poll is a dataset that has data.
+The debate over internet platforms' and technologies' effects on individuals' psychological well-being remains a central topic because of their potentially global consequences.
+While past results on this topic have been mixed, the overwhelming majority of studies have examined convenience samples from the global north, thereby ignoring the fact that the penetration of the internet has been a global phenomenon.
+In this study, we examined associations between internet use and access, and a broad variety of well-being indicators in a representative sample of `r number2(nrow(dat))` individuals across `r length(unique(dat$country))` countries within an age range that spanned from late adolescence to older adults.
+We found that on average across countries and demographics, individuals who had internet access, mobile internet access, or actively used the internet reported greater levels of life satisfaction, positive experiences, and social well-being, and lower levels of negative experiences.
 
-## Internet engagement
+The main thrust of our analysis was to examine to what extent this positive association between internet and well-being was sensitive to different demographic groups, time periods, and modelling decisions.
+Furthermore, we attempted to estimate the unique contributions of internet on well-being by examining this association across `r length(unique(specs$covariate))` different permutations of sets of plausible covariates that might otherwise create or mask associations.
+Across `r number2(nrow(filter(fits, term == x)))` of such model specifications, `r out_sum_2$Positive[5]` of the associations were significantly positive, and only `r out_sum_2$Negative[5]` were negative.
+We thus conclude that the proliferation of (mobile) internet access and increasing engagement with the internet has been a net benefit to the well-being of individuals around the world.
 
-- "Communications Access Index"
-  - [WP39]: Does your home have access to the internet? 
-  - [WP16056]: Do you have access to the internet in any way, whether on a mobile phone, a computer, or some other device?
-    1 Yes
-    2 No
-    3 (DK)
-    4 (Refused)
-- "Communications Use Index"
-  - [WP15862]: Have you used the internet in the past seven days, whether on a mobile phone, a computer, or some other device?
-    1 Yes
-    2 No
-    3 (DK)
-    4 (Refused)
-- In "Appendix A: 2021 Core Questions and Codes"
-  - [WP19544]: Can your mobile phone be used to access the Internet?
-    1 Yes
-    2 No
-    3 (DK)
-    4 (Refused)
+Nevertheless, our conclusion is qualified by a number of factors.
+First, we compared individuals to each other.
+There are likely myriad other features about the human condition that are associated with both uptake of internet technologies and well-being in such a manner that they might cause positive associations to be observed.
+While we attempted to adjust for such features by including various covariates in our models, the data and theory to guide model selection were both limited.
 
-## Data analysis
+Second, while between-person data such as we studied can inform inferences about average causal effects, longitudinal studies that track individuals and their internet use over time would be more informative in understanding the contexts of how and why an individual is affected by the internet [@rohrerTheseAreNot2021].
 
-We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses.
+Third, while the constructs that we studied represent the general gamut of well-being outcomes that are typically studied in connection to digital media and technology, they do not capture everything, nor are they standard and methodically validated measures otherwise found in the psychological literature.
+That is, the GWP data that we used represent a uniquely valuable resource in terms of its scope both over time and space.
+But the measurement quality of its items and scales might not be sufficient to capture the targeted constructs in the detailed manner that we would hope for.
+It is therefore possible that there are other features of well-being that are differently affected by internet technologies, and that our estimates might be noisier than would be found using psychometrically validated instruments.
 
-\clearpage
+Fourth, the validity of self-reported measures of technology engagement is found lacking, as self-reported quantities of use correlate only modestly with actual use, as measured for example by apps installed on smartphones.
+In our study, we used reports of whether an individual has access to or has used the internet in the past week.
+Nevertheless, we believe it is more difficult to be mistaken in answering those questions than it would be if answering questions about e.g.
+average hours used in the past year.
+
+To overcome these limitations, we think the best way forward for this field is the expend more resources on collecting larger and more representative longitudinal datasets that include validated measurements of the constructs that researchers care about.
+In addition, these datasets should include accurate data on individuals' engagement with the internet in lieu of self-reports.
+Fortunately, both of these data are already collected; large cohort-based surveys in many countries already track individuals' psychological states over time, and internet platforms are infamous for collecting detailed data on their users' behaviors.
+A significant but potentially fruitful challenge then would be to marry those two streams of data for a more detailed understanding of internet technologies in individuals' lives.
+
+# Author contributions
+
+Conceptualization: MV & AKP; Data curation: MV; Formal Analysis: MV; Funding acquisition: AKP; Investigation: MV & AKP; Methodology: MV & AKP; Project administration MV & AKP; Resources: AKP; Software: MV; Supervision: AKP; Visualization: MV & AKP; Writing – original draft: MV & AKP; Writing – review & editing: MV & AKP.
 
@@
 
-<!-- Create an appendix with new page, table, and figure numbers. -->
+\clearpage
+\onecolumn
 
-<!-- \clearpage -->
-<!-- \onecolumn -->
-
-<!-- # Supplementary online material to Title (Authors) -->
+# Supplementary online analyses to *Internet and well-being* (Vuorre & Przybylski, 2022)
 
 <!-- Prepend table & figure numbers with S and reset counters -->
-<!-- \setcounter{page}{1} -->
-<!-- \setcounter{table}{0} -->
-<!-- \setcounter{figure}{0} -->
-<!-- \renewcommand{\thetable}{S\arabic{table}} -->
-<!-- \renewcommand{\thefigure}{S\arabic{figure}} -->
 
-<!-- ```{r include-only-for-pdf} -->
-<!-- #| include: !expr knitr::is_latex_output() -->
-<!-- ``` -->
+\setcounter{page}{1}
+\setcounter{table}{0}
+\setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
+Table \@ref(tab:tbl-correlation-matrix) shows the pearson correlations between all variables, across demographics, time and space.
+
+```{r}
+#| label: tbl-correlation-matrix
+#| include: true
+x <- dat %>% 
+  # filter(year > 2013) %>% 
+  select(
+    starts_with("internet"),
+    income, healthproblems, relationship, 
+    laworder, foodshelter,
+    life_satisfaction, negative_experiences, positive_experiences, social_life,
+    starts_with("gwb_")
+  ) %>% 
+  mutate(across(where(is.factor), ~as.numeric(.)-1)) %>% 
+  correlate()
+y <- x %>% 
+  # shave() %>% 
+  fashion(na_print = " ") %>% 
+  as_tibble() %>% 
+  mutate(term = str_glue("{term} ({1:nrow(x)})")) %>% 
+  mutate(term = sanitize_labels(term, FALSE))
+  names(y) <- c(" ", 1:(ncol(y)-1))
+  y %>%   
+    apa_table(
+      font_size = "scriptsize",
+      placement = "h",
+      caption = "Pearson correlations between key variables.",
+      note = "We used all pairwise-complete observations."
+    )
+```
+
+```{r}
+#| label: fig-summary
+#| include: true
+#| fig.height: 6.5
+#| fig.cap: Key variables' averages and availability over time.
+A.
+Internet access and use variables.
+B.
+Covariates, excluding income because it is on a different scale.
+C.
+Well-being outcomes, excluding the GWB indices, because they were only collected in 2013 to 2015.
+
+# Figure
+tmp <- dat %>% 
+  select(
+    year, starts_with("internet"),
+    life_satisfaction, negative_experiences, 
+    positive_experiences, social_life, 
+    healthproblems, laworder, relationship
+  ) %>% 
+  mutate(across(c(where(is.factor)), ~as.numeric(.)-1)) %>% 
+  group_by(year) %>% 
+  summarise(
+    across(
+      everything(), 
+      list(valid = ~sum(!is.na(.)) / n(), mean = ~mean(., na.rm = TRUE)), 
+      .names = "{.col}.{.fn}"
+    )
+  ) %>% 
+  mutate(across(ends_with("valid"), ~if_else(. < 0.1, NaN, .))) %>% 
+  pivot_longer(-c(year)) %>% 
+  separate(name, c("variable", "measure"), sep = "\\.") %>% 
+  mutate(
+    group = case_when(
+      str_detect(variable, "internet") ~ "A",
+      variable %in% 
+        c("income", "healthproblems", "relationship", "laworder") ~ "B",
+      TRUE ~ "C"
+    )
+  )
+
+p1 <- tmp %>% 
+  ggplot(aes(year, value, col = measure)) +
+  scale_color_brewer(
+    "Variable",
+    palette = "Dark2",
+    labels = ~factor(., levels = c("mean", "valid"), labels = c("Mean response", "Valid responses"))
+  ) +
+  scale_y_continuous(
+    limits = 0:1,
+    expand = expansion(c(0.03, 0.06)),
+    labels = ~percent(., 1)
+  ) +
+  scale_x_continuous(
+    "Year",
+    breaks = extended_breaks(5)
+  ) +
+  geom_line(linewidth = 0.8) +
+  # geom_point() +
+  facet_wrap(
+    "variable", 
+    scales = "free_x",
+    labeller = as_labeller(sanitize_labels),
+    nrow = 1
+  ) +
+  theme(
+    axis.title.y = element_blank(),
+    legend.position = "bottom", 
+    legend.title = element_blank()
+  )
+
+p2 <- (p1 %+% filter(p1$data, group == "A")) + 
+  theme(
+    legend.position = "none",
+    axis.title.x = element_blank()
+  )
+p3 <- (p1 %+% filter(p1$data, group == "B")) +
+  theme(
+    legend.position = "none",
+    axis.title.x = element_blank()
+  )
+p4 <- (p1 %+% filter(p1$data, group == "C"))
+(p2 / p3 / p4) +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r}
+#| label: fig-internet-by-sex
+#| include: true
+#| fig.height: 2.8
+#| fig.cap: Overall proportions of each country's internet users by sex.
+Points are individual countries.
+The regression line indicates that males overall were more likely to have internet access and used internet more frequently, but this divide was smaller for countries where overall adoption was greater.
+dat %>% 
+  group_by(country, year, sex) %>% 
+  summarise(across(starts_with("internet"), ~mean(as.numeric(.)-1, na.rm = TRUE))) %>% 
+  group_by(country, sex) %>% 
+  summarise(across(starts_with("internet"), ~mean(., na.rm = TRUE))) %>% 
+  ungroup() %>% 
+  mutate(m = rowMeans(select(., starts_with("internet")), na.rm = TRUE)) %>% 
+  arrange(m) %>% 
+  mutate(country = fct_inorder(country)) %>% 
+  select(-m) %>% 
+  pivot_longer(starts_with("internet")) %>%
+  pivot_wider(names_from = sex, values_from = value) %>% 
+  ggplot(aes(Male, Female)) +
+  scale_x_continuous(
+    "Males",
+    labels = ~percent(., 1)
+  ) +
+  scale_y_continuous(
+    "Females",
+    labels = ~percent(., 1)
+  ) +
+  geom_abline(linetype = "dotted") +
+  geom_point(shape = 1, col = "dodgerblue1") +
+  geom_smooth(method = "lm", se = FALSE, col = "dodgerblue4") +
+  facet_wrap(
+    "name",
+    nrow = 1,
+    labeller = as_labeller(sanitize_labels),
+  ) +
+  theme(
+    aspect.ratio = 1
+  )
+```

### 2022-12-16 ms.Rmd
Manuscript updates

@@
     gwb_purpose = c("WP14442", "WP14443"),
-    gwb_social = c("WP14444", "WP14445"),
+    gwb_community = c("WP14450", "WP14451"),
     gwb_physical = c("WP14448", "WP14449")
@@
       ) / 4,
-      gwb_social = (
-        rowMeans(select(., WP14444, WP14445), na.rm = TRUE) - 1
+      gwb_community = (
+        rowMeans(select(., WP14450, WP14451), na.rm = TRUE) - 1
       ) / 4,
@@
         WP112, WP113, WP117, 
-        WP118, WP1223, starts_with("WP1444")
+        WP118, WP1223, starts_with("WP144")
       )
@@
 #| label: multiverse-specifications
-dat2 <- dat %>% 
+
+# We will be running two multiverse analyses.
+The first (main one) uses year as a subgroup.
+The second (robustness check) uses year in the data but uses random effects over years and the country-year interaction.
+
+dat_mv <- dat %>% 
   select(
@@
     healthproblems, relationship,
-    income,
+    foodshelter, income,
     starts_with("internet"),
@@
     )
-  ) %>% 
-  group_by(country, year) %>% 
+  )
+
+dat_mv_reyear <- dat_mv %>% 
+  group_by(country) %>% 
   mutate(
@@
     across(
-      c(healthproblems, relationship, work, starts_with("internet")), 
+      c(healthproblems, foodshelter, relationship, work, starts_with("internet")), 
+      ~((as.numeric(.)-1) - mean((as.numeric(.)-1), na.rm = TRUE))
+    )
+  ) %>% 
+  ungroup()
+
+dat_mv <- dat_mv %>% 
+  group_by(country, year) %>% 
+  mutate(
+    # Center all covariates and predictors
+    across(
+      c(education, income),
+      ~. - mean(., na.rm = TRUE)
+    ),
+    across(
+      c(healthproblems, foodshelter, relationship, work, starts_with("internet")), 
       ~((as.numeric(.)-1) - mean((as.numeric(.)-1), na.rm = TRUE))
@@
 
-specs <- expand_grid(
-  year = unique(dat2$year),
-  distinct(dat2, sex, age),
-  y = c(
+ys <- c(
     "life_satisfaction",
@@
     "social_life",
-    "gwb_purpose", "gwb_social", "gwb_physical"
-  ),
-  x = c(
+    "gwb_purpose", "gwb_community", "gwb_physical"
+  )
+xs <- c(
     "internet_access",
@@
     "internet_phone"
-  ),
-  covariate = c(
+  )
+cs <- c(
     "healthproblems",
@@
     "work",
-    "income"
-  ) %>% expand_covariate(),
-  model = c("No", "Yes")
+    "income",
+    "foodshelter"
+  ) %>% expand_covariate()
+
+specs <- expand_grid(
+  year = unique(dat_mv$year),
+  distinct(dat_mv, sex, age),
+  y = ys,
+  x = xs,
+  covariate = cs,
+  weights = c("No", "Yes")
 ) %>% 
@@
   )
+
+specs_reyear <- expand_grid(
+  distinct(dat_mv_reyear, sex, age),
+  y = ys,
+  x = xs,
+  covariate = cs,
+  weights = c("No", "Yes")
+) %>% 
+  mutate(
+    formula = str_glue("{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)")
+  )
 ```
@@
 path <- "tmp/multiverse-lmer.rds"
+path_reyear <- "tmp/multiverse-lmer-reyear.rds"
 if (!file.exists(path)) {
@@
   opts <- furrr_options(
-    globals = list(dat2 = dat2, No = No, Yes = Yes),
+    globals = list(
+      dat_mv = dat_mv, dat_mv_reyear = dat_mv_reyear, 
+      No = No, Yes = Yes
+    ),
     packages = c("lme4", "purrr", "dplyr", "broom.mixed")
@@
 
-  fits <- specs %>% 
+  specs <- specs %>% 
     mutate(
       out = future_pmap(
-        list(model, formula, year, sex, age),
+        list(weights, formula, year, sex, age),
         ~do.call(
@@
             data = filter(
-              dat2, 
+              dat_mv, 
               year == ..3, 
@@
     ) %>% 
-    ungroup() %>% 
-    unnest(out)
-
-  saveRDS(fits, path)
-} else {fits <- readRDS(path)}
+    unnest(out) %>% 
+    filter(n > 0)
+  saveRDS(specs, path)
+
+  specs_reyear <- specs_reyear %>% 
+    mutate(
+      out = future_pmap(
+        list(weights, formula, sex, age),
+        ~do.call(
+          what = ..1, 
+          args = list(
+            formula = ..2, 
+            data = filter(
+              dat_mv_reyear, 
+              sex == ..3, 
+              age == ..4
+            )
+          )
+        ),
+        .options = opts
+      )
+    ) %>% 
+    unnest(out) %>% 
+    filter(n > 0)
+  saveRDS(specs_reyear, path_reyear)
+
+} else {specs <- readRDS(path)}
 
@@
 # Counts for text
-n_specs_all <- nrow(specs) %>% number2()
-n_specs_main <- specs %>% 
+n_specs_all <- fits %>% 
+  filter(effect == x)
+n_specs_main <- n_specs_all %>% 
   filter(!str_detect(y, "gwb_")) %>% 
@@
   number2()
-n_specs_gwb <- specs %>% 
+n_specs_gwb <- n_specs_all %>% 
   filter(str_detect(y, "gwb_")) %>% 
+  nrow() %>% 
+  number2()
+n_specs_all <- n_specs_all %>% 
   nrow() %>% 
@@
 Moreover, research findings on the effects of internet technologies on well-being have been mixed and, to date, inconclusive and of limited geographic and demographic scope.
-In the current work, we examined the extent to which having internet access, a smartphone, or being an active internet user affected seven well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals living in `r length(unique(dat$country))` countries.
+In the current work, we examined the extent to which having internet access, mobile internet access, or being an active internet user affected seven well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals living in `r length(unique(dat$country))` countries.
 We first tested the extent to which well-being varied as a function of internet connectivity.
-Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being using a multiverse analysis over `r n_specs_all` plausible model and subgroup specifications.
+Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being with a multiverse analysis over `r n_specs_all` plausible model and subgroup specifications.
 `r percent(mvs$Positive[5], .01)` of these specifications indicated that internet connectivity was associated with positive well-being, while only `r percent(mvs$Negative[5], .01)` indicated negative associations.
+These results indicate that internet access and active use are positive contributors to individuals' well-being.
 ---
@@
 
-Our overarching aim was to estimate the extent to which internet access and use predicts psychological well-being in cross-sectional samples of `r number2(nrow(dat))` individuals from `r length(unique(dat$country))` countries between 2006 and 2021.
-We studied seven indicators of well-being; life satisfaction, the extent to which individuals experienced daily negative and positive experiences; two indicators of social well-being; physical well-being, and feelings of purpose.
-We investigated the extent to which having any access to the internet; having mobile internet; and having used internet in the past 7 days predicted those aspects of well-being.
+Our overarching aim was to estimate how and to what extent internet access, mobile internet access, and internet use might affect psychological well-being using cross-sectional samples of `r number2(nrow(dat))` individuals from `r length(unique(dat$country))` countries between 2006 and 2021.
+We studied seven indicators of well-being; life satisfaction, the extent to which individuals experienced daily negative and positive experiences; social well-being; physical well-being, community well-being, and experiences of purpose.
+We predicted these well-being indicators from whether individuals had any access to the internet, smartphone access, or whether they were active internet users.
 
@@
 For the GWP methodological details, see @gallupWorldPollMethodology2022.
-We used data from `r number2(nrow(dat))` individuals from 2006 to 2021.
-(There were only 5,001 respondents from three countries in 2022, so we did not analyse that year.)
-
-## Data availability
+We used data from 2006 to 2021, because in 2005 the internet questions were answered by fewer than a quarter of respondents, and the 2022 data only contained five thousand responses from three countries.
+We refer to the 2006-2021 dataset below.
+The total sample size for this analysis was `r number2(nrow(dat))`, with `r length(unique(dat$country))` countries.
+The sample was ZZZ female, and the interquartile range of age was ZZZ.
+
+## Data and material availability
 
 We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
-All our code, and a simulated GWP dataset, is available at [DOI].
-We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database.
+All our code and a simulated GWP dataset is available at [DOI].
+We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the above exclusions).
 
@@
 The key variables that we considered as predictors measured the respondents' access and use of the internet.
-From 2005 to 2021, GWP has surveyed these with four items with varying coverage over time.
-First, GWP measures internet access with *"Does your home have access to the internet?"* (2005 to 2015).
-Because the coverage of existing data for this variable was very low in 2005, we used this variable from 2006 to 2015, where the mean percentage of non-missing values was `r percent(mean(x_sum$internet_home[1:10]), .1)`.
-From 2016 to 2022, a similar question measured overall internet access with *"Do you have access to the internet in any way, whether on a mobile phone, a computer, or some other device?"* (mean coverage `r percent(mean(x_sum$internet_access[11:16]), .1)`).
-Because these two questions were so similar, and to extend the range of data coverage, we merged these two to one "internet access" variable.
-
-Second, GWP has asked about mobile internet access with *"Can your mobile phone be used to access the Internet?"* from 2017 to 2022 (mean coverage `r percent(mean(x_sum$internet_phone[12:16]), .1)`).
-Third, GWP has measured internet *use* with *"Have you used the internet in the past seven days, whether on a mobile phone, a computer, or some other device?"* from 2015 to 2022.
-However, due to poor coverage in 2015, we used this variable from 2016 to 2021 (mean coverage `r percent(mean(x_sum$internet_past7days[11:16]), .1)`).
-
-All of these items had binary "Yes"/"No" response options, and respondents were given the option to decline an answer or report that they didn't know. We coded the latter two as missing values.
+GWP has surveyed these with four items with varying coverage over time.
+First, GWP measured internet access with *"Does your home have access to the internet?"* from 2006 to 2015, where the mean percentage of non-missing values was `r percent(mean(x_sum$internet_home[1:10]), .1)`.
+From 2016 to 2021, a similar question measured overall internet access with *"Do you have access to the internet in any way, whether on a mobile phone, a computer, or some other device?"* (mean valid responses: `r percent(mean(x_sum$internet_access[11:16]), .1)`).
+Because these two questions were so similar, and to extend the range of data coverage, we merged these two to one variable indicating internet access.
+
+Second, GWP asked about mobile internet access with *"Can your mobile phone be used to access the Internet?"* from 2017 to 2021 (mean valid responses: `r percent(mean(x_sum$internet_phone[12:16]), .1)`).
+Third, GWP measured internet use with *"Have you used the internet in the past seven days, whether on a mobile phone, a computer, or some other device?"* from 2015 to 2021 (mean valid responses: `r percent(mean(x_sum$internet_past7days[11:16]), .1)`).
+All of these items had binary "Yes"/"No" response options, and respondents were given the option to decline an answer or report that they didn't know.
+We coded the latter two as missing values.
 
@@
 
-We focused on eight measures of well-being, broadly defined, in the Gallup World Poll: Life satisfaction, negative and positive experiences, social life satisfaction.
-In addition to these four outcomes, which were included in the GWP from 2005 to 2022, we studied four indicators from the Gallup-Sharecare Global Well-being Index™ (GWPI), which is a "barometer of individuals perceptions of their own well-being".
+We focused on seven measures of well-being, broadly defined, in the Gallup World Poll: Life satisfaction, negative and positive experiences, and social life satisfaction.
+In addition to these four outcomes, which were included in the GWP from 2006 to 2021, we studied three indicators from the Gallup-Sharecare Global Well-being Index™ (GWPI), which is a "barometer of individuals perceptions of their own well-being" [@gallupWorldPollMethodology2022].
 
@@
 We included these items as a proxy for social well-being.
-While we recognize their potentially limited validity, we thought that, from the variables available, they best corresponded to the inverse of loneliness, an important and much-studied aspect of well-being in connection to digital technologies.
-
-In 2013 through 2015, the GWP database also included a (Gallup-Sharecare) Global Well-being Index™ (GWPI), which measured (among others) experiences of purpose (*"liking what one does each day and being motivated to achieve one’s goals"*); social well-being (*"having supportive relationships and love in your life"*); and physical well-being, from which we included the item *"In the last seven days, you have felt active and productive every day"*.
-The sense of purpose was measured with prompts *"You like what you do every day"* and *"You learn or do something interesting every day"*.
-All items included the prompt *"Thinking about your life in general, please rate your level of agreement with each of the following using a five-point scale, where 5 means you STRONGLY AGREE and 1 means you STRONGLY DISAGREE.
+While we recognize their potentially limited validity, we thought that, from the variables available, they best approximated an absence of loneliness, an important and much-studied aspect of well-being in connection to digital technologies.
+
+In 2013 through 2015, the GWP database also included a (Gallup-Sharecare) Global Well-being Index™ (GWPI), which measured (among others) experiences of purpose (*"liking what one does each day and being motivated to achieve one’s goals"*); community well-being (*"liking where one lives, feeling safe and having pride in one’s community"*); and physical well-being (*"having good health and enough energy to get things done daily"*).
+Experiences of purpose were measured with prompts *"You like what you do every day"* and *"You learn or do something interesting every day"*.
+Community well-being was prompted with *"The city or area where you live is a perfect place for you"* and *"In the last 12 months, you have received recognition for helping to improve the city or area where you live"*.
+Physical well-being had prompts *"In the last seven days, you have felt active and productive every day"* and *"Your physical health is near-perfect"*.
+All GWPI items included the prompt *"Thinking about your life in general, please rate your level of agreement with each of the following using a five-point scale, where 5 means you STRONGLY AGREE and 1 means you STRONGLY DISAGREE.
 You may choose any of the numbers 1, 2, 3, 4, or 5."* However, because the GWPI was measured only between 2013 and 2015, we present those results separately in the appendix.
@@
 5).
-While we find that statement of dubious value, we believe that the extensive scope of the dataset, across both time and countries, makes these variables uniquely valuable objects of study.
+While this statement doesn't make up for these scales' lack of validation, we believe that the extensive scope of the dataset, across both time and countries, makes them uniquely valuable objects of study.
 
@@
 
-Our intent in this study was to approach the independent contributions of internet access and use on well-being.
-To that end, we adjusted our models for plausible covariates that were available in the GWP.
-First, previous research has highlighted important differences between age groups and sexes in their levels of well-being and use of internet technologies, and associations between the two.
-We therefore conducted our analyses separately for each sex and age group.
-However, to reduce the computational complexity of our analyses, and because there are no strong a priori reasons to assume large differences between adjacent ages, we split the continuous age variable into eight categories (15 to 24, 25 to 34, 35 to 44, 45 to 54, 55 to 64, and 65 +).
-
-Second, internet platforms and technologies are not static but continuously developed in order to better serve their users, and to be more engaging.
-Because this has led to worries that their effects on individuals' well-being might change over time [@vuorreThereNoEvidence2021], we analysed the data separately for each year.
-
-Third, because individuals' levels of well-being and internet access (and use) are likely associated with multiple contextual factors, we chose a set of plausible covariates to adjust our models in an attempt to isolate the independent contributions of internet access and use on well-being.
-To that end, we used the respondent's income, educational, work, and relationship statuses, and whether or not they reported having health problems as covariates in our models.
-
-The GWP queries respondents' for their monthly household income in their local currencies.
+In addressing our second research question, our aim was to approach the independent contributions of internet access and use on well-being.
+To that end, we adjusted for plausible (and available) covariates in our models that might otherwise mask or bias any independent contributions of internet access on well-being, or create spurious associations.
+We chose six variables to represent such potentially confounding factors: The respondent's income, educational, work, and relationship statuses, their ability to meet basic needs for food and shelter, and whether or not they reported having health problems.
+
+The GWP reports respondents' monthly household income in their local currencies.
 GWP used hot deck imputation for individuals who reported an income range (~15%) or who did not provide responses (~15%).
-GWP then converted those values to International Dollars using the World Bank's purchasing power parity conversion factor, with the intent of making income estimates comparable across all respondents and countries.
+GWP then converted those values to international dollars using the World Bank's purchasing power parity conversion factor, with the intent of making income estimates comparable across all respondents and countries.
 In our analyses, we log-transformed income.
 The GWP coded each respondent's educational status to one of three categories: Elementary education or less (up to eight years of education), some secondary education (nine to 15 years), and tertiary (education beyond high school).
-We used this variable as a continuous predictor with values 0, 1, and 2.
+We used this variable as a continuous predictor.
 Since 2009, GWP measured work status with five levels related to the quantity of work, but we recoded this as a binary employed vs.
@@
 not variable.
+Basic need satisfaction was measured with two items querying whether the respondent had had difficulties in providing for their food and shelter in the past 12 months.
 Respondents also answered "Do you have any health problems that prevent you from doing any of the things people your age normally can do?" with a binary yes/no response format.
 
-## Multiverse analysis
+In addition to these covariates, we identified meaningful subgroups in the data.
+First, previous research has highlighted important differences between age groups and sexes in their levels of well-being and use of internet technologies, and associations between the two.
+We therefore conducted our analyses separately for each sex and age group.
+However, to reduce the computational complexity of our analyses, and because there are no strong a priori reasons to assume large differences between adjacent ages, we split the continuous age variable into six categories (15 to 24, 25 to 34, 35 to 44, 45 to 54, 55 to 64, and 65 +).
+Second, internet platforms and technologies are not static but instead technologies and media that are continuously developed and whose affordances changes over time.
+Because this has led to worries that their effects on individuals' well-being might change over time [@vuorreThereNoEvidence2021], we analysed the data separately for each year.
+
+## Data analysis
 
 Our general data-analytic approach was a regression model predicting one outcome (e.g.
-life satisfaction) from an intercept, one predictor (e.g.
-overall internet access), and zero or more of the covariates discussed above.
+life satisfaction) from an intercept and one predictor (e.g.
+internet access).
 Where the outcome consisted of multiple items, we took the mean.
-We conducted models separately for each sex, age group, and year.
-Because the data for each year, sex, and age was nested within countries, we specified a multilevel model where the intercept and coefficient of the internet predictor varied randomly over countries.
-For well-being outcome $y$ and internet predictor $x$, the model was
-
+In addition, we within-country centered all our predictors, so as to not include between-country differences in the coefficients, which consequently indicated contrasts between individuals who (e.g.) had access to the internet to those who didn't, within a given country.
+In addition, because the data were nested within countries, we specified a multilevel model where the intercept and coefficient of the internet predictor varied randomly over countries.
+We addressed our first research question about average contrasts with a multilevel model of well-being outcome $y$ for observation $i$ and country $j$ on internet predictor $x$, specified as
+
+$$
 \begin{align*} 
-y_i &\sim \text{Normal}(\mu_i, \sigma^{2}), \\
-\mu_i &= \alpha_{0} + \beta_{0\text{country}[i]} +
-  (\alpha_{1} + \beta_{1\text{country}[i]})x_i
-  \dots, \\
+y_{ij} &\sim \text{Normal}(\mu_{ij}, \sigma^{2}), \\
+\mu_{ij} &= \alpha_{0} + \beta_{0j} +
+  (\alpha_{1} + \beta_{1j})(x_{ij} - \bar{x}_{.j}), \\
 \begin{bmatrix} 
@@
 \end{align*}
-
-In the above, $i$ indexes rows in the data, and $j$ indicates one of the 164 countries.
-We wrote $\dots$ to represent a particular combination of the covariates (including none), of which there were 32.
-In addition to the model specifications, GWP recommends using model weights to adjust for demographic representativeness in some analyses, and so we conducted the analyses both with and without model weights.
-
-Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariates, and whether model weights were included or not, leading to `r number2(n_specs_all)` specifications.
-However, because not all combinations were possible (e.g.
-mobile internet access did not exist before 2017), our final multiverse consisted of `r number2(n_specs)` specifications.
-We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses.
+$$
+
+In this manner, $\alpha_1$ is the difference in well-being indicator $y$ between individuals who had access to the internet and those who didn't, for the average country.
+For our second, primary, research question we then conducted a multiverse analysis over different covariate permutations on this base model and subgroups in the data.
+We analysed all the possible ways in which the covariates could be included in this model as fixed effects (including no covariates), leading to XXX different covariate specifications.
+In addition to model specifications and subgroups, GWP recommends using model weights to adjust for demographic representativeness in some analyses, and so we conducted the analyses both with and without model weights.
+Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariate combinations, and whether model weights were included or not, leading to `r number2(n_specs_all)` specifications.
+(This number was smaller than the theoretical number of specifications, because not all combinations were possible (e.g.
+mobile internet access did not exist before 2017)).
+
+Because an additional concern with this analytic strategy was a diminishing sample size per analysis (reported below), we conducted a second multiverse analysis as a robustness check.
+That analysis was otherwise similar to our main multiverse analysis, but instead of subgrouping data by year we used year and its interaction with countries as random effect clusters in the multilevel model.
+In addition to examining the robustness of our results, this additional analysis was motivated by our prior study, where differences in technology-use and well-being associations over time were very small [@vuorreThereNoEvidence2021].
+We report this robustness analysis in Appendix B.
+We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses and the lme4 package for estimating the multilevel models [batesFittingLinearMixedEffects2015].
 
@@
 
-Before conducting our full multiverse analysis, we addressed our first research question concerning the overall associations between internet access and use, and well-being.
-To do so, we regressed each outcome on each predictor with the multilevel model described above, but without using covariates or weights, and using all available data without partitioning it by sex, age, or time.
+Our first research question concerned the average differences in well-being between individuals who had access to (mobile) internet or had used the internet in the past seven days, and those who didn't.
+We display the results of this analysis in Figure \@ref(fig:fig-rq1).
+The associations between (mobile) internet access and use and well-being were consistently positive.
+For the average country, individuals who had access to the internet reported approximately 0.08 units greater life satisfaction, positive experiences, and social life satisfaction, and 0.06 units lower negative experiences than individuals who did not have access.
+Results across the other two internet access and use predictors were of the same sign and comparable magnitude.
+To put these magnitudes to context, the models' standard deviations in well-being across countries ranged from XXX to XXX, representing the natural variation in well-being between countries.
+The observed differences in well-being between individuals who had access to or used the internet were of comparable magnitude.
+This suggests that the well-being differences, although they don't indicate causality and were numerically small, were of meaningful magnitude.
+
+Moreover, Figure \@ref(fig:fig-rq1) shows individual countries' observed difference scores as small points; they were very consistently in the same direction as the average contrasts, indicating that this difference held similarly across most countries.
+These results showed uniformly across the four well-being outcomes that individuals who had access to, or actively used the internet reported meaningfully greater well-being than those who did not.
 
@@
 
-The overall association between internet access and use and well-being was consistently positive (Figure \@ref(fig:fig-rq1)).
-On average, across the three internet predictors and four well-being outcomes, individuals who had access to (or used) the internet reported (median) `r number(tmp$estimate, .01)` units (median SE: `r number(tmp$std.error, .001)`) greater well-being than those who did not (we reversed the coefficients for negative experiences for these aggregate numbers).
-Figure \@ref(fig:fig-rq1) shows these data aggregated for each country, and the spread across countries of differences between people who had access to (or used) the internet and who didn't.
-These results showed, uniformly across the four well-being outcomes, that individuals who had access to, or actively used, the internet reported greater well-being than those who did not.
-
 ```{r}
@@
 
-However, although the estimates in Figure \@ref(fig:fig-rq1) were surprisingly uniform across outcomes and predictors, they did not yet address our second, main research question: The extent to which internet access and use might independently contribute to individuals' well-being.
-To best do so, while at the same time incorporate uncertainty in how, where, or for whom to study this association, we next turned to the multiverse analysis.
-In this analysis, we examined the association between well-being and internet use over `r number2(n_specs)` model specifications (and an additional `r number2(n_specs_gwb)` specifications for the GWBI outcomes in the appendix).
-
-We show the average results of this multiverse analysis in Table \@ref(tab:tbl-multiverse).
-First, for life satisfaction, the median sample size across specifications was `r out_sum_2$N[[1]]`.
-On average, answering 'Yes' to an internet access or use question was associated with a `r out_sum_2$Median[[1]]` unit increase in life satisfaction, with the central 50% of associations lying in the `r out_sum_2$IQR[[1]]` interval.
-`r out_sum_2$Positive[[1]]` of the estimated associations were positive.
-Numerical results for the other three well-being outcomes were consistent, and the total proportion of specifications that resulted in negative associations was only `r out_sum_2$Negative[[5]]`.
+However, although the estimates in Figure \@ref(fig:fig-rq1) were surprisingly uniform across outcomes and predictors, they did not yet address our second, main research question: The extent to which internet access and use might independently contribute to individuals' well-being, and whether the associations might be unique to specific subgroups of individuals.
+To best answer this question, while at the same time appreciate the theoretical uncertainty in how, where, or for whom to study this association, we next turned to our main multiverse analysis.
+In the analysis presented here, we examined the association between well-being and internet access or use over `r number2(n_specs_main)` model specifications.
+In appendix A, we present an additional `r number2(n_specs_gwb)` models examining the GWBI outcomes in 2013 to 2015.
+
+We summarize the results of this multiverse analysis in Table \@ref(tab:tbl-multiverse).
+First, for life satisfaction, the median sample size across specifications was `r mvs$N[[1]]`.
+Answering 'Yes' to an internet access or use question was associated with a median `r mvs$Median[[1]]` unit increase in life satisfaction.
+The central 50% of the distribution of associations was within the `r mvs$IQR[[1]]` interval.
+The association between internet access or use and life satisfaction was positive in `r mvs$Positive[[1]]` of model specifications.
+Numerical results for the other three well-being outcomes were of similar magnitude, and the total proportion of specifications that resulted in negative associations was only `r mvs$Negative[[5]]`.
 
@@
 Each vertical slice of figure \@ref(fig:fig-multiverse) identifies a model specification, indexed on the x-axis.
+The resulting estimated association is displayed in panel A.
+The model's specification is the combination of covariates and grouping variables enumerated in panel B.
 For example, one point could represent the association between internet access (X = Internet access in panel B) for males aged 65 or over (Age), with a model that included only an intercept (Covariates = 1) as additional covariates, in the year 2019, for a model estimated without weights (No weights).
@@
 
+A visual examination of Figure \@ref(fig:fig-multiverse) did not suggest any strong patterns in subgroups or covariates such that there would have been an especially strong relation for a specific subgroup or covariate inclusion.
+If that were the case, we should have observed a clustering of points in the dashboard along a single covariate or grouping factor indicating a distinctly strong relation among one or more of the outcomes, which we did not.
+However, the large number of specifications in this figure might make it difficult to tease apart factors that might have led to meaningful variation among the estimated associations.
+To help see the variance among results with respect to covariate specification, Figure XYZ shows the median associations between each outcome and predictor, separately for each covariate specification.
+From this figure, we observe that while generally increasing the number and complexity of covariates in the model did somewhat decrease the magnitudes of the estimated associations, they remained positive and significantly so for most cases.
+This observations shows that even after adjusting for all possible combinations of covariates, the relationships between internet access or use and well-being remained positive.
+In turn, this suggests that the contributions of internet access and use on well-being were independent of the covariates we selected for, and thus might indicate causal relations.
+
 ```{r}
@@
 ```
+
+We then focused on another aspect of potential variation among the associations between internet access or use and well-being. Figure XYZ shows the median associations for each demographic
 

### 2022-12-16 ms.Rmd
:heart: renv

@@
 library(tidyverse)
+library(ragg)
 opts_chunk$set(

### 2022-12-16 ms.Rmd
Small ms edits

@@
   mutate(
-    formula = str_glue("{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)")
+    formula = str_glue(
+      "{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)"
+    )
   )
@@
 
-fits <- rename(fits, weights = model) %>% 
-  filter(n > 0)
-fits_gwb <- fits %>% filter(str_detect(y, "gwb_"))
-fits <- fits %>% filter(!str_detect(y, "gwb_"))
-
-# Counts for text
-n_specs_all <- fits %>% 
-  filter(effect == x)
-n_specs_main <- n_specs_all %>% 
-  filter(!str_detect(y, "gwb_")) %>% 
-  nrow() %>% 
-  number2()
-n_specs_gwb <- n_specs_all %>% 
-  filter(str_detect(y, "gwb_")) %>% 
-  nrow() %>% 
-  number2()
-n_specs_all <- n_specs_all %>% 
-  nrow() %>% 
-  number2()
-
-mv <- fits %>% 
+specs_gwb <- specs %>% filter(str_detect(y, "gwb_"))
+specs <- specs %>% filter(!str_detect(y, "gwb_"))
+
+n_specs_main <- specs %>% 
+  filter(term == x) %>% 
+  nrow()
+n_specs_gwb <- specs_gwb %>% 
+  filter(term == x) %>% 
+  nrow()
+n_specs_all <- n_specs_main + n_specs_gwb
+
+mv <- specs %>% 
   filter(term == x) %>% 
@@
 We first tested the extent to which well-being varied as a function of internet connectivity.
-Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being with a multiverse analysis over `r n_specs_all` plausible model and subgroup specifications.
+Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being with a multiverse analysis over XXXX plausible model and subgroup specifications.
 `r percent(mvs$Positive[5], .01)` of these specifications indicated that internet connectivity was associated with positive well-being, while only `r percent(mvs$Negative[5], .01)` indicated negative associations.
@@
 
-$$
 \begin{align*} 
@@
 \end{align*}
-$$
 
@@
 In addition to model specifications and subgroups, GWP recommends using model weights to adjust for demographic representativeness in some analyses, and so we conducted the analyses both with and without model weights.
-Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariate combinations, and whether model weights were included or not, leading to `r number2(n_specs_all)` specifications.
+Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariate combinations, and whether model weights were included or not, leading to `r n_specs_all` specifications.
 (This number was smaller than the theoretical number of specifications, because not all combinations were possible (e.g.
@@
 We report this robustness analysis in Appendix B.
-We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses and the lme4 package for estimating the multilevel models [batesFittingLinearMixedEffects2015].
+We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses and the lme4 package for estimating the multilevel models [@batesFittingLinearMixedEffects2015].
 
@@
 ```{r}
-path <- "tmp/fits-lmer-total.rds"
+path <- "tmp/specs-lmer-total.rds"
 if (!file.exists(path)) {
@@
 
-  fits_avg <- expand_grid(
+  specs_avg <- expand_grid(
     y = c(
@@
 
-  fits_avg <- fits_avg %>% 
+  specs_avg <- specs_avg %>% 
     filter(term == x) %>% 
@@
 
-  saveRDS(fits_avg, path)
-} else {fits_avg <- readRDS(path)}
+  saveRDS(specs_avg, path)
+} else {specs_avg <- readRDS(path)}
 
 # Median association (with reversed negative experiences)
-tmp <- fits_avg %>% 
+tmp <- specs_avg %>% 
   mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
@@
   geom_label(
-    data = fits_avg %>% 
+    data = specs_avg %>% 
       filter(!str_detect(y, "gwb_")) %>% 
@@
 #| include: true
-out_sum_2 <- out_sum_2 %>% 
+mvs2 <- mvs %>% 
   mutate(
@@
   )
-out_sum_2 %>%   
+mvs2 %>%   
   apa_table(
@@
 #| fig.env: "figure*"
-#| fig.height: 7.6
+#| fig.height: 7.8
 #| fig.width: 9
@@
 Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
-
-p1 <- out %>% 
+p1 <- mv %>% 
   ggplot(aes(i, estimate, col = decision)) +
@@
   geom_ysidepoint(
-    data = out_sum %>% 
+    data = mv %>% 
+      group_by(y) %>% 
+      summarise(median = median(estimate)) %>% 
       # Just for coloring the dot
@@
         decision = cut(
-          `0.5`, 
+          median,
           breaks = c(-1, -.0001, .0001, 1),
-          labels = levels(out$decision)
-        )
-      ),
-    aes(y = `0.5`, x = 0),
+          labels = c("Negative", "Not significant", "Positive")
+        )
+      ),
+    aes(y = median, x = 0),
     size = 2, position = position_nudge(x = .025)
@@
 
-p2 <- out %>% 
+p2 <- mv %>% 
   mutate(
@@
     ),
-    value = fct_relevel(value, unique(specs$covariate)),
+    value = fct_relevel(value, cs),
     value = fct_recode(value, `No covariates` = "1")
@@
   ) +
-  geom_point(shape = 20, size = .2) +
+  geom_point(
+    shape = 20, 
+    size = .1, 
+    position = position_quasirandom(groupOnX = FALSE, width = .2)
+  ) +
   facet_grid(
@@
 ((p1 / p2) +
-  plot_layout(heights = c(3.6, 6.4))) +
+  plot_layout(heights = c(3.2, 6.8))) +
   plot_annotation(tag_levels = "A")
@@
 The specifications are ordered as in Figure 2; where greater numbers indicate more covariates in the model.
-p1 <- fits %>% 
+p1 <- specs %>% 
   filter(term == x) %>% 
@@
 ```{r}
-fits %>% 
+specs %>% 
   filter(term == x) %>% 
@@
 library(ggh4x)
-fits %>% 
+specs %>% 
   drop_na(age, sex) %>% 
@@
 Furthermore, we attempted to estimate the unique contributions of internet on well-being by examining this association across `r length(unique(specs$covariate))` different permutations of sets of plausible covariates that might otherwise create or mask associations.
-Across `r number2(nrow(filter(fits, term == x)))` of such model specifications, `r out_sum_2$Positive[5]` of the associations were significantly positive, and only `r out_sum_2$Negative[5]` were negative.
+Across `r number2(nrow(filter(specs, term == x)))` of such model specifications, `r mvs$Positive[5]` of the associations were significantly positive, and only `r mvs$Negative[5]` were negative.
 We thus conclude that the proliferation of (mobile) internet access and increasing engagement with the internet has been a net benefit to the well-being of individuals around the world.

### 2023-03-22 ms.Rmd

@@
     corresponding: yes
-    address: Oxford Internet Institute, University of Oxford
-    email: matti.vuorre@oii.ox.ac.uk
+    address: Tilburg University
+    email: m.j.vuorre@tilburguniversity.edu
   - name: Andrew K. Przybylski
@@
 wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
-bibliography: "references.bib"
+bibliography: references.bib
 floatsintext: yes
@@
 footnotelist: no
-csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
 documentclass: apa7
-classoption: jou
+classoption: doc
 header-includes:
@@
     number_sections: false
-    keep_tex: false
+    keep_tex: true
   papaja::apa6_docx: 
     number_sections: false
-editor_options: 
-  chunk_output_type: console
+    keep_tex: false
 ---
@@
     social_life = c("WP27", "WP10248"), 
-    laworder = c("WP112", "WP113", "WP117", "WP118"), 
     foodshelter = c("WP40", "WP43"), 
@@
     gwb_community = c("WP14450", "WP14451"),
+    gwp_social = c("WP14444", "WP14445"),
     gwb_physical = c("WP14448", "WP14449")
@@
       income = as.numeric(INCOME_2),
-      income_feeling = 4 - as.integer(WP2319),
-      education = as.numeric(WP3117),
+      education = as.numeric(WP3117) - 1,
       work = EMP_2010,
@@
   # Then the other scales
-  dat %>% 
+  dat[,-1] %>% 
     generate_dictionary()
@@
     mutate(
-      # Law and order
-      WP112 = 2 - WP112,
-      WP113 = 2 - WP113,
-      WP117 = WP117 - 1,
-      WP118 = WP118 - 1,
-    ) %>% mutate(
-      laworder = rowMeans(
-        select(., WP112, WP113, WP117, WP118), na.rm = TRUE
-      ),
       # Food and shelter [note below], 
@@
       ) - 1,
-      # GWPI items
+      # GWPI items and scale to 0-1
       gwb_purpose = (
@@
       ) / 4,
+      gwb_social = (
+        rowMeans(select(., WP14444, WP14445), na.rm = TRUE) - 1
+      ) / 4,
       .keep = "unused"
@@
   dat <- dat %>% 
-    select(
-      -c(
-        WP16, WP40, WP43, 
-        WP112, WP113, WP117, 
-        WP118, WP1223, starts_with("WP144")
-      )
-    )
+    select(-starts_with("WP"))
+  glimpse(dat)
+  summary(dat)
+
+  # A few dozen missing sex and age
+  dat <- drop_na(dat, sex, age) %>% 
+    mutate(sex = fct_drop(sex))
+
+  # Income logp1
+  dat <- mutate(dat, income = log(income+1))
+
+  # Too little data in 2022, and poor internet value coverage in 2005
+  dat <- filter(dat, between(year, 2006, 2021))
+
+  # Create combined internet access variable
+  dat <- dat %>% 
+    mutate(
+      internet_access = if_else(year < 2016, internet_home, internet_access)
+    ) %>% 
+    select(-internet_home)
 
@@
 }
+```
+
+```{r}
+#| label: data-synth-create
+#| eval: false
+
+# Here we create a synthetic smaller dataset that mimics some statistical properties of the dataset. It is a smaller dataset because generating the full table is very slow.
+if (FALSE) {
+  dir.create("synthetic-data", FALSE)
+  library(synthpop)
+  set.seed(909090)
+  x <- read_rds(path)
+  x <- x %>% 
+    filter(year > 2013) %>% 
+    filter(country %in% sample(unique(x$country), 20)) %>% 
+    # drop_na(starts_with("internet")) %>% 
+    slice_sample(n = 200, by = country)
+  x <- tibble(syn(x, method = "sample")$syn)
+  write_csv(x, "synthetic-data/synthetic-data.csv.gz")
+}
+```
+
+```{r}
+#| label: data-load
 dat <- read_rds(path)
-
-# A few dozen missing sex and age
-dat <- drop_na(dat, sex, age) %>% 
-  mutate(sex = fct_drop(sex))
-
-# Income logp1
-dat <- mutate(dat, income = log(income+1))
-
-# Count observations and take out years with small N
+# dat <- read_csv("synthetic-data/synthetic-data.csv.gz") # Synthetic dataset
+
 # Summarise original values
@@
   )
-# Too little data in 2022, and poor internet value coverage in 2005
-dat <- filter(dat, between(year, 2006, 2021))
-
-# Create combined internet access variable
+
+yr <- paste(range(dat$year), collapse = " to ")
+```
+
+```{r}
+#| label: multiverse-specifications
+
+# Select variables and categorize age
+age_iqr <- quantile(dat$age, probs = c(.25, .75)) %>% paste(collapse = ", ")
 dat <- dat %>% 
-  mutate(
-    internet_access = if_else(year < 2016, internet_home, internet_access)
-  ) %>% 
-  select(-internet_home)
-yr <- paste(range(dat$year), collapse = " to ")
-```
-
-```{r}
-#| label: multiverse-specifications
-
-# We will be running two multiverse analyses.
-The first (main one) uses year as a subgroup.
-The second (robustness check) uses year in the data but uses random effects over years and the country-year interaction.
-
-dat_mv <- dat %>% 
   select(
@@
 
-dat_mv_reyear <- dat_mv %>% 
+# Within-country center variables
+dat_raw <- dat
+dat <- dat %>% 
   group_by(country) %>% 
   mutate(
-    # Center all covariates and predictors
-    across(
-      c(education, income),
-      ~. - mean(., na.rm = TRUE)
-    ),
-    across(
-      c(healthproblems, foodshelter, relationship, work, starts_with("internet")), 
-      ~((as.numeric(.)-1) - mean((as.numeric(.)-1), na.rm = TRUE))
-    )
-  ) %>% 
-  ungroup()
-
-dat_mv <- dat_mv %>% 
-  group_by(country, year) %>% 
-  mutate(
-    # Center all covariates and predictors
     across(
@@
     "social_life",
-    "gwb_purpose", "gwb_community", "gwb_physical"
+    "gwb_purpose", 
+    "gwb_physical",
+    "gwb_community",
+    "gwb_social"
   )
@@
     "foodshelter"
-  ) %>% expand_covariate()
+  ) %>% 
+  expand_covariate()
 
 specs <- expand_grid(
-  year = unique(dat_mv$year),
-  distinct(dat_mv, sex, age),
+  distinct(dat, sex, age),
   y = ys,
@@
 ) %>% 
-  mutate(
-    formula = str_glue("{y} ~ {x} + {covariate} + ({x} | country)")
-  )
-
-# Subset the specs to things that exist in the data
-specs <- specs %>% 
-  filter(
-    !(x == "internet_phone" & year < 2017),  # Existed 2017 onwards
-    !(x == "internet_past7days" & year < 2015), # 2015 onwards
-    !(str_starts(y, "gwb_") & !between(year, 2013, 2015)) # only these years
-  )
-
-specs_reyear <- expand_grid(
-  distinct(dat_mv_reyear, sex, age),
-  y = ys,
-  x = xs,
-  covariate = cs,
-  weights = c("No", "Yes")
-) %>% 
-  mutate(
-    formula = str_glue(
-      "{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)"
+  # Drop year from formula for GWB outcomes (only ~1 year)
+  mutate(
+    formula = if_else(
+      str_starts(y, "gwb_"),
+      str_glue("{y} ~ {x} + {covariate} + ({x} | country)"),
+      str_glue("{y} ~ {x} + {covariate} + ({x} | country) + ({x} | year) + ({x} | country:year)"),
     )
@@
 #| label: multiverse-run
+
 dir.create("tmp", FALSE)
 path <- "tmp/multiverse-lmer.rds"
-path_reyear <- "tmp/multiverse-lmer-reyear.rds"
 if (!file.exists(path)) {
@@
     globals = list(
-      dat_mv = dat_mv, dat_mv_reyear = dat_mv_reyear, 
-      No = No, Yes = Yes
+      dat = dat, No = No, Yes = Yes
     ),
@@
   specs <- specs %>% 
-    mutate(
-      out = future_pmap(
-        list(weights, formula, year, sex, age),
-        ~do.call(
-          what = ..1, 
-          args = list(
-            formula = ..2, 
-            data = filter(
-              dat_mv, 
-              year == ..3, 
-              sex == ..4, 
-              age == ..5
-            )
-          )
-        ),
-        .options = opts
-      )
-    ) %>% 
-    unnest(out) %>% 
-    filter(n > 0)
-  saveRDS(specs, path)
-
-  specs_reyear <- specs_reyear %>% 
     mutate(
@@
             data = filter(
-              dat_mv_reyear, 
+              dat, 
               sex == ..3, 
@@
     filter(n > 0)
-  saveRDS(specs_reyear, path_reyear)
-
-} else {specs <- readRDS(path)}
-
-specs_gwb <- specs %>% filter(str_detect(y, "gwb_"))
-specs <- specs %>% filter(!str_detect(y, "gwb_"))
-
-n_specs_main <- specs %>% 
-  filter(term == x) %>% 
-  nrow()
-n_specs_gwb <- specs_gwb %>% 
-  filter(term == x) %>% 
-  nrow()
-n_specs_all <- n_specs_main + n_specs_gwb
-
+
+  saveRDS(specs, path)
+
+}
+```
+
+```{r}
+#| Label: multiverse-tidy
+specs <- readRDS(path) # Load from file
+
+# Parameter of interest (slope of x)
+specs <- specs %>% filter(term == x)
+
+# Arrange outcomes
+specs <- specs %>% 
+  mutate(y = factor(y, levels = ys))
+
+# Arranged table with extra info 
 mv <- specs %>% 
-  filter(term == x) %>% 
   arrange(estimate, y) %>% 
@@
 
+# Summary of multiverse magnitudes
 mvs <- mv %>% 
@@
 
+# Summary of multiverse magnitudes and decisions
 mvs <- mv %>% 
@@
 
+# Grand summary (also across outcome)
 mvs_all <- mv %>% 
@@
   )
+
 mvs <- bind_rows(
@@
 rm(mvs_all)
+
+# Add count of specs
+mvs <- mv %>% 
+  count(Outcome = y, name = "K") %>% 
+  add_row(Outcome = "Total", K = nrow(mv)) %>% 
+  mutate(Outcome = sanitize_labels(Outcome)) %>% 
+  left_join(mvs)
 ```
@@
 abstract: |
-  With the increasing global penetration of the internet, and technologies and platforms enabled by it, their potential effects on individuals' well-being remains hotly debated.
-On one hand, these technologies have enabled novel forms of commerce, education, and leisure; on the other, many are worried that their use might negatively affect individuals by, for example, displacing time spent on other healthy activities.
-Moreover, research findings on the effects of internet technologies on well-being have been mixed and, to date, inconclusive and of limited geographic and demographic scope.
-In the current work, we examined the extent to which having internet access, mobile internet access, or being an active internet user affected seven well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals living in `r length(unique(dat$country))` countries.
-We first tested the extent to which well-being varied as a function of internet connectivity.
-Then, to go beyond describing average associations, we examined the potential causal effects of internet connectivity on well-being with a multiverse analysis over XXXX plausible model and subgroup specifications.
-`r percent(mvs$Positive[5], .01)` of these specifications indicated that internet connectivity was associated with positive well-being, while only `r percent(mvs$Negative[5], .01)` indicated negative associations.
-These results indicate that internet access and active use are positive contributors to individuals' well-being.
+  With internet technologies' and platforms' increasing global penetration, their potential consequences to well-being remain debated.
+While these technologies have spurred novel forms of commerce, education, and leisure, many are worried that they might negatively affect individuals by, for example, displacing time spent on other healthy activities.
+Findings on internet technologies' effects on well-being have been, to date, inconclusive and of limited geographic and demographic scope.
+We examined the extent to which having (mobile) internet access or actively using the internet predicted eight well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals across `r length(unique(dat$country))` countries.
+We first queried the extent to which well-being varied as a function of internet connectivity.
+Then, we examined these associations' robustness in a multiverse of `r number2(nrow(specs))` analysis and subgroup specifications.
+`r percent(mvs$Positive[9], .01)` of these specifications resulted in positive and statistically significant associations between internet connectivity and well-being.
+These results indicate that (mobile) internet access and active internet use predict well-being positively and independent from a set of plausible confounders.
+
+  \emph{Statement of relevance.} Are internet technologies, such as smartphones and social media, psychologically harmful?
+Past results have generally offered mixed evidence and, critically, focused on a narrow slice of the global population.
+At the same time, stakeholders from international health bodies to technology companies are investing in regulation and tools to protect internet users' well-being.
+We examined 2.5 million individual's, from 168 nations, psychosocial well-being and internet adoption and use over a period of fifteen years.
+We find that (mobile) internet adoption and use predict positive well-being and that this association is robust across thousands of adjustments for alternative explanations and demographic subgroups.
+While merely suggestive of causal associations, our results highlight social scientists' need for more transparent access to the large databases currently held behind the closed doors of the technology industry.
 ---
@@
 The increasing adoption and use of internet-enabled technologies and platforms has spurred debate about their potential effects on people's psychological well-being and functioning.
-However, even after considerable scientific attention, an understanding of the associations between internet technology use and well-being remains elusive, and results of scientific studies on this topic have been mixed.
-
-## Current study
-
-Our overarching aim was to estimate how and to what extent internet access, mobile internet access, and internet use might affect psychological well-being using cross-sectional samples of `r number2(nrow(dat))` individuals from `r length(unique(dat$country))` countries between 2006 and 2021.
-We studied seven indicators of well-being; life satisfaction, the extent to which individuals experienced daily negative and positive experiences; social well-being; physical well-being, community well-being, and experiences of purpose.
-We predicted these well-being indicators from whether individuals had any access to the internet, smartphone access, or whether they were active internet users.
-
-We first asked what was the average difference, among the whole sample, in well-being between those individuals who had access to or used the internet, and those who did not.
-That is, our first research question addressed the basic association between internet and well-being.
-
-Second, our aim was to identify the unique contributions that internet access and use might have on well-being, and whether those might vary between demographics or over time.
-To this end, we used a set of meaningful covariates to adjust our models with.
-
-# Methods
-
-We analysed data from the Gallup World Poll [@gallupWorldPollMethodology2022].
-Gallup World Poll (GWP) is a nationally representative (of each country's civilian, non-institutionalized, adult [15+] population) continuous annual survey of approximately 1,000 individuals from each of 164 countries, conducted from 2005 to 2022.
-Gallup conducts the surveys through one-hour interviews either face-to-face or via telephone, with questionnaires that are translated to the major conversational language of each country.
-For the GWP methodological details, see @gallupWorldPollMethodology2022.
-We used data from 2006 to 2021, because in 2005 the internet questions were answered by fewer than a quarter of respondents, and the 2022 data only contained five thousand responses from three countries.
-We refer to the 2006-2021 dataset below.
-The total sample size for this analysis was `r number2(nrow(dat))`, with `r length(unique(dat$country))` countries.
-The sample was ZZZ female, and the interquartile range of age was ZZZ.
-
-## Data and material availability
+Social scientists have shifted focus from other topics such as violent video games and television-based technologies to new and emerging platforms and handheld digital devices [@orbenSisypheanCycleTechnology2020].
+Large technology firms such as Meta [@metaNewToolsResources2022], Google [@googleDigitalWellbeingTechnology2022], Apple [@appleIOS12Introduces2018], and TikTok [@tiktokDigitalWellbeing2021] have reacted to concerns and released a host of "digital well-being" tools.
+At the same time, health professionals [@officeofthesurgeongeneralosgProtectingYouthMental2021] and officials in many countries are working to enact new regulations [@departmentfordigitalculturemedia&sportGuideOnlineSafety2022] to ensure internet and technology platforms protect user well-being.
+However, even after considerable scientific attention, an understanding of the fundamental associations between internet technology adoption and use and well-being remains elusive, and results of scientific studies on this topic are decidedly mixed [@appelAreSocialMedia2020; @bestOnlineCommunicationSocial2014; @dickson2018screen].
+
+The rise in tools, advice, and regulation aimed at addressing well-being is interesting, in part, because of how the studies informing this debate are done.
+For example, despite the fact the challenge is often framed as a world-wide issue, the geographic and demographic scope of the evidence base is narrow and not well mapped onto worldwide trends [@ghaiLackSampleDiversity2021].
+In the past decades, the expansion of access to the internet has accelerated the most [@ituITUICTStatistics2021] in places where social scientists are the least likely to study their effects [@ghaiSocialMediaAdolescent2022].
+Similarly, whilst studying technology adoption and well-being across countries requires frequent and high-quality measures of both factors, few if any investigations successfully combine the two.
+Measurement quality and consistency varies significantly and the most widely cited international studies either lack a longitudinal component [@byrneGlobalKidsOnline2016], or have long three [@oecdPISA2018Technical2018] or four year [@inchleyEnhancingUnderstandingAdolescent2020] intervals between data collections.
+Finally, because most of the debate surrounding the global impact of internet technologies is focused on younger people, little if any global data reflect associations between technology and well-being across the life course.
+This important lack of context means that it remains an open question of who, where, and when internet technologies and connectivity might be influencing people's well-being.
+Without knowing this it is impossible to deploy limited resources to capitalize on benefits or redress harms.
+To our knowledge, no research has directly grappled with these issues and addressed the worldwide scope of the debate.
+
+Considering this impasse, our overarching research goal was to estimate the extent to which internet access, mobile internet access, and internet use might predict psychological well-being on a global level.
+To this end, we analyzed data from a series of cross-sectional samples of `r number2(nrow(dat))` individuals from `r length(unique(dat$country))` countries from `r yr`.
+We studied eight indicators of well-being; life satisfaction, the extent to which individuals reported experiencing daily negative and positive experiences; two indices of social well-being; physical well-being, community well-being, and experiences of purpose.
+We started by first asking how well-being differed between individuals who had access to or used (mobile) internet, and those who did not.
+To answer, we predicted the well-being indicators from whether individuals had access to the internet, smartphone access, or whether they were active internet users.
+We then sought to probe the robustness of these associations by conducting a series of multiverse analyses that examined how national, demographic, and individual factors might serve to mask or create links between internet connectivity and well-being.
+
+# Open Practices Statement
 
@@
 All our code and a simulated GWP dataset is available at [DOI].
-We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the above exclusions).
+We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below).
+This study was not pre-registered.
+
+# Methods
+
+We analysed data from the Gallup World Poll [@gallupWorldPollMethodology2022].
+Gallup World Poll (GWP) is a nationally representative (of each country's civilian, non-institutionalized, adult [15+] population) continuous annual panel survey of approximately 1,000 individuals from each of 164 countries, conducted from 2005 to 2022.
+Gallup conducts the surveys through one-hour interviews either face-to-face or via telephone, with questionnaires that are translated to the major conversational language of each country.
+See @gallupWorldPollMethodology2022 for the GWP methodological details.
+We used data from 2006 to 2021, because in 2005 the internet questions were answered by fewer than a quarter of respondents, and the 2022 data only contained five thousand responses from three countries.
+We refer to the `r yr` dataset below.
+The total sample size for this analysis was `r number2(nrow(dat))`, with `r length(unique(dat$country))` countries.
+The sample was `r percent(prop.table(table(dat$sex))["Female"], .1)` female, and the interquartile range of age was [`r age_iqr`].
 
@@
 
-We focused on seven measures of well-being, broadly defined, in the Gallup World Poll: Life satisfaction, negative and positive experiences, and social life satisfaction.
-In addition to these four outcomes, which were included in the GWP from 2006 to 2021, we studied three indicators from the Gallup-Sharecare Global Well-being Index™ (GWPI), which is a "barometer of individuals perceptions of their own well-being" [@gallupWorldPollMethodology2022].
+We focused on eight measures of well-being, broadly defined, in the Gallup World Poll: Life satisfaction, negative and positive experiences, and social life satisfaction.
+In addition to these four outcomes, which were included in the GWP from 2006 to 2021, we studied four indicators from the Gallup-Sharecare Global Well-being Index™ (GWPI), which is a "barometer of individuals perceptions of their own well-being" [@gallupWorldPollMethodology2022].
 
@@
 How about physical pain / worry / sadness / stress / anger?"*.
-For positive experiences, the items were *"Did you feel well-rested yesterday?"*; *"Were you treated with respect all day yesterday?"*; *"Did you smile or laugh a lot yesterday?"*; *"Did you learn or do something interesting yesterday?*"; and *"Did you experience the following feelings during a lot of the day yesterday?
-How about enjoyment?"*.
+For positive experiences, the items were *"Did you feel well-rested yesterday?"*; *"Were you treated with respect all day yesterday?"*; *"Did you smile or laugh a lot yesterday?"*; *"Did you learn or do something interesting yesterday?"; and* "Did you experience the following feelings during a lot of the day yesterday?
+How about enjoyment?".
 
 In addition, we included two variables intended to measure individuals' "social support structure and opportunities to make friends" (*"Someone in your life always encourages you to be healthy"* and *"Your friends and family give you positive energy every day"*).
-We included these items as a proxy for social well-being.
+We included these items as a proxy for social well-being (hereafter, "social life").
 While we recognize their potentially limited validity, we thought that, from the variables available, they best approximated an absence of loneliness, an important and much-studied aspect of well-being in connection to digital technologies.
 
-In 2013 through 2015, the GWP database also included a (Gallup-Sharecare) Global Well-being Index™ (GWPI), which measured (among others) experiences of purpose (*"liking what one does each day and being motivated to achieve one’s goals"*); community well-being (*"liking where one lives, feeling safe and having pride in one’s community"*); and physical well-being (*"having good health and enough energy to get things done daily"*).
+In 2013 through 2015, the GWP database also included a (Gallup-Sharecare) Global Well-being Index™ (GWPI), which measured (among others) experiences of purpose (*"liking what one does each day and being motivated to achieve one's goals"*); community well-being (*"liking where one lives, feeling safe and having pride in one's community"*), physical well-being (*"having good health and enough energy to get things done daily"*), and social well-being (*"having supportive relationships and love in your life"*).
 Experiences of purpose were measured with prompts *"You like what you do every day"* and *"You learn or do something interesting every day"*.
@@
 Physical well-being had prompts *"In the last seven days, you have felt active and productive every day"* and *"Your physical health is near-perfect"*.
-All GWPI items included the prompt *"Thinking about your life in general, please rate your level of agreement with each of the following using a five-point scale, where 5 means you STRONGLY AGREE and 1 means you STRONGLY DISAGREE.
-You may choose any of the numbers 1, 2, 3, 4, or 5."* However, because the GWPI was measured only between 2013 and 2015, we present those results separately in the appendix.
+Social well-being was measured with the same items as the above "social life" index, but instead on a rating scale: All GWPI items included the prompt *"Thinking about your life in general, please rate your level of agreement with each of the following using a five-point scale, where 5 means you STRONGLY AGREE and 1 means you STRONGLY DISAGREE.
+You may choose any of the numbers 1, 2, 3, 4, or 5."*
 
@@
 The GWP reports respondents' monthly household income in their local currencies.
-GWP used hot deck imputation for individuals who reported an income range (~15%) or who did not provide responses (~15%).
+GWP used hot deck imputation for individuals who reported an income range (\~15%) or who did not provide responses (\~15%).
 GWP then converted those values to international dollars using the World Bank's purchasing power parity conversion factor, with the intent of making income estimates comparable across all respondents and countries.
@@
 In addition to these covariates, we identified meaningful subgroups in the data.
-First, previous research has highlighted important differences between age groups and sexes in their levels of well-being and use of internet technologies, and associations between the two.
+Previous research has highlighted important differences between age groups and sexes in their levels of well-being and use of internet technologies, and associations between the two.
 We therefore conducted our analyses separately for each sex and age group.
 However, to reduce the computational complexity of our analyses, and because there are no strong a priori reasons to assume large differences between adjacent ages, we split the continuous age variable into six categories (15 to 24, 25 to 34, 35 to 44, 45 to 54, 55 to 64, and 65 +).
-Second, internet platforms and technologies are not static but instead technologies and media that are continuously developed and whose affordances changes over time.
-Because this has led to worries that their effects on individuals' well-being might change over time [@vuorreThereNoEvidence2021], we analysed the data separately for each year.
 
@@
 In addition, because the data were nested within countries, we specified a multilevel model where the intercept and coefficient of the internet predictor varied randomly over countries.
-We addressed our first research question about average contrasts with a multilevel model of well-being outcome $y$ for observation $i$ and country $j$ on internet predictor $x$, specified as
-
+To be conservative, we also added random intercepts and slopes over years, and the country by year interaction, because any associations might be heterogeneous over time [@vuorreThereNoEvidence2021].
+We addressed our first research question about average contrasts with a multilevel model of well-being outcome $y$ for observation $i$, country $j$, year $k$ and year by country $l$, on internet predictor $x$, specified as
+
+```{=tex}
 \begin{align*} 
-y_{ij} &\sim \text{Normal}(\mu_{ij}, \sigma^{2}), \\
-\mu_{ij} &= \alpha_{0} + \beta_{0j} +
-  (\alpha_{1} + \beta_{1j})(x_{ij} - \bar{x}_{.j}), \\
-\begin{bmatrix} 
-\beta_0 \\ \beta_1 
-\end{bmatrix} 
-& \sim\text{Normal}\left(
-  \begin{bmatrix}
-  0 \\ 0 
-  \end{bmatrix}, 
-  \begin{bmatrix} 
-  \sigma_{\beta_0}^2 & \\ \sigma_{\beta_0\beta_1} & \sigma_{\beta_1}^2 
-  \end{bmatrix} 
-\right).
+y_{ijkl} \sim\ &\text{Normal}(\mu_{ijkl}, \sigma^{2}), \\
+\mu_{ijkl} =\ &\alpha_{0} + \beta_{0j} + \gamma_{0k} + \delta_{0l} + \\
+  &(\alpha_{1} + \beta_{1j} + \gamma_{1k} + \delta_{1l})(x_{ijkl} - \bar{x}_{.jkl}), \\
+\pmb{\beta} \sim\ &\text{Normal}\left(\begin{bmatrix}  0 \\ 0 \end{bmatrix}, \Sigma_\beta\right), \\
+\pmb{\gamma} \sim\ &\text{Normal}\left(\begin{bmatrix}  0 \\ 0 \end{bmatrix}, \Sigma_\gamma\right), \\
+\pmb{\delta} \sim\ &\text{Normal}\left(\begin{bmatrix}  0 \\ 0 \end{bmatrix}, \Sigma_\delta\right).
 \end{align*}
-
-In this manner, $\alpha_1$ is the difference in well-being indicator $y$ between individuals who had access to the internet and those who didn't, for the average country.
+```
+In this manner, $\alpha_1$ is the difference in well-being indicator $y$ between individuals who had access to the internet and those who didn't, for the average country and year.
+
 For our second, primary, research question we then conducted a multiverse analysis over different covariate permutations on this base model and subgroups in the data.
-We analysed all the possible ways in which the covariates could be included in this model as fixed effects (including no covariates), leading to XXX different covariate specifications.
+We analysed all the possible ways in which the covariates could be included in this model (including no covariates) as fixed effects, leading to `r length(cs)` different covariate specifications.
 In addition to model specifications and subgroups, GWP recommends using model weights to adjust for demographic representativeness in some analyses, and so we conducted the analyses both with and without model weights.
-Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, years, covariate combinations, and whether model weights were included or not, leading to `r n_specs_all` specifications.
-(This number was smaller than the theoretical number of specifications, because not all combinations were possible (e.g.
-mobile internet access did not exist before 2017)).
-
-Because an additional concern with this analytic strategy was a diminishing sample size per analysis (reported below), we conducted a second multiverse analysis as a robustness check.
-That analysis was otherwise similar to our main multiverse analysis, but instead of subgrouping data by year we used year and its interaction with countries as random effect clusters in the multilevel model.
-In addition to examining the robustness of our results, this additional analysis was motivated by our prior study, where differences in technology-use and well-being associations over time were very small [@vuorreThereNoEvidence2021].
-We report this robustness analysis in Appendix B.
+Our multiverse therefore consisted of all the distinct combinations of outcomes, predictors, age, sex, covariate combinations, and whether model weights were included or not, leading to `r number2(nrow(specs))` specifications.
 We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses and the lme4 package for estimating the multilevel models [@batesFittingLinearMixedEffects2015].
@@
 ```{r}
+#| label: multiverse-average-run
+
 path <- "tmp/specs-lmer-total.rds"
@@
   opts <- furrr_options(
-    globals = list(dat2 = dat2, No = No),
+    globals = list(dat = dat, No = No),
     packages = c("lme4", "purrr", "dplyr", "broom.mixed")
@@
       "social_life",
-      "gwb_purpose", "gwb_social", "gwb_physical"
+      "gwb_purpose",
+      "gwb_social",
+      "gwb_physical",
+      "gwb_community"
     ),
@@
   ) %>% 
-    mutate(
-      model = "No",
-      formula = str_glue("{y} ~ {x} + ({x} | country)")
+    # Drop year from formula for GWB outcomes (only ~1 year)
+    mutate(
+      model = "No", # No weights here
+      formula = if_else(
+        str_starts(y, "gwb_"),
+        str_glue("{y} ~ {x} + ({x} | country)"),
+        str_glue("{y} ~ {x} + ({x} | country) + ({x} | year) + ({x} | country:year)"),
+      )
     ) %>% 
@@
             formula = ..2, 
-            data = dat2
+            data = dat
           )
@@
 # Median association (with reversed negative experiences)
-tmp <- specs_avg %>% 
-  mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
-  summarise(across(c(estimate, std.error), median))
-```
-
-Our first research question concerned the average differences in well-being between individuals who had access to (mobile) internet or had used the internet in the past seven days, and those who didn't.
-We display the results of this analysis in Figure \@ref(fig:fig-rq1).
-The associations between (mobile) internet access and use and well-being were consistently positive.
-For the average country, individuals who had access to the internet reported approximately 0.08 units greater life satisfaction, positive experiences, and social life satisfaction, and 0.06 units lower negative experiences than individuals who did not have access.
-Results across the other two internet access and use predictors were of the same sign and comparable magnitude.
-To put these magnitudes to context, the models' standard deviations in well-being across countries ranged from XXX to XXX, representing the natural variation in well-being between countries.
-The observed differences in well-being between individuals who had access to or used the internet were of comparable magnitude.
-This suggests that the well-being differences, although they don't indicate causality and were numerically small, were of meaningful magnitude.
-
-Moreover, Figure \@ref(fig:fig-rq1) shows individual countries' observed difference scores as small points; they were very consistently in the same direction as the average contrasts, indicating that this difference held similarly across most countries.
-These results showed uniformly across the four well-being outcomes that individuals who had access to, or actively used the internet reported meaningfully greater well-being than those who did not.
+# tmp <- specs_avg %>% 
+#   mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
+#   summarise(across(c(estimate, std.error), median))
+```
+
+```{r}
+ysds <- summarise(dat, across(all_of(ys), ~sd(., na.rm = TRUE)))
+stdz_internet_ls <- number(specs_avg$estimate[1] / ysds[1,1,TRUE], .01)
+```
 
@@
 #| include: true
-#| fig.height: 5.4
+#| out.width: "\\textwidth"
+#| fig.env: "figure*"
+#| fig.height: 5.6
+#| fig.width: 9
 #| fig.cap: Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences.
@@
 Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\% confidence interval.
-
-tmp1 <- dat %>% 
+The GWBI outcomes did not overlap in time with mobile internet data.
+
+tmp1 <- dat_raw %>% 
   pivot_longer(starts_with("internet")) %>% 
@@
     across(
-      c(life_satisfaction:social_life), 
+      all_of(ys), 
       ~mean(., na.rm = TRUE)
@@
   mutate(z = Yes - No) %>% 
-  pivot_longer(c(No, Yes, z), names_to = "x")
+  pivot_longer(c(No, Yes, z), names_to = "x") %>% 
+  mutate(outcome = factor(outcome, levels = ys))
 
@@
       fct_drop()
-  )
+  ) %>% 
+  mutate(outcome = factor(outcome, levels = ys))
 
@@
     breaks = extended_breaks(7),
-    expand = expansion(.1)
+    expand = expansion(.01)
   ) +
@@
     data = specs_avg %>% 
-      filter(!str_detect(y, "gwb_")) %>% 
       mutate(
@@
         name = x, x = "No", outcome = y
-        ),
+      ) %>% 
+      mutate(outcome = factor(outcome, levels = ys)),
     aes(
@@
     x = -Inf, y = -Inf, 
-    size = 2.7, hjust = 0, vjust = 0, lineheight = 1, fill = NA,
-    label.size = 0, label.padding = unit(0.5, "line")
+    size = 2.5, hjust = 0, vjust = 0, lineheight = 1, fill = NA,
+    label.size = 0, label.padding = unit(0.3, "line")
   ) +
@@
     name ~ outcome, 
-    labeller = as_labeller(~sanitize_labels(.))
+    labeller = labeller(
+      .cols = ~sanitize_labels(.) %>% str_replace_all(" ", "\n"),
+      .rows = ~sanitize_labels(.)
+    )
   ) +
@@
 
-```{r}
-tmp1 <- dat %>% 
-  pivot_longer(starts_with("internet")) %>% 
-  drop_na(value) %>%
-  group_by(country, year, name, value) %>% 
-  summarise(
-    across(
-      c(life_satisfaction:social_life), 
-      ~mean(., na.rm = TRUE)
-    ),
-  ) %>% 
-  ungroup() %>% 
-  pivot_longer(contains("_"), names_to = "outcome", values_to = "y") %>% 
-  filter(!(name == "internet_phone" & str_detect(outcome, "gwb_"))) %>% 
-  pivot_wider(names_from = value, values_from = y) %>% 
-  mutate(z = Yes - No) %>% 
-  pivot_longer(c(No, Yes, z), names_to = "x")
-
-tmp2 <- tmp1 %>% 
-  group_by(year, name, outcome, x) %>% 
-  summarise(m = mean_cl_boot(value, conf.int = 0.95)) %>% 
-  ungroup() %>% 
-  unnest(m) %>% 
-  mutate(sig = sign(ymin) == sign(ymax)) %>% 
-  mutate(
-    decision = case_when(
-      ymin < 0 & ymax < 0 ~ "Negative",
-      ymin > 0 & ymax > 0 ~ "Positive",
-      !sig ~ "Not significant"
-    ) %>% 
-      factor(levels = c("Negative", "Not significant", "Positive")) %>% 
-      fct_drop()
-  )
-tmp2 %>% 
-  filter(x == "z") %>% 
-  ggplot(aes(year, y)) +
-  coord_cartesian(ylim = c(-0.2, 0.25)) +
-  geom_hline(yintercept = 0, linewidth = .1) +
-  geom_line(
-    data = tmp1 %>% filter(x == "z"),
-    aes(y = value, group = country),
-    alpha = .1, color = "grey60"
-  ) +
-  geom_ribbon(
-    aes(ymin = ymin, ymax = ymax),
-    alpha = .33
-  ) +
-  geom_line() +
-  facet_grid(
-    name ~ outcome, 
-    labeller = as_labeller(~sanitize_labels(.))
-  )
-```
+Our first research question concerned the average differences in well-being between individuals who had access to (mobile) internet or had used the internet in the past seven days, and those who didn't.
+We display the results of this analysis in Figure \@ref(fig:fig-rq1).
+The associations between internet access and well-being were consistently positive.
+For the average country, individuals who had access to the internet reported on average approximately 0.08 units greater life satisfaction, positive experiences, and social life satisfaction, and 0.06 units lower negative experiences than individuals who did not have access.
+Results regarding the more temporally restricted (2013-2015) GWBI outcomes portrayed a similar picture: Individuals with internet access reported approximately 0.08 units greater experiences of purpose, 0.1 unit greater physical, 0.02 units greater community, and 0.08 units greater social well-being than individuals without access.
+
+Results across the other two internet access and use predictors were of the same sign and comparable magnitude.
+Being an active internet user was associated with 0.03 to 0.08 unit increases in life satisfaction, positive experiences, social well-being and physical well-being, and with a 0.04 unit decrease in negative experiences.
+The overall association between being an active internet user and community well-being was not significantly different from zero.
+Mobile phone internet access predicted increases between 0.06 and 0.07 units.
+
+The estimates discussed above and in Figure \@ref(fig:fig-rq1) refer to percentages of the scale: To put these magnitudes to another context, the well-being outcomes' standard deviations across individuals, countries, and time ranged from `r number(min(ysds), .01)` to `r number(max(ysds), .01)`.
+In standardized terms, the observed differences were therefore quite small (e.g.
+the median life satisfaction difference was `r stdz_internet_ls` standard deviations between individuals who had access to the internet and those who did not), but not negligible.
+
+Moreover, Figure \@ref(fig:fig-rq1) shows individual countries' observed difference scores as small points; they were very consistently in the same direction as the average contrasts, indicating that this difference held similarly across most countries.
+These results showed uniformly across the eight well-being outcomes that individuals who had access to, or actively used the internet reported meaningfully greater well-being than those who did not.
+
+However, although the estimates in Figure \@ref(fig:fig-rq1) were surprisingly uniform across outcomes and predictors, they did not yet address our second, main research question: The robustness of this association across different analysis specifications and subgroups, and the extent to which internet access and use might independently predict individuals' well-being.
+To best answer this question, while at the same time appreciate the theoretical uncertainty in how, where, or for whom to study this association, we next turned to our main multiverse analysis.
 
@@
   mutate(
+    K = number2(K, 1),
     N = number2(N, 1),
-    across(c(Negative, `Not significant`, Positive), ~percent(., .01)),
+    across(c(Negative, `Not significant`, Positive), ~percent(., .1)),
     across(c(`0.25`, `0.5`, `0.75`), ~number(., .01))
@@
     .keep = "unused",
-    .after = 2
-  )
+    .after = 3
+  ) %>% 
+  mutate(Outcome = factor(Outcome, levels = sanitize_labels(c(ys, "Total"))))
 mvs2 %>%
@@
     caption = "Summary of multiverse analysis of associations between internet access (or use) and well-being.", 
-    note = 'N is the median sample size across specifications.
+    note = 'K is the number of specifications, and N is the median sample size across specifications.
 "Total" indicates quantities across well-being outcomes (we reversed associations with negative experiences for this aggregate number).',
     col_spanners = list(
-      "Association magnitude" = c(3, 4),
-      "Proportions of significant associations" = c(5, 7)
-    ), 
-    placement = "ht"
-  )
-```
-
-However, although the estimates in Figure \@ref(fig:fig-rq1) were surprisingly uniform across outcomes and predictors, they did not yet address our second, main research question: The extent to which internet access and use might independently contribute to individuals' well-being, and whether the associations might be unique to specific subgroups of individuals.
-To best answer this question, while at the same time appreciate the theoretical uncertainty in how, where, or for whom to study this association, we next turned to our main multiverse analysis.
-In the analysis presented here, we examined the association between well-being and internet access or use over `r number2(n_specs_main)` model specifications.
-In appendix A, we present an additional `r number2(n_specs_gwb)` models examining the GWBI outcomes in 2013 to 2015.
-
-We summarize the results of this multiverse analysis in Table \@ref(tab:tbl-multiverse).
-First, for life satisfaction, the median sample size across specifications was `r mvs$N[[1]]`.
-Answering 'Yes' to an internet access or use question was associated with a median `r mvs$Median[[1]]` unit increase in life satisfaction.
-The central 50% of the distribution of associations was within the `r mvs$IQR[[1]]` interval.
-The association between internet access or use and life satisfaction was positive in `r mvs$Positive[[1]]` of model specifications.
-Numerical results for the other three well-being outcomes were of similar magnitude, and the total proportion of specifications that resulted in negative associations was only `r mvs$Negative[[5]]`.
-
-Figure \@ref(fig:fig-multiverse) shows that across all model specifications, the multilevel model's estimated association between internet access and use, for the average country, was very consistently positive.
-Each vertical slice of figure \@ref(fig:fig-multiverse) identifies a model specification, indexed on the x-axis.
-The resulting estimated association is displayed in panel A.
-The model's specification is the combination of covariates and grouping variables enumerated in panel B.
-For example, one point could represent the association between internet access (X = Internet access in panel B) for males aged 65 or over (Age), with a model that included only an intercept (Covariates = 1) as additional covariates, in the year 2019, for a model estimated without weights (No weights).
+      "Association magnitude" = c(4, 5),
+      "Proportions of significant associations" = c(6, 8)
+    ), 
+    font_size = "scriptsize"
+  )
+```
 
@@
 #| fig.env: "figure*"
-#| fig.height: 7.8
+#| fig.height: 6
 #| fig.width: 9
-#| fig.cap: Multiverse analysis results of associations between three internet use predictors and four well-being outcomes.
-A.
-Estimated associations, in order of increasing magnitude, shown separately for each of the four main well-being outcomes.
+#| fig.cap: Multiverse analysis results of associations between three internet use predictors and eight well-being outcomes.
+The estimated associations are ordered by increasing magnitude; the x-axis denotes the ordered number of (predictor * age * sex * covariate combination * weights) specification.
 The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point.
-B.
-A dashboard of model specifications.
-Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
-p1 <- mv %>% 
+draw_sca <- function(Y) {
+  this_mv <- filter(mv, y %in% Y) %>% 
+    mutate(y = factor(y, levels = Y))
+  p1 <- this_mv %>% 
     ggplot(aes(i, estimate, col = decision)) +
@@
     geom_ysidepoint(
-    data = mv %>% 
+      data = this_mv %>% 
         group_by(y) %>% 
@@
       scales = "free_x", 
-    nrow = 1, 
+      ncol = 4, 
       drop = TRUE,
@@
 
-p2 <- mv %>% 
+  p2 <- this_mv %>% 
     mutate(
@@
     pivot_longer(
-    c(year, age, sex, x, covariate, weights), 
+      c(age, sex, x, covariate, weights), 
       values_transform = as.character
@@
         name, 
-      levels = c("x", "age", "sex", "covariate", "year", "weights"),
-      labels = c("X", "Age", " ", "Covariates", "Year", "  ")
+        levels = c("x", "age", "sex", "covariate", "weights"),
+        labels = c("X", "Age", " ", "Covariates", "  ")
       ),
@@
       size = .1, 
-    position = position_quasirandom(groupOnX = FALSE, width = .2)
+      position = position_quasirandom(width = .2)
     ) +
@@
       rows = vars(name), 
-    scales = "free_y", 
+      scales = "free", 
       space = "free_y", 
@@
       axis.title.y = element_blank(),
-    # axis.text.x = element_blank(),
       legend.position = "none"
@@
 
-((p1 / p2) +
-  plot_layout(heights = c(3.2, 6.8))) +
-  plot_annotation(tag_levels = "A")
-```
+  list(a = p1, b = p2)
+}
+tmp <- draw_sca(ys)
+tmp$a +
+  coord_cartesian(ylim = c(-0.1, 0.125)) + 
+  theme(axis.title.x = element_text())
+```
+
+We summarize the results of this multiverse analysis in Table \@ref(tab:tbl-multiverse).
+First, for life satisfaction, the median sample size across specifications was `r number2(mvs$N[[1]])` individuals.
+Answering 'Yes' to an internet access or use question was associated with a median `r number(mvs[["0.5"]][[1]], .01)` unit increase in life satisfaction.
+The central 50% of the distribution of associations was within the `r number(mvs[["0.25"]][[1]], .01)`, `r number(mvs[["0.75"]][[1]], .01)` interval.
+The association between internet access or use and life satisfaction was positive in `r percent(mvs$Positive[[1]], .01)` of model specifications.
+Numerical results for the other well-being outcomes were of similar magnitude, and the total proportion of specifications that resulted in negative associations was only `r percent(mvs$Negative[[9]], .01)`.
+
+Figure \@ref(fig:fig-multiverse) shows that across all model specifications, the multilevel model's estimated association between internet access and use for the average country was very consistently positive.
+Each estimated association in Figure \@ref(fig:fig-multiverse) identifies a model specification (e.g.
+the coefficient for internet access for 15 to 24 year old males, adjusting for health problems and income, estimated with weights), which are ordered on increasing association magnitude.
+
+Whereas Figure \@ref(fig:fig-rq1) showed that the overall average associations were consistent across internet adoption predictors and well-being outcomes, Figure \@ref(fig:fig-multiverse) highlights a surprising consistency in that association across demographic subgroups and, moreover, in model covariate specifications.
+If these associations were spurious associations caused by any of the covariates we considered, we should observe clusters of non-significant or reversed estimates for specific covariate sets.
+This was mostly not the case: Figures S1 and S2 show additional "dashboards" that indicate the covariate specifications for each estimate in Figure \@ref(fig:fig-multiverse), and we did not discern any clear patterns among them with respect to the covariate specifications.
+
+Notably, however, Figure \@ref(fig:fig-multiverse) shows a large group of negative associations between community well-being and internet adoption among otherwise mostly positive relationships.
+To examine these differences further, Figure \@ref(fig:fig-multiverse-zoom) focuses on variability in the associations across demographics and covariate specifications.
+The association between community well-being and internet adoption was particular to active internet use (rather than access) and individuals in the youngest 15 to 24 age category.
 
@@
 #| fig.env: "figure*"
-#| fig.cap: Median associations between the internet predictors and well-being outcomes by sex and age, ordered by covariate specification.
-The specifications are ordered as in Figure 2; where greater numbers indicate more covariates in the model.
+#| fig.width: 9
+#| fig.height: 5
+#| fig.cap: Associations between the internet predictors and well-being outcomes by sex and age, ordered by covariate specification.
+The specifications are ordered such that greater numbers indicate more covariates in the model.
+Estimates are means across weighted and non-weighted models.
 p1 <- specs %>% 
+  mutate(y = factor(y, ys)) %>% 
   filter(term == x) %>% 
-  reframe(
-    q = c(.1, .5, .9),
-    value = quantile(estimate, probs = c(.1, .5, .9)),
+  summarise(
+    estimate = mean(estimate),
+    n = n(),
     .by = c(covariate, age, sex, x, y)
   ) %>%
-  pivot_wider(names_from = q) %>% 
   mutate(
@@
   ) %>%
-  ggplot(aes(i, `0.5`)) +
+  ggplot(aes(i, estimate)) +
   geom_hline(yintercept = 0, size = .1) +
@@
   scale_y_continuous(
-    "Median association"
+    "Mean association"
   ) +
@@
   ) +
+  guides(color = guide_legend(reverse = TRUE)) +
   geom_line(aes(group = age, col = age)) +
@@
     x + sex ~ y,
-    labeller = as_labeller(sanitize_labels)
+    labeller = labeller(
+      .cols = ~sanitize_labels(.) %>% str_replace_all(" ", "\n"),
+      .rows = ~sanitize_labels(.)
+    )
   )
@@
 
-```{r}
-specs %>% 
-  filter(term == x) %>% 
-  reframe(
-    q = c(.1, .5, .9),
-    value = quantile(estimate, probs = c(.1, .5, .9)),
-    .by = c(covariate, age, x, y)
-  ) %>% 
-  pivot_wider(names_from = q) %>% 
-  mutate(
-    covariate = fct_relevel(covariate, unique(specs$covariate)),
-    covariate = fct_recode(covariate, `No covariates` = "1")
-  ) %>%
-  ggplot(aes(`0.5`, covariate, col = age)) +
-  geom_vline(xintercept = 0, size = .1) +
-  scale_color_brewer(palette = "Set1") +
-  scale_x_continuous(
-    "Estimated association"
-  ) +
-  ggstance::geom_pointrangeh(
-    aes(xmin = `0.1`, xmax = `0.9`),
-    size = .1, fatten = 0.25,
-    position = position_dodge(width = 1)
-  ) +
-  facet_nested(
-    x ~ y,
-    labeller = as_labeller(sanitize_labels)
-  )
-```
-
-A visual examination of Figure \@ref(fig:fig-multiverse) did not suggest any strong patterns in subgroups or covariates such that there would have been an especially strong relation for a specific subgroup or covariate inclusion.
-If that were the case, we should have observed a clustering of points in the dashboard along a single covariate or grouping factor indicating a distinctly strong relation among one or more of the outcomes, which we did not.
-However, the large number of specifications in this figure might make it difficult to tease apart factors that might have led to meaningful variation among the estimated associations.
-To help see the variance among results with respect to covariate specification, Figure XYZ shows the median associations between each outcome and predictor, separately for each covariate specification.
-From this figure, we observe that while generally increasing the number and complexity of covariates in the model did somewhat decrease the magnitudes of the estimated associations, they remained positive and significantly so for most cases.
-This observations shows that even after adjusting for all possible combinations of covariates, the relationships between internet access or use and well-being remained positive.
+More generally, Figure \@ref(fig:fig-multiverse-zoom) also shows that while increasing the number and complexity of covariates in the model did tend to decrease the magnitudes of the estimated associations, they typically remained positive.
+This observation shows that even after adjusting for all possible combinations of the covariates that we considered, the relationships between internet access or use and well-being remained positive.
 In turn, this suggests that the contributions of internet access and use on well-being were independent of the covariates we selected for, and thus might indicate causal relations.
-
-```{r}
-#| eval: false
-library(ggstance)
-library(ggh4x)
-specs %>% 
-  drop_na(age, sex) %>% 
-  filter(
-    covariate %in% c("1", "healthproblems + income"),
-    !str_detect(y, "gwb"),
-    year %% 2 == 1,
-    year >= 2015
-  ) %>% 
-  ungroup() %>% 
-  mutate(
-    sig = sign(conf.low) == sign(conf.high),
-    covariate = factor(
-      covariate, labels = c("No covariates", "Income and health problems")
-    ),
-    color = str_glue("{sex}\n{covariate}")
-  ) %>% 
-  arrange(sex, covariate) %>% 
-  mutate(color = fct_inorder(color)) %>% 
-  ggplot(aes(year, estimate, col = color)) +
-  scale_color_manual(
-    "Model covariates",
-    values = c("firebrick1", "firebrick4", "dodgerblue1", "dodgerblue4")
-  ) +
-  scale_shape_manual(values = c(21, 19)) +
-  scale_y_continuous(
-    "Estimated association (95%CI)",
-    labels = ~percent(., 1)
-  ) +
-  scale_x_continuous(
-    "Year",
-    breaks = c(2015, 2017, 2019, 2021),
-    labels = ~str_glue("'{str_sub(., 3, 4)}")
-  ) +
-  geom_hline(yintercept = 0, linewidth = .1) +
-  geom_pointrange(
-    aes(ymin = conf.low, ymax = conf.high, shape = sig),
-    position = position_dodge2(1),
-    fatten = 2.5, fill = "white", stroke = .8
-  ) +
-  guides(shape = "none") +
-  facet_nested(
-    age ~ y + x, scales = "free_x",
-    labeller = as_labeller(sanitize_labels)
-  ) +
-  theme(
-    legend.position = "bottom", 
-    legend.title = element_blank()
-  )
-```
-
-We then focused on another aspect of potential variation among the associations between internet access or use and well-being. Figure XYZ shows the median associations for each demographic
+(Although we highlight the evidence here for causal claims is less than thin.)
 
@@
 In this study, we examined associations between internet use and access, and a broad variety of well-being indicators in a representative sample of `r number2(nrow(dat))` individuals across `r length(unique(dat$country))` countries within an age range that spanned from late adolescence to older adults.
-We found that on average across countries and demographics, individuals who had internet access, mobile internet access, or actively used the internet reported greater levels of life satisfaction, positive experiences, and social well-being, and lower levels of negative experiences.
-
-The main thrust of our analysis was to examine to what extent this positive association between internet and well-being was sensitive to different demographic groups, time periods, and modelling decisions.
-Furthermore, we attempted to estimate the unique contributions of internet on well-being by examining this association across `r length(unique(specs$covariate))` different permutations of sets of plausible covariates that might otherwise create or mask associations.
-Across `r number2(nrow(filter(specs, term == x)))` of such model specifications, `r mvs$Positive[5]` of the associations were significantly positive, and only `r mvs$Negative[5]` were negative.
-We thus conclude that the proliferation of (mobile) internet access and increasing engagement with the internet has been a net benefit to the well-being of individuals around the world.
-
-Nevertheless, our conclusion is qualified by a number of factors.
+We found that on average across countries and demographics, individuals who had internet access, mobile internet access, or actively used the internet reported greater levels of life satisfaction, positive experiences, experiences of purpose, and physical, community, and social well-being, and lower levels of negative experiences.
+
+The main thrust of our analysis was to examine to what extent this positive association between internet and well-being was sensitive to different demographic groups and modelling decisions.
+Furthermore, we attempted to estimate the unique contributions of internet on well-being by examining this association across `r length(cs)` different permutations of sets of plausible covariates that might otherwise create or mask associations.
+Across `r number2(nrow(specs))` of such model specifications, `r percent(mvs$Positive[9], .1)` of the associations were significantly positive, and only `r percent(mvs$Negative[9], .1)` were negative.
+These results therefore suggest that the proliferation of (mobile) internet access and increasing engagement with the internet has been a net benefit to the well-being of individuals around the world.
+
+Nevertheless, this conclusion is qualified by a number of factors.
 First, we compared individuals to each other.
@@
 
-Second, while between-person data such as we studied can inform inferences about average causal effects, longitudinal studies that track individuals and their internet use over time would be more informative in understanding the contexts of how and why an individual is affected by the internet [@rohrerTheseAreNot2021].
+Second, while between-person data such as we studied can inform inferences about average causal effects, longitudinal studies that track individuals and their internet use over time would be more informative in understanding the contexts of how and why an individual might be affected by internet technologies and platforms [@rohrerTheseAreNot2021].
 
@@
 
-Fourth, the validity of self-reported measures of technology engagement is found lacking, as self-reported quantities of use correlate only modestly with actual use, as measured for example by apps installed on smartphones.
-In our study, we used reports of whether an individual has access to or has used the internet in the past week.
-Nevertheless, we believe it is more difficult to be mistaken in answering those questions than it would be if answering questions about e.g.
-average hours used in the past year.
-
-To overcome these limitations, we think the best way forward for this field is the expend more resources on collecting larger and more representative longitudinal datasets that include validated measurements of the constructs that researchers care about.
-In addition, these datasets should include accurate data on individuals' engagement with the internet in lieu of self-reports.
+Fourth, the validity of self-reported measures of technology engagement is found lacking, as self-reported quantities of use correlate only modestly with actual use, as measured for example by apps installed on smartphones [@parrySystematicReviewMetaanalysis2021; @wu-ouyangOverestimatingUnderestimatingCommunication2022].
+In our study, we used reports of whether an individual has access to or has used the internet in the past week, which may suffer from these biases.
+Nevertheless, we believe it is more difficult to be mistaken in answering those questions than e.g.
+questions about average hours used in the past year.
+
+Finally, we further highlight the tentative-at-most nature of our results with respect to causal effects of internet access and use on individuals' well-being.
+Causal inference from observational data, such as studied here, is notoriously difficult [@rohrerThinkingClearlyCorrelations2018; @vanderweeleCausalInferenceLongitudinal2016].
+Critical theoretical assumptions must be made and properly applied in the statistical models in order to approach unbiased causal estimates, steps that we did not take in the current work.
+We nevertheless remain hopeful that the clarity with which we hoped to address this issue will provide a solid foundation for future work on internet technologies causal effects [@groszTabooExplicitCausal2020].
+
+To overcome these limitations, we think the best way forward for this field is to expend more resources on collecting larger and more representative longitudinal datasets that include validated measurements of the constructs that researchers care about.
+In addition, these datasets should include accurate data on individuals' engagement with internet technologies in lieu of self-reports.
 Fortunately, both of these data are already collected; large cohort-based surveys in many countries already track individuals' psychological states over time, and internet platforms are infamous for collecting detailed data on their users' behaviors.
-A significant but potentially fruitful challenge then would be to marry those two streams of data for a more detailed understanding of internet technologies in individuals' lives.
+A significant but potentially fruitful challenge then would be to marry those two streams of data and use them in transparent and independent scientific inquiry for a more detailed understanding of internet technologies in individuals' lives.
 
@@
 
-Conceptualization: MV & AKP; Data curation: MV; Formal Analysis: MV; Funding acquisition: AKP; Investigation: MV & AKP; Methodology: MV & AKP; Project administration MV & AKP; Resources: AKP; Software: MV; Supervision: AKP; Visualization: MV & AKP; Writing – original draft: MV & AKP; Writing – review & editing: MV & AKP.
+Conceptualization: MV & AKP; Data curation: MV; Formal Analysis: MV; Funding acquisition: AKP; Investigation: MV & AKP; Methodology: MV & AKP; Project administration MV & AKP; Resources: AKP; Software: MV; Supervision: AKP; Visualization: MV & AKP; Writing -- original draft: MV & AKP; Writing -- review & editing: MV & AKP.
 
@@
 
+```{=tex}
 \clearpage
 \onecolumn
-
-# Supplementary online analyses to *Internet and well-being* (Vuorre & Przybylski, 2022)
+```
+# Supplementary online material to *A multiverse analysis of the associations between internet use and well-being* (Vuorre & Przybylski, tbd)
 
@@
 
+```{=tex}
 \setcounter{page}{1}
@@
 \setcounter{figure}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
-
+\renewcommand{\thetable}{SOM-\arabic{table}}
+\renewcommand{\thefigure}{SOM-\arabic{figure}}
+```
 Table \@ref(tab:tbl-correlation-matrix) shows the pearson correlations between all variables, across demographics, time and space.
@@
     income, healthproblems, relationship,
-    laworder, foodshelter,
     life_satisfaction, negative_experiences, positive_experiences, social_life,
@@
 
-```{r}
-#| label: fig-summary
+Figures \@ref(fig:fig-sca-full-1) and \@ref(fig:fig-sca-full-2) show the full specification curve analysis plots, including the "dashboards" in panels B.
+
+```{r}
 #| include: true
-#| fig.height: 6.5
-#| fig.cap: Key variables' averages and availability over time.
+#| label: fig-sca-full-1
+#| out.width: "\\textwidth"
+#| fig.env: "figure*"
+#| fig.height: 9
+#| fig.width: 9
+#| fig.cap: Multiverse analysis results of associations between three internet use predictors and four main well-being outcomes.
 A.
-Internet access and use variables.
+Estimated associations, in order of increasing magnitude, shown separately for each of the four main well-being outcomes.
+The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point.
 B.
-Covariates, excluding income because it is on a different scale.
-C.
-Well-being outcomes, excluding the GWB indices, because they were only collected in 2013 to 2015.
-
-# Figure
-tmp <- dat %>% 
-  select(
-    year, starts_with("internet"),
-    life_satisfaction, negative_experiences, 
-    positive_experiences, social_life, 
-    healthproblems, laworder, relationship
-  ) %>% 
-  mutate(across(c(where(is.factor)), ~as.numeric(.)-1)) %>% 
-  group_by(year) %>% 
-  summarise(
-    across(
-      everything(), 
-      list(valid = ~sum(!is.na(.)) / n(), mean = ~mean(., na.rm = TRUE)), 
-      .names = "{.col}.{.fn}"
-    )
-  ) %>% 
-  mutate(across(ends_with("valid"), ~if_else(. < 0.1, NaN, .))) %>% 
-  pivot_longer(-c(year)) %>% 
-  separate(name, c("variable", "measure"), sep = "\\.") %>% 
-  mutate(
-    group = case_when(
-      str_detect(variable, "internet") ~ "A",
-      variable %in% 
-        c("income", "healthproblems", "relationship", "laworder") ~ "B",
-      TRUE ~ "C"
-    )
-  )
-
-p1 <- tmp %>% 
-  ggplot(aes(year, value, col = measure)) +
-  scale_color_brewer(
-    "Variable",
-    palette = "Dark2",
-    labels = ~factor(., levels = c("mean", "valid"), labels = c("Mean response", "Valid responses"))
-  ) +
-  scale_y_continuous(
-    limits = 0:1,
-    expand = expansion(c(0.03, 0.06)),
-    labels = ~percent(., 1)
-  ) +
-  scale_x_continuous(
-    "Year",
-    breaks = extended_breaks(5)
-  ) +
-  geom_line(linewidth = 0.8) +
-  # geom_point() +
-  facet_wrap(
-    "variable", 
-    scales = "free_x",
-    labeller = as_labeller(sanitize_labels),
-    nrow = 1
-  ) +
-  theme(
-    axis.title.y = element_blank(),
-    legend.position = "bottom", 
-    legend.title = element_blank()
-  )
-
-p2 <- (p1 %+% filter(p1$data, group == "A")) + 
-  theme(
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-p3 <- (p1 %+% filter(p1$data, group == "B")) +
-  theme(
-    legend.position = "none",
-    axis.title.x = element_blank()
-  )
-p4 <- (p1 %+% filter(p1$data, group == "C"))
-(p2 / p3 / p4) +
+A dashboard of model specifications.
+Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
+tmp <- draw_sca(ys[1:4])
+((tmp$a / tmp$b) +
+      plot_layout(heights = c(3.2, 6.8))) +
     plot_annotation(tag_levels = "A")
@@
 ```{r}
-#| label: fig-internet-by-sex
 #| include: true
-#| fig.height: 2.8
-#| fig.cap: Overall proportions of each country's internet users by sex.
-Points are individual countries.
-The regression line indicates that males overall were more likely to have internet access and used internet more frequently, but this divide was smaller for countries where overall adoption was greater.
-dat %>% 
-  group_by(country, year, sex) %>% 
-  summarise(across(starts_with("internet"), ~mean(as.numeric(.)-1, na.rm = TRUE))) %>% 
-  group_by(country, sex) %>% 
-  summarise(across(starts_with("internet"), ~mean(., na.rm = TRUE))) %>% 
-  ungroup() %>% 
-  mutate(m = rowMeans(select(., starts_with("internet")), na.rm = TRUE)) %>% 
-  arrange(m) %>% 
-  mutate(country = fct_inorder(country)) %>% 
-  select(-m) %>% 
-  pivot_longer(starts_with("internet")) %>%
-  pivot_wider(names_from = sex, values_from = value) %>% 
-  ggplot(aes(Male, Female)) +
-  scale_x_continuous(
-    "Males",
-    labels = ~percent(., 1)
-  ) +
-  scale_y_continuous(
-    "Females",
-    labels = ~percent(., 1)
-  ) +
-  geom_abline(linetype = "dotted") +
-  geom_point(shape = 1, col = "dodgerblue1") +
-  geom_smooth(method = "lm", se = FALSE, col = "dodgerblue4") +
-  facet_wrap(
-    "name",
-    nrow = 1,
-    labeller = as_labeller(sanitize_labels),
-  ) +
-  theme(
-    aspect.ratio = 1
-  )
-```
+#| label: fig-sca-full-2
+#| out.width: "\\textwidth"
+#| fig.env: "figure*"
+#| fig.height: 9
+#| fig.width: 9
+#| fig.cap: Multiverse analysis results of associations between three internet use predictors and four GWBI well-being outcomes.
+A.
+Estimated associations, in order of increasing magnitude, shown separately for each of the four GWBI well-being outcomes.
+The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point.
+B.
+A dashboard of model specifications.
+Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
+tmp <- draw_sca(ys[5:8])
+((tmp$a / tmp$b) +
+      plot_layout(heights = c(3.2, 6.8))) +
+    plot_annotation(tag_levels = "A")
+```

### 2023-03-22 ms.Rmd
edit mcedit

@@
 documentclass: apa7
-classoption: doc
+classoption: jou
 header-includes:
@@
     number_sections: false
-    keep_tex: true
+    keep_tex: false
   papaja::apa6_docx: 
@@
 abstract: |
+  \paragraph{Abstract}
   With internet technologies' and platforms' increasing global penetration, their potential consequences to well-being remain debated.
@@
 Then, we examined these associations' robustness in a multiverse of `r number2(nrow(specs))` analysis and subgroup specifications.
-`r percent(mvs$Positive[9], .01)` of these specifications resulted in positive and statistically significant associations between internet connectivity and well-being.
-These results indicate that (mobile) internet access and active internet use predict well-being positively and independent from a set of plausible confounders.
-
-  \emph{Statement of relevance.} Are internet technologies, such as smartphones and social media, psychologically harmful?
+`r percent(mvs$Positive[9], .1)` of these specifications resulted in positive and statistically significant associations between internet connectivity and well-being.
+These results indicate that (mobile) internet access and active internet use predict well-being positively and independently from a set of plausible alternatives.
+  \paragraph{Statement of relevance}
+  Are internet technologies, such as smartphones and social media, psychologically harmful?
 Past results have generally offered mixed evidence and, critically, focused on a narrow slice of the global population.
@@
     ), 
-    font_size = "scriptsize"
+    font_size = "scriptsize",
+    span_text_columns = TRUE
   )
@@
 The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point.
-draw_sca <- function(Y) {
+draw_sca <- function(mv, Y) {
   this_mv <- filter(mv, y %in% Y) %>% 
@@
     scale_color_manual(values = c("firebrick2", "grey70", "dodgerblue2")) +
-    scale_y_continuous(position = "right",
+    scale_y_continuous(
+      position = "right",
       "Estimated association (95%CI)",
@@
 }
-tmp <- draw_sca(ys)
+tmp <- mv %>% 
+  arrange(desc(std.error)) %>% 
+  # Take out one degenerate estimate for this plot
+  slice(-1) %>% 
+  draw_sca(ys)
 tmp$a +
@@
     starts_with("internet"),
-    income, healthproblems, relationship,
+    income, healthproblems, relationship, foodshelter,
     life_satisfaction, negative_experiences, positive_experiences, social_life,
@@
 Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
-tmp <- draw_sca(ys[1:4])
+tmp <- draw_sca(mv, ys[1:4])
 ((tmp$a / tmp$b) +
@@
 Each point in the small panels indicates the value of the grouping variable or covariate specification for the model indicated on the x-axis.
-tmp <- draw_sca(ys[5:8])
+tmp <- draw_sca(mv, ys[5:8])
 ((tmp$a / tmp$b) +

### 2023-03-27 ms.Rmd
URLs

@@
   - name: Matti Vuorre
-    affiliation: 1
+    affiliation: "1,2"
     corresponding: yes
@@
   - name: Andrew K. Przybylski
-    affiliation: 1
+    affiliation: "2"
     email: andy.przybylski@oii.ox.ac.uk
@@
   - id: 1
+    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
+  - id: 2
     institution: Oxford Internet Institute, University of Oxford
@@
   \paragraph{Abstract}
-  With internet technologies' and platforms' increasing global penetration, their potential consequences to well-being remain debated.
-While these technologies have spurred novel forms of commerce, education, and leisure, many are worried that they might negatively affect individuals by, for example, displacing time spent on other healthy activities.
-Findings on internet technologies' effects on well-being have been, to date, inconclusive and of limited geographic and demographic scope.
-We examined the extent to which having (mobile) internet access or actively using the internet predicted eight well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals across `r length(unique(dat$country))` countries.
+  Internet technologies' and platforms' potential psychological consequences remain debated.
+While these technologies have spurred new forms of commerce, education, and leisure, many are worried that they might negatively affect individuals by, for example, displacing time spent on other healthy activities.
+Relevant findings to date have been inconclusive and of limited geographic and demographic scope.
+We examined whether having (mobile) internet access or actively using the internet predicted eight well-being outcomes from `r yr` among `r number2(nrow(dat))` individuals across `r length(unique(dat$country))` countries.
 We first queried the extent to which well-being varied as a function of internet connectivity.
-Then, we examined these associations' robustness in a multiverse of `r number2(nrow(specs))` analysis and subgroup specifications.
-`r percent(mvs$Positive[9], .1)` of these specifications resulted in positive and statistically significant associations between internet connectivity and well-being.
-These results indicate that (mobile) internet access and active internet use predict well-being positively and independently from a set of plausible alternatives.
+Then, we examined these associations' robustness in a multiverse of `r number2(nrow(specs))` analysis specifications.
+`r percent(mvs$Positive[9], .1)` of these resulted in positive and statistically significant associations between internet connectivity and well-being.
+These results indicate that internet access and use predict well-being positively and independently from a set of plausible alternatives.
   \paragraph{Statement of relevance}
@@
 We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
-All our code and a simulated GWP dataset is available at [DOI].
+All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923.
 We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below).
@@
 
-Notably, however, Figure \@ref(fig:fig-multiverse) shows a large group of negative associations between community well-being and internet adoption among otherwise mostly positive relationships.
-To examine these differences further, Figure \@ref(fig:fig-multiverse-zoom) focuses on variability in the associations across demographics and covariate specifications.
-The association between community well-being and internet adoption was particular to active internet use (rather than access) and individuals in the youngest 15 to 24 age category.
-
 ```{r}
@@
 
-More generally, Figure \@ref(fig:fig-multiverse-zoom) also shows that while increasing the number and complexity of covariates in the model did tend to decrease the magnitudes of the estimated associations, they typically remained positive.
+However, Figure \@ref(fig:fig-multiverse) shows a notable group of negative associations between community well-being and internet adoption among otherwise mostly positive relationships.
+To examine these differences further, Figure \@ref(fig:fig-multiverse-zoom) focuses on variability in the associations across demographics and covariate specifications.
+The association between community well-being and internet adoption was particular to active internet use (rather than access) and individuals in the youngest 15 to 24 age category.
+
+More generally, Figure \@ref(fig:fig-multiverse-zoom) also shows that while increasing the number of covariates in the model did tend to decrease the magnitudes of the estimated associations, they typically remained positive.
 This observation shows that even after adjusting for all possible combinations of the covariates that we considered, the relationships between internet access or use and well-being remained positive.
@@
 The debate over internet platforms' and technologies' effects on individuals' psychological well-being remains a central topic because of their potentially global consequences.
-While past results on this topic have been mixed, the overwhelming majority of studies have examined convenience samples from the global north, thereby ignoring the fact that the penetration of the internet has been a global phenomenon.
+While past results on this topic have been mixed, the overwhelming majority of studies have examined convenience samples from the global north, thereby ignoring the fact that the penetration of the internet has been, and continues to be, a global phenomenon.
 In this study, we examined associations between internet use and access, and a broad variety of well-being indicators in a representative sample of `r number2(nrow(dat))` individuals across `r length(unique(dat$country))` countries within an age range that spanned from late adolescence to older adults.
@@
 
-Nevertheless, this conclusion is qualified by a number of factors.
+We did, however, observe a notable group of negative associations between internet use and community well-being.
+These negative associations were restricted to a portion of analyses concerning young (15-24 year old) individuals, and mostly females.
+These associations occurred across the full spectrum of covariate specifications, and thereby were not likely driven by a particular model specification.
+Further research should investigate whether low community well-being drives engagement with the internet, or vice versa.
+
+Nevertheless, our conclusions are qualified by a number of factors.
 First, we compared individuals to each other.

### 2023-05-11 ms.Rmd
Start new draft

@@
 classoption: jou
+csl: "pnas.csl"
 header-includes:
@@
 These results indicate that internet access and use predict well-being positively and independently from a set of plausible alternatives.
-  \paragraph{Statement of relevance}
+  \paragraph{Significance statement}
   Are internet technologies, such as smartphones and social media, psychologically harmful?
-Past results have generally offered mixed evidence and, critically, focused on a narrow slice of the global population.
-At the same time, stakeholders from international health bodies to technology companies are investing in regulation and tools to protect internet users' well-being.
-We examined 2.5 million individual's, from 168 nations, psychosocial well-being and internet adoption and use over a period of fifteen years.
+Past results have offered mixed evidence and, critically, focused on a narrow slice of the global population.
+Stakeholders from international health bodies to technology companies are investing in regulation and tools to protect internet users' well-being.
+We examined 2.5 million individual's psychosocial well-being and internet adoption and use over a period of fifteen years.
 We find that (mobile) internet adoption and use predict positive well-being and that this association is robust across thousands of adjustments for alternative explanations and demographic subgroups.
-While merely suggestive of causal associations, our results highlight social scientists' need for more transparent access to the large databases currently held behind the closed doors of the technology industry.
+While merely suggestive of causal associations, our results highlight a need for more transparent access to large databases currently held behind the closed doors of the technology industry.
 ---

### 2023-09-12 ms.Rmd
New journal

@@
 authornote: |
-  \noindent \textbf{This manuscript is not yet peer-reviewed.}
-
+  \noindent \textbf{This manuscript is not yet peer-reviewed. The preprint is available at https://psyarxiv.com/jp5nd/}
+  We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
+All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923.
+We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below).
+This study was not pre-registered.
 keywords: well-being, internet technology, technology effects
@@
 documentclass: apa7
-classoption: jou
-csl: "pnas.csl"
+classoption: doc
 header-includes:
@@
 abstract: |
-  \paragraph{Abstract}
   Internet technologies' and platforms' potential psychological consequences remain debated.
@@
 These results indicate that internet access and use predict well-being positively and independently from a set of plausible alternatives.
-  \paragraph{Significance statement}
-  Are internet technologies, such as smartphones and social media, psychologically harmful?
-Past results have offered mixed evidence and, critically, focused on a narrow slice of the global population.
-Stakeholders from international health bodies to technology companies are investing in regulation and tools to protect internet users' well-being.
-We examined 2.5 million individual's psychosocial well-being and internet adoption and use over a period of fifteen years.
-We find that (mobile) internet adoption and use predict positive well-being and that this association is robust across thousands of adjustments for alternative explanations and demographic subgroups.
-While merely suggestive of causal associations, our results highlight a need for more transparent access to large databases currently held behind the closed doors of the technology industry.
 ---
@@
 We then sought to probe the robustness of these associations by conducting a series of multiverse analyses that examined how national, demographic, and individual factors might serve to mask or create links between internet connectivity and well-being.
-
-# Open Practices Statement
-
-We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
-All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923.
-We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below).
-This study was not pre-registered.
 
@@
 We used R [@rcoreteamLanguageEnvironmentStatistical2022] for analyses and the lme4 package for estimating the multilevel models [@batesFittingLinearMixedEffects2015].
+
+# Data availability statement
+
+We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
+All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923.
+We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below).
+This study was not pre-registered.
 

### 2023-11-13 ms.Rmd
Update renv

@@
 keywords: well-being, internet technology, technology effects
-wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
+wordcount: "4,217"
 bibliography: references.bib
@@
 #| include: false
+
 library(papaja)
@@
 library(tidyverse)
-library(ragg)
 opts_chunk$set(
   include = FALSE,
-  cache = TRUE,
-  dev = "ragg_png"
+  cache = TRUE
 )
@@
 # Parallel computation options
-MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
-if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
+MAX_CORES <- as.numeric(
+  Sys.getenv(
+    "MAX_CORES", 
+    unset = parallel::detectCores(logical = FALSE)
+  )
+)
 CORES <- MAX_CORES - 2
@@
 #| label: data-clean
+
 path <- "data-raw/gwp.rds"

### 2023-11-13 ms.Rmd
Improve reproducibility

@@
     address: Tilburg University
-    email: m.j.vuorre@tilburguniversity.edu
+    email: mjvuorre@uvt.nl
   - name: Andrew K. Przybylski
@@
 authornote: |
-  \noindent \textbf{This manuscript is not yet peer-reviewed. The preprint is available at https://psyarxiv.com/jp5nd/}
+  \textbf{This manuscript is not yet peer-reviewed. The preprint is available at \url{https://psyarxiv.com/jp5nd/}.}
   We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website.
-All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923.
+All our code and a simulated GWP dataset is available at \url{https://doi.org/10.5281/zenodo.7774923}.
 We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below).
@@
 
-# Parallel computation options
+# Environment options
+DATA_PATH_GWP <- Sys.getenv(
+  "DATA_PATH_GWP"
+)
+DATA_PATH_GWP_CLEAN <- "data-raw/gwp.rds"
+DATA_PATH_SYN <- Sys.getenv(
+  "DATA_PATH_SYN",
+  unset = "data-synthetic/synthetic-data.rds"
+)
 MAX_CORES <- as.numeric(
@@
 )
-CORES <- MAX_CORES - 2
+
+# Figure theme
 theme_set(
@@
 
-path <- "data-raw/gwp.rds"
-if (dir.exists("data-raw/gallup") & !file.exists(path)) {
+# Wrangle GWP .sav file
+if (file.exists(DATA_PATH_GWP) & !file.exists(DATA_PATH_GWP_CLEAN)) {
 
@@
   dat <- read_spss(
-    "data-raw/gallup/The_Gallup_042722.sav", 
+    DATA_PATH, 
     col_select = c(
@@
   # Save
-  write_rds(dat, path)
+  write_rds(dat, DATA_PATH_GWP_CLEAN)
 }
@@
 #| label: data-synth-create
-#| eval: false
-
-# Here we create a synthetic smaller dataset that mimics some statistical properties of the dataset. It is a smaller dataset because generating the full table is very slow.
-if (FALSE) {
-  dir.create("synthetic-data", FALSE)
+
+# Create synthetic smaller dataset for code reproducibility.
+if (!file.exists(DATA_PATH_SYN)) {
+  dir.create(dirname(DATA_PATH_SYN), FALSE)
+
+  renv::settings$ignored.packages(c("synthpop", "mice"))
   library(synthpop)
+  library(mice)
+
   set.seed(909090)
-  x <- read_rds(path)
-  x <- x %>% 
-    filter(year > 2013) %>% 
-    filter(country %in% sample(unique(x$country), 20)) %>% 
-    # drop_na(starts_with("internet")) %>% 
-    slice_sample(n = 200, by = country)
-  x <- tibble(syn(x, method = "sample")$syn)
-  write_csv(x, "synthetic-data/synthetic-data.csv.gz")
+  data_synthetic <- read_rds(DATA_PATH_GWP_CLEAN) %>% 
+    filter(country %in% sample(unique(country), 20)) %>% 
+    slice_sample(n = 200, by = country) %>% 
+    mice(m = 1) %>% 
+    complete() %>% 
+    tibble()
+
+  data_synthetic <- data_synthetic %>% 
+    syn() %>% 
+    pluck("syn") %>% 
+    tibble()
+
+  write_rds(data_synthetic, DATA_PATH_SYN)
 }
@@
 #| label: data-load
-dat <- read_rds(path)
-# dat <- read_csv("synthetic-data/synthetic-data.csv.gz") # Synthetic dataset
+
+if (file.exists(DATA_PATH_GWP_CLEAN)) {
+  message("\n---\nUsing real data\n---\n")
+  dat <- read_rds(DATA_PATH_GWP_CLEAN)
+} else {
+  message("\n---\nUsing synthetic data\n---\n")
+  dat <- read_rds(DATA_PATH_SYN)
+}
 
@@
 
-dir.create("tmp", FALSE)
 path <- "tmp/multiverse-lmer.rds"
+dir.create(dirname(path), FALSE)
 if (!file.exists(path)) {
@@
   library(furrr)
-  plan(multisession, workers = CORES)
+  plan(multisession, workers = MAX_CORES)
 
@@
 }
+
+specs <- readRDS(path)
 ```
@@
 #| Label: multiverse-tidy
-specs <- readRDS(path) # Load from file
 

### 2023-11-13 ms.Rmd
Sample specs for synthetic data

@@
 DATA_PATH_SYN <- Sys.getenv(
-  "DATA_PATH_SYN",
-  unset = "data-synthetic/synthetic-data.rds"
+  "DATA_PATH_SYN"
 )
@@
   )
+
+# If only simulated data exists, sun small subset of specs
+set.seed(9091090)
+if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = MAX_CORES)
 ```

### 2023-11-13 ms.Rmd
Require Hmisc

@@
 library(ggside)
+library(Hmisc)
 library(ggbeeswarm)

### 2023-11-13 ms.Rmd
More reproducibility improvements

@@
 
-# If only simulated data exists, sun small subset of specs
+# If only simulated data exists, run just 1 spec by every X, Y pair
 set.seed(9091090)
-if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = MAX_CORES)
+if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = 1, by = c(y, x))
 ```
@@
 
-path <- "tmp/specs-lmer-total.rds"
+path <- "tmp/multiverse-lmer-average.rds"
 if (!file.exists(path)) {
@@
 } else {specs_avg <- readRDS(path)}
-
-# Median association (with reversed negative experiences)
-# tmp <- specs_avg %>% 
-#   mutate(estimate = if_else(y == "negative_experiences", -1*estimate, estimate)) %>% 
-#   summarise(across(c(estimate, std.error), median))
 ```
@@
 #| fig.width: 9
-#| fig.cap: Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences.
+#| fig.cap: "Scatterplots of countries' mean well-being outcomes for individuals who responded No and Yes to the internet question, and their differences.
 Small points are countries' means, and solid colored points and lines are means of the countries' means.
 Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\% confidence interval.
-The GWBI outcomes did not overlap in time with mobile internet data.
+The GWBI outcomes did not overlap in time with mobile internet data."
 
@@
 #| fig.width: 9
-#| fig.cap: Multiverse analysis results of associations between three internet use predictors and eight well-being outcomes.
+#| fig.cap: "Multiverse analysis results of associations between three internet use predictors and eight well-being outcomes.
 The estimated associations are ordered by increasing magnitude; the x-axis denotes the ordered number of (predictor * age * sex * covariate combination * weights) specification.
 The small shaded areas to the right of each panel show the kernel density estimates of the associations' point estimates, and the median association with a colored point.
+"
+
 draw_sca <- function(mv, Y) {

### 2023-11-13 ms.Rmd
Improve reproducibility
Sample specs for synthetic data

Require Hmisc

More reproducibility improvements

More reproducibility

@@
   include = FALSE,
-  cache = TRUE
+  cache = TRUE,
+  warning = FALSE
 )
@@
 set.seed(9091090)
-if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = 1, by = c(y, x))
+if (DATA_PATH_GWP == "") specs <- slice_sample(specs, n = 2, by = c(y, x))
 ```
@@
 Small points are countries' means, and solid colored points and lines are means of the countries' means.
-Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\% confidence interval.
+Numbers in each panel's left bottom corner indicate the regression coefficient (Yes - No) and its 95\\% confidence interval.
 The GWBI outcomes did not overlap in time with mobile internet data."

### 2023-11-13 ms.Rmd
Work on reproducibility (#4)
Fixes to reproducibility & links

@@
 # Environment options
-DATA_PATH_GWP <- Sys.getenv(
-  "DATA_PATH_GWP"
-)
-DATA_PATH_GWP_CLEAN <- "data-raw/gwp.rds"
-DATA_PATH_SYN <- Sys.getenv(
-  "DATA_PATH_SYN"
-)
-MAX_CORES <- as.numeric(
-  Sys.getenv(
-    "MAX_CORES", 
-    unset = parallel::detectCores(logical = FALSE)
-  )
-)
+MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
+DATA_PATH_GWP <- Sys.getenv("DATA_PATH_GWP")
+DATA_PATH_GWP_CLEAN <- Sys.getenv("DATA_PATH_GWP_CLEAN")
+DATA_PATH_SYN <- Sys.getenv("DATA_PATH_SYN")
+USE_GWP_DATA <- file.exists(DATA_PATH_GWP)
 
@@
 # Wrangle GWP .sav file
-if (file.exists(DATA_PATH_GWP) & !file.exists(DATA_PATH_GWP_CLEAN)) {
+if (USE_GWP_DATA & !file.exists(DATA_PATH_GWP_CLEAN)) {
 
@@
 # Create synthetic smaller dataset for code reproducibility.
-if (!file.exists(DATA_PATH_SYN)) {
+if (!file.exists(DATA_PATH_SYN) && file.exists(DATA_PATH_GWP_CLEAN)) {
   dir.create(dirname(DATA_PATH_SYN), FALSE)
